### 2022-09-16 paper/paper.tex
Adding ACM template for paper initialisation

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Evaluating Ad Creative and Web Context Alignment with Attention Measurement}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{John Hawkins}
\email{john.hawkins@playgroundxyz.com}
\orcid{1234-5678-9012}
\author{Graham Burton}
\email{graham.burton@playgroundxyz.com}
\affiliation{%
  \institution{Playground XYZ}
  \streetaddress{Level 11/61 York St}
  \city{Sydney}
  \state{NSW}
  \country{Australian}
  \postcode{2000}
}

\renewcommand{\shortauthors}{Hawkins \& Burton}

\begin{abstract}
Contextual targeting is a common strategy that places marketing messages
in media locations that are aligned with a target audience.
The challenge of contextual targeting is knowing the ideal schema and
the set of categories that provide the right audience.
Refinement of the contextual targeting process has been
limited by the use of metrics that are either rapid but
unreliable (click through rates), or reliable
but slow, expensive and inaccessible in real-time (conversions or brand awareness).

In this study we evaluate the use of attention measurement as a technique for
understanding the alignment between advertising creatives and media contexts.
We perform the analysis using
a large scale dataset of impressions categorised using the iAB V2.0 taxonomy. We
evaluate the alignment by looking for consistency across time in the attention
a given creative attracts over the levels of the categorisation hierarchy.

Our research is the largest known study of the relationship between advertising creative,
media context and consumer attention. We provide strong empirical evidence that consumer
attention is related to an alignment between the creative execution and topics of media
context. Furthermore, we show that this relationship transcends any specific publication
by providing reliable indications of attention on new website domains.

\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{Contextual Targeting, Attention Measurement, Digital Advertising, Digital Media}

\maketitle

\section{Introduction}
Contextual targeting allows advertisers to reach people with known interests,
rendered explicit
by the choice to consume media with content about a specific topic.
These contexts are thereby used to infer potential purchase intentions,
due to the association
between interests and products. Context is increasingly seen as a critical
factor in creating and defining brand engagement \cite{Wang2006}.

Context is also often used as an indirect method of reaching people that belong to certain
audiences or groups on the basis that people's interests and demographics are aligned \cite{str2016}.
A strategy that may be more effective given that targeting on the basis of gender alone
may not drive better results for many campaigns \cite{Jansen2013}.
The underlying assumptions about the relationships between demographics,
content and intentions
are supported by investigations into the social media behaviour of different demographic
groups \cite{Wang2016}.
Multiple studies have looked at the effect of media context on advertising outcomes.
A recent meta-analysis found significant effects for multiple dimensions of
media context on advertising recall \cite{Kwon2019}.
However, studies that look at the congruence
between the topic context of a page and the content of an ad have found some
counterintuitive results. For
example, brand recall can be associated with ads appearing within irrelevant contexts,
potentially due to an ability to stand out from a suite of relevant ads \cite{Kononova2020}.

The difficulty of implementing effective contextual targeting comes down three key issues.
You will need to determine an ideal contextual hierarcy or categorisation scheme that can be
applied uniformly across all media. You need to identify which components of that categorisation
scheme are appropriate for your brand or specific campaign. Finally, you need to balance the
contextual targeting against other goals like reach and frequency.
Advertisers generally must expand targeting to across high-level categories in order to
fulfill requirements as highly specific contexts are both expensive and rare.

In this work we experiment with the use of gaze duration as a measurement of
visual attention to determine the relative performance of categories within
the iAB V2.0 Contextual Hierarchy \cite{iabv2}.
We undertake this to understand the uniformity of the right context for a given brand, and
the reliability of performance across the hierarchy and across time. The goal is to determine
strategies by which contextual targeting can be refined for advertising outcomes.

Eye tracking studies are widely used as a method of measuring overt attention
to visual stimuli and have been applied to study the extent to which people
look at, and remember, advertising \cite{Hervet2011}. The technology has also
allowed the study of many factors that contribute to effective marketing,
including the impact of images of faces \cite{Djamasbi2010},
the use of animation \cite{Hamborg2012,Lee2012}, the relationship with
social media posts \cite{Barreto2013}, and emotional responses to visual stimuli
in different physical spaces \cite{Kim2021}.

Multiple investigations have identifed that attention time on advertising
provides a real-time metric that is correlated with important downstream
impacts like brand recall \cite{Lee2012}, consideration and purchase intent (\citeauthor{dentsu,PlaygroundXYZ}). Importantly, even though low attention can drive brand outcomes,
multiple studies have demonstrated that greater attention through direct
fixation has a greater impact on marketing outcomes, including
consideration, choice \cite{Santoso2021} and short term advertising
strength \cite{NelsonField}. The pervasive evidence of the role of visual attention
in the success of advertising has led to increasing focus on Attention Based Marketing
research \cite{Orquin2020}.

Contextual relevance is a method of aligning the message in advertising with the editorial
content that it is presented with \cite{Wang2011}. This is not simply a matter of
being \emph{about} the same topic, as consumers's have been shown to
to pay more attention to advertising that is relevant to their current task
(i.e. what they are looking for, or why they are reading) than simply advertising that
is contextually aligned \cite{Resnick2016}. This is coherent with observations
in the psychological literature that overt visual attention is influenced by motivations
and personality traits of individuals \cite{Kaspar2011}. Thus, the role of contextual
targeting may be to bring \emph{top-down} attention selection to advertising that would
otherwise garner attention in a \emph{bottom-up} manner \cite{Greenberg2013}.

We draw on two observations to motivate the current work. Firstly, advertisers are aware
that alignment between a campaign creative and media context can drive outcomes.
Secondly, they require methods for detecting when that alignment is functioning and
when it is not. The thesis of this research is that large scale real-time
measurement of ad attention can determine if an ad is aligned with a specific context,
and thereby provide a tool for fine tuning contextual targeting
strategies for advertiser outcomes. Conversely, it opens the door to using contextual
targeting as a method for advertisers to combat diminishing attention on
advertising \cite{Teixeira2014,Orquin2020}.

\section{Methodology}

In this research we investigate the efficacy of contextual targeting strategies
for obtaining improvements in the mean attention time paid to digital advertising.
The essential research question is whether the attention as ad attracts
within a given media context provides information about its future performance.
The null model assumes that context is not relevant and any contextual
variation should be subject to a regression to the mean.
In other words, the control hypothesis is that the mean attention paid to
a specific creative should be a better predictor of
future attention, than the attention that was paid within a specific context.

For the purposes of obtaining large scale measurements of attention time on
display advertising we utilise a machine learning system trained on data
collected from eye-tracking studies.
The attention model provides an impression level estimate of attention time,
that aggregates up into low error measurements of mean attention
time over groups of inventory.

\subsection{Attention Measurement}

We developed an attention measurement system that predicts attention time from user
behavioural signals. The training data is collected from eye tracking panels in
which subjects read media in self-directed sessions while eye tracking data is collected
using a gaze fixation model trained on facial images \cite{Krafka2016}.

As the eye tracking data is collected, we track a large number of other signals
about the user experience including environmental signals like the page structure,
and behavioural data like scroll events and the position of the advertising
in the viewport.

\begin{table}
  \caption{Attention Measurement Model - Aggregate Error}
  \label{tab:atm}
\begin{tabular}{|l|r|r|}
\toprule
Metric                  &Banner       &MREC       \\
\midrule
Aggregate MAE           &10.5 ms      &12.5 ms    \\
95\% Upper Bound        &19.0 ms      &20.6 ms    \\
95\% Lower Bound        &-22.8 ms     &-31.1 ms   \\
  \bottomrule
\end{tabular}
\end{table}

The signals collected along with the eye tracking data allow us to build and deploy an
attention measurment model that can predict the attention time paid to
specific ad units within a page. The attention model can
be applied to all digital inventory that accepts the javascript tag.

Our model evaluation process focuses on the accuracy of measuring mean
attention time for a specific ad format, over varying samples of inventory.
To generate the performance statistics we run bootstrap sampling of the test data
to look at the expected error when predicting the mean attention time over
impressions for a specific ad format. Each metric is calculated by taking 50 impression
samples 2000 times, and using the resulting distribution of mean error.
The mean attention time measurement performance is summarised in Table
\ref{tab:atm}.
We see that the aggregate mean absolute error (MAE) for both formats is very low
at $10.5 ms$ and $12.5 ms$ for banners and MRECs respectively. Furthermore, the
$95\%$ confidence intervals for these values is tightly constrained to be well under
$50 ms$ either side of the true value.
We apply this attention measurement model across large scale digitial inventory to
collect a data set of attention time paid to a range of advertisments over time.
We use these attention measured impressions to investigate the
impact of contextual categories of media on the attention paid to advertising.

\subsection{Data}
The data used in this study was collected from a wide range of advertisers running
broadly targeted campaigns between February and March 2022. It includes brands in
the automotive, retail, travel and health services verticals.
The data is broken into two one week time periods, the raw data was filtered
such that we had impressions for every creative in both
periods of time. This was a requirement of our approach so that we can
study the continuity of the relationships between creative, context and attention
across time.

In the analysis that follows we apply different levels of aggregation to the
log level impression data, so that we calculate the mean attention time for
a given creative in the specific context. Within each experiment we will
filter the aggregated data to ensure that every sample point is derived from
a least 50 impressions. This is done to ensure robust estimates of mean attention within
a given category.
Summary statistics for the dataset are shown in Table \ref{tab:dataset}. Note, that
due to the restriction outlined above, not every sample point will be in all experiemnts.

\begin{table}
\caption{Dataset of Attention Measured Impressions}
\label{tab:dataset}
\begin{tabular}{|l|r|r|}
\toprule
Metric          &Feb 18 - 24    &Feb 25 - March 03          \\
\midrule
Impressions     &16,895,661     &10,488,816     \\
URLS            &26,006         &27,855         \\
Domains         &2,263          &2,585          \\
Creatives       &683            &683            \\
Advertisers     &59             &59             \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Contextual Categorisation}

In order to derive contextual categories for each record in our dataset,
we applied the Verity API (\citeauthor{verity}) to the URLs. We converted the results of
the API response into a variety of features that describe the contextual
categories derived from the iAB V2.0 hierarchy \cite{iabv2}.

We identified the iAB category for which Verity had returned the
highest score and converted that category into a set of labels for
classification across the four Tiers of iAB V2.0. In instances where the
classified category is from a higher position in the hierarchy, then the
lower level tiers are given the deepest category. For example, if we have
a URL that is classified as iABv2 category "Business and Finance"
(a Tier 1 category) then Tiers 2, 3 and 4 will also contain the same value.

Alternatively, if we have another URL that is classified as "Marketing and Advertising"
(a Tier3 category below "Business and Finance"), then the hierarchical labels
would be assigned as follows:

\begin{itemize}
    \item {\texttt{Tier 1}}: ["Business and Finance"]
    \item {\texttt{Tier 2}}: ["Business"]
    \item {\texttt{Tier 3}}: ["Marketing and Advertising"]
    \item {\texttt{Tier 4}}: ["Marketing and Advertising"]
\end{itemize}

The idea of this scheme is that every page will be assigned a categorisation across
all four levels in the hierarchy, but sometimes the category at a given Tier
will not be any more specific than the parent category. This approach ensures
that comparisons can always be made, and when we look at a deeper level in the hierarchy
we will have at least as many distinct categories as the parent.

\subsection{Metrics}

The focus of our analysis is to determine whether the performance of each creative,
in a set of contexts, remains consistent across the two time periods.
Within each time period we aggregate
the measured attention time over the impression level data to obtain multiple metrics
for the reliability of attention time within a given context.

The attention metrics are calculated for a set of impressions $I_p$ in a time period $p$.
We first define a baseline for a creative $c$ in period $p$ as:
${}^c\mathcal{A}_p$. This is defined in equation \ref{campaign_baseline}.

\begin{equation}
\label{campaign_baseline}
{}^c\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}^c(i) A_i }{ \sum_{i \in I_p} \mathbf{1}^c(i) }
\end{equation}

Where the function $A(i)$ returns the attention measured on impression $i$ and
$\mathbf{1}^c(i)$ is an indicator function that
tests whether impression $i$ belongs to creative $c$, as shown in equation \ref{indicator}.

\begin{equation}
\label{indicator}
  \mathbf{1}^{c}(i):=
  \begin{cases}1~&{\text{ if }}~i\in c~,\\0~&{\text{ if }}~i\notin c~.\end{cases}
\end{equation}

Similarly, we denote the baseline attention achieved by ads on pages classified
as belonging to category $t$ in period $p$ as: ${}_t\mathcal{A}_p$. Defined in
equation \ref{topic_baseline}. Note, we use the notation $t$ for categories as they
are equivalent to topics, and this distinguishes them from the creatives.

\begin{equation}
\label{topic_baseline}
{}_t\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}_t(i) A(i) }{ \sum_{i \in I_p} \mathbf{1}_t(i) }
\end{equation}

Where $\mathbf{1}_t(i)$ is an indicator function that
tests whether impression $i$ was shown on a page classified as category $t$,
as show in in equation \ref{indicator2}.

\begin{equation}
\label{indicator2}
  \mathbf{1}_{t}(i):=
  \begin{cases}1~&{ i\text{ categorised as }}~t~,\\0~&{\text{ otherwise }}.\end{cases}
\end{equation}

We denote the mean attention performance for a creative $c$, on media of category $t$
within period $p$ as ${}^c_t\mathcal{A}_p$.
This is defined as shown in Equation \ref{mean_attention}.

\begin{equation}
\label{mean_attention}
{}^c_t\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}^c_t(i) A(i) }{ \sum_{i \in I_p} \mathbf{1}^c_t(i) }
\end{equation}

Where we simply apply a indicator function $\mathbf{1}^c_t(i)$ that is a composite
of Equations \ref{indicator} and \ref{indicator2} to filter for inventory that
belongs both to creative $c$ and category $t$. These equations should illustrate that we
make our evaluations by looking at the expected attention time across difference slices
of the inventory.

\subsection{Analysis}

Our analysis proceeds by ranking all topics that each creative $c$ was exposed
to according to the value of ${}^c_t\mathcal{A}_1$.
We then look at the same creatives in period 2 and
evaluate ${}^c_t\mathcal{A}_2$ for the top three ranking categories from the first period,
as well as the bottom ranking category.
This approach necessitates that each creative be exposed to a minimum
of these same 4 categories in both periods.
In the results that will follow we report the number
of records in each trial, reflecting the number of aggregated records
that fulfills these requirements.

Once we have the datasets in each period that meet these requirements we use multiple metrics
to evaluate the impact of the contextual categories. Our primary metric is the percentage
of instances in which the category specific performance ${}^c_t\mathcal{A}_2$ is above the
creative's baseline expected performance ${}^c\mathcal{A}_1$.
This is shown as \textbf{\% Over} (the baseline) in the tables of results.

In addition we look at the mean difference between ${}^c_t\mathcal{A}_2$ and ${}^c\mathcal{A}_1$
over all creatives in the experiment. This is denoted \boldmath$\mu\delta$ (or mean delta) in
the tables and defined in Equation \ref{delta}

\begin{equation}
\label{delta}
\mu\delta = \frac{ \sum_{c \in \mathcal{C}} {}^c_t\mathcal{A}_2 - {}^c\mathcal{A}_1 }{ \mathcal{C} }
\end{equation}

The mean delta illustrates an expectation of the difference between attention time performance
and the creative baseline, using a specific contextual targeting strategy. In addition, we show
that difference expressed as a mean percentage (against the baseline) in the column
$\mathbf{\mu\%\delta}$. This can be interpreted as the expected percentage increase/decrease
relative to the creative's baseline attention, when using that contextual targeting strategy.

\section{Results}

We conduct two variations of the experiment, each one looking at different
criteria for evaluating performance on new inventory.
These are referred to as the
\emph{No URL Repeats} and the \emph{No Domain Repeats} experiments.

\subsection{No URL Repeats}

In Table \ref{tab:nourlrepeats} we see the results of looking at performance on novel
URLs for a creative, where the iAB V2.0 contextual categories of those URLs were present
in either the top three or last ranking position in the initial period.

\begin{table}
\caption{Attention Performance by Category Rank on Novel URLs}
\label{tab:nourlrepeats}
\begin{tabular}{|l|r|l|r|r|r|}
\toprule
Level   &Count    &Rank &\% Over  &$\mu\delta$  &$\mu\%\delta$        \\
\midrule
Tier1   &206      &1st  &100.0\%    &4.5         &93.2\%     \\
        &         &2nd  &96.6\%     &2.6         &49.8\%     \\
        &         &3rd  &80.6\%     &1.4         &28.7\%     \\
        &         &Last &0.0\%      &-3.7        &-53.3\%     \\
Tier2   &210      &1st  &99.5\%     &6.3         &132.0\%     \\
        &         &2nd  &95.7\%     &3.7         &68.6\%     \\
        &         &3rd  &80.0\%     &2.4         &41.2\%     \\
        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
Tier3   &210      &1st  &99.5\%     &6.4         &135.7\%     \\
        &         &2nd  &95.7\%     &3.8         &69.5\%     \\
        &         &3rd  &79.5\%     &2.4         &41.8\%     \\
        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
Tier4   &210      &1st  &99.5\%     &6.4         &135.7\%     \\
        &         &2nd  &95.7\%     &3.8         &69.5\%     \\
        &         &3rd  &79.5\%     &2.4         &41.8\%     \\
        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
\bottomrule
\end{tabular}
\end{table}

We see that, in general, targeting pages using categories deeper into the hierarchy
improves the expected increase in attention through contextual targeting.
However, the effect appears to plateau at Tier3, likely due to the small proportion of inventory
that is uniquely classified at a Tier 4 level.

\begin{figure*}
\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_url_repeat.png}
\caption{Expected Lift in Attention Time on Inventory without Repeated URLs.}
\label{fig:no_url}
\end{figure*}

We show the change in attention lift across the dimensions of iAB Tiers and category ranking
in Figure \ref{fig:no_url}. This figure demonstrates the increased performance with the specificity
of the iAB Tiers and the reduction in performance with the movement down category ranks.

\subsection{No Domain Repeats}
We repeat the analysis restricting ourselves to impressions in the second period
that involve URLS for which the domain was not present in the URLs for the first period.
The results are shown in Table \ref{tab:nodomainrepeats}.
We note that the number of records has dropped by
more than half in this experiment, due to the difficulty of finding domains that were
not present in the first period.

\begin{table}
\caption{Attention Performance by Category Rank on Novel Domains}
\label{tab:nodomainrepeats}
\begin{tabular}{|l|r|l|r|r|r|}
\toprule
Level   &Count  &Rank &\% Over  &$\mu\delta$  &$\mu\%\delta$        \\
\midrule
Tier1   &86       &1st  &98.8\%     &5.2         &144.3\%     \\
        &         &2nd  &83.7\%     &2.3         &58.8\%     \\
        &         &3rd  &60.5\%     &0.4         &26.9\%     \\
        &         &Last &0.0\%      &-4.1        &-64.5\%     \\
Tier2   &83       &1st  &96.4\%     &6.4         &159.1\%     \\
        &         &2nd  &84.3\%     &2.6         &71.0\%     \\
        &         &3rd  &59.0\%     &0.7         &35.8\%     \\
        &         &Last &0.0\%      &-4.5        &-70.0\%     \\
Tier3   &82       &1st  &96.3\%     &6.5         &161.3\%     \\
        &         &2nd  &84.2\%     &2.7         &71.2\%     \\
        &         &3rd  &56.1\%     &0.6         &34.7\%     \\
        &         &Last &0.0\%      &-4.6        &-69.9\%     \\
Tier4   &82       &1st  &96.3\%     &6.5         &161.3\%     \\
        &         &2nd  &84.2\%     &2.7         &71.6\%     \\
        &         &3rd  &56.1\%     &0.6         &34.7\%     \\
        &         &Last &0.0\%      &-4.6        &-69.9\%     \\
\bottomrule
\end{tabular}
\end{table}

We show the change in attention lift across the dimensions of iAB Tiers and category ranking
in Figure \ref{fig:no_dom}. This figure demonstrates that in the no domain repeat experiment
we get a very similar overall pattern to the previous experiment. The primary difference
being a higher expected lift at the rank one position, and a faster drop off in expected
lift as we move down the ranks.

\begin{figure*}
\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_dom_repeat.png}
\caption{Expected Lift in Attention Time on Inventory without Repeated Domains.}
\label{fig:no_dom}
\end{figure*}

The restriction to unique domains in the second period has lifted the expected improvement
of targeting the top performing category (Tier 3) from 135% to 161%. However, this improvement
only occurs with the category in ranking position one. For the other ranking positions
the results are mixed, even though the percentage amount is sometimes higher, the
absolute amount can be lower, due to the fact that the baseline is calculated on
the impressions that qualify for inclusion.

These result seems counterintuitive at first glance. Our current hypothesis about why
this is the case is that it relates to the specificity of the content on a given domain.
The \emph{no domain repeats} study is biased towards data on less common domains.
These may have a tendency to be more subject specific.
These ideas need to be tested in follow up research.

Additionally, we note that the percentage of instances where the category targeting
delivers an improvement over the baseline drops when we look at unique domains.
This drop is approximately 3% for rank 1 categories, but by the time we arrive at
the 3rd ranked category it has dropped from 80% to 56% at Tier 4, meaning that
targeting new domains with the 3rd ranked category offers a marginally better than
random chance of delivering improved attention.

\subsection{Significance Tests}

We estimated p-values for the significance of the proportion of URLs within a given category
that outperform the baseline. We did this using a binomial distribution, under the null model
assumption that the relationship between the attention on a URL and its contextual category
is random. Hence, the p-value can be estimated as the probability of obtaining the observed
number of successful improvements over the baseline as samples from a binomial with a probability
of success equal to $0.5$.

The computed p-values were extremely small, starting at $10^{-62}$ for first rank of Tier 1 in
the \emph{No URL Repeats} experiment, $10^{-24}$ for the \emph{No Domain Repeats} experiment.
The p-values increase gradually as we move down the ranking of the categories or at deeper
levels in the iAB hierarchy, but they always remain below a significance level
of 0.05.

A more stringent analysis would apply a Bonferroni correction to account for the multiple
hypothesis tests in these tables of data. Even with this correction, the vast majority
of results
are many orders of magnitude below the significance threshold. However, under this criteria
we would reject the third ranking category within the \emph{No Domain Repeats} experiments.
However, as the observed data is overwhelmingly statistically significant, and these values
are consistent with the hypothesis being true, but suffering from a diminishing effect size,
and reduced sample sizes, we included the values for the third ranking categories in the
table.

\section{Conclusion}
The pattern we observe is consistent between the two experiments. Regardless of
how novel the inventory is, there is a tendency for media sharing the top contextual
categories from the
initial period to consistently outperform the baseline attention.
This pattern is strongest with the number one category, and then recedes
as we progress down the ranking of categories from the first period.

Similarly, the bottom performing category from the first period consistently under performs
the baseline in the subsequent period, regardless of whether you are looking at new URLs
on existing domains, or entirely new domains.
These results strongly suggest that the topics discussed on pages in which an ad appears
interact with ad creatives in a way that enables prediction of ad attention.

As we move deeper into the hierarchy from Tier 1 down to Tier 4 we see that the average size
of the improvement increases, but this effect appears to plateau at Tier 3. We note that this
improvement would often be countered by reduced inventory volumes, suggesting that application
of these results will require weighting the gains against potential reach.

When we look at inventory on novel domains we see that there is a further small drop in the
proportion of instances where the category continues to deliver improved results. This is
countered by an improvement in the gain for the top performing category, suggesting that a
reasonable and risk efficient strategy for finding new inventory is to target multiple top
ranking categories on known websites, but just the top ranking category on novel websites.

Overall, these results provide strong evidence that attention measurement provides a signal
as to whether a given contextual targeting strategy is aligned with an advertising creative.
Performance, in terms of attention garnered, in an initial period is predictive of
attention in a future period even when the specific media changes.
The reliability of attention on new URLs or domains within the same contextual category
suggests that the iAB hierarchy provides insight into factors that align advertising
creatives with consumer psychology beyond the specifics of a particular media platform.

\section{Acknowledgments}
This research was financially supported by Playground XYZ and Gumgum.
The content benefited from commentary and observations made by Rob Hall.

\bibliographystyle{ACM-Reference-Format}
\bibliography{../bibliography/refs}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2022-09-16 paper/paper.tex
Reshaping paper template

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Evaluating Ad Creative and Web Context Alignment with Attention Measurement}
+\title{What's in a Domain?}
 
@@
 \author{John Hawkins}
-\email{john.hawkins@playgroundxyz.com}
+\email{john.hawkins@Getting-Data-Science-Done.com}
 \orcid{1234-5678-9012}
-\author{Graham Burton}
-\email{graham.burton@playgroundxyz.com}
 \affiliation{%
-  \institution{Playground XYZ}
-  \streetaddress{Level 11/61 York St}
+  \institution{Getting-Data-Science-Done.com}
   \city{Sydney}
   \state{NSW}
-  \country{Australian}
+  \country{Australia}
   \postcode{2000}
@@
 
-\renewcommand{\shortauthors}{Hawkins \& Burton}
+\renewcommand{\shortauthors}{Hawkins}
 
 \begin{abstract}
-Contextual targeting is a common strategy that places marketing messages
-in media locations that are aligned with a target audience.
-The challenge of contextual targeting is knowing the ideal schema and
-the set of categories that provide the right audience.
-Refinement of the contextual targeting process has been
-limited by the use of metrics that are either rapid but
-unreliable (click through rates), or reliable
-but slow, expensive and inaccessible in real-time (conversions or brand awareness).
-
-In this study we evaluate the use of attention measurement as a technique for
-understanding the alignment between advertising creatives and media contexts.
-We perform the analysis using
-a large scale dataset of impressions categorised using the iAB V2.0 taxonomy. We
-evaluate the alignment by looking for consistency across time in the attention
-a given creative attracts over the levels of the categorisation hierarchy.
-
-Our research is the largest known study of the relationship between advertising creative,
-media context and consumer attention. We provide strong empirical evidence that consumer
-attention is related to an alignment between the creative execution and topics of media
-context. Furthermore, we show that this relationship transcends any specific publication
-by providing reliable indications of attention on new website domains.
 
@@
 
-\keywords{Contextual Targeting, Attention Measurement, Digital Advertising, Digital Media}
+\keywords{URL Features, Document Classification, Machine Learning, Semantic Web}
 
@@
 \section{Introduction}
-Contextual targeting allows advertisers to reach people with known interests,
-rendered explicit
-by the choice to consume media with content about a specific topic.
-These contexts are thereby used to infer potential purchase intentions,
-due to the association
-between interests and products. Context is increasingly seen as a critical
-factor in creating and defining brand engagement \cite{Wang2006}.
-
-Context is also often used as an indirect method of reaching people that belong to certain
-audiences or groups on the basis that people's interests and demographics are aligned \cite{str2016}.
-A strategy that may be more effective given that targeting on the basis of gender alone
-may not drive better results for many campaigns \cite{Jansen2013}.
-The underlying assumptions about the relationships between demographics,
-content and intentions
-are supported by investigations into the social media behaviour of different demographic
-groups \cite{Wang2016}.
-Multiple studies have looked at the effect of media context on advertising outcomes.
-A recent meta-analysis found significant effects for multiple dimensions of
-media context on advertising recall \cite{Kwon2019}.
-However, studies that look at the congruence
-between the topic context of a page and the content of an ad have found some
-counterintuitive results. For
-example, brand recall can be associated with ads appearing within irrelevant contexts,
-potentially due to an ability to stand out from a suite of relevant ads \cite{Kononova2020}.
-
-The difficulty of implementing effective contextual targeting comes down three key issues.
-You will need to determine an ideal contextual hierarcy or categorisation scheme that can be
-applied uniformly across all media. You need to identify which components of that categorisation
-scheme are appropriate for your brand or specific campaign. Finally, you need to balance the
-contextual targeting against other goals like reach and frequency.
-Advertisers generally must expand targeting to across high-level categories in order to
-fulfill requirements as highly specific contexts are both expensive and rare.
-
-In this work we experiment with the use of gaze duration as a measurement of
-visual attention to determine the relative performance of categories within
-the iAB V2.0 Contextual Hierarchy \cite{iabv2}.
-We undertake this to understand the uniformity of the right context for a given brand, and
-the reliability of performance across the hierarchy and across time. The goal is to determine
-strategies by which contextual targeting can be refined for advertising outcomes.
-
-Eye tracking studies are widely used as a method of measuring overt attention
-to visual stimuli and have been applied to study the extent to which people
-look at, and remember, advertising \cite{Hervet2011}. The technology has also
-allowed the study of many factors that contribute to effective marketing,
-including the impact of images of faces \cite{Djamasbi2010},
-the use of animation \cite{Hamborg2012,Lee2012}, the relationship with
-social media posts \cite{Barreto2013}, and emotional responses to visual stimuli
-in different physical spaces \cite{Kim2021}.
-
-Multiple investigations have identifed that attention time on advertising
-provides a real-time metric that is correlated with important downstream
-impacts like brand recall \cite{Lee2012}, consideration and purchase intent (\citeauthor{dentsu,PlaygroundXYZ}). Importantly, even though low attention can drive brand outcomes,
-multiple studies have demonstrated that greater attention through direct
-fixation has a greater impact on marketing outcomes, including
-consideration, choice \cite{Santoso2021} and short term advertising
-strength \cite{NelsonField}. The pervasive evidence of the role of visual attention
-in the success of advertising has led to increasing focus on Attention Based Marketing
-research \cite{Orquin2020}.
-
-Contextual relevance is a method of aligning the message in advertising with the editorial
-content that it is presented with \cite{Wang2011}. This is not simply a matter of
-being \emph{about} the same topic, as consumers's have been shown to
-to pay more attention to advertising that is relevant to their current task
-(i.e. what they are looking for, or why they are reading) than simply advertising that
-is contextually aligned \cite{Resnick2016}. This is coherent with observations
-in the psychological literature that overt visual attention is influenced by motivations
-and personality traits of individuals \cite{Kaspar2011}. Thus, the role of contextual
-targeting may be to bring \emph{top-down} attention selection to advertising that would
-otherwise garner attention in a \emph{bottom-up} manner \cite{Greenberg2013}.
-
-We draw on two observations to motivate the current work. Firstly, advertisers are aware
-that alignment between a campaign creative and media context can drive outcomes.
-Secondly, they require methods for detecting when that alignment is functioning and
-when it is not. The thesis of this research is that large scale real-time
-measurement of ad attention can determine if an ad is aligned with a specific context,
-and thereby provide a tool for fine tuning contextual targeting
-strategies for advertiser outcomes. Conversely, it opens the door to using contextual
-targeting as a method for advertisers to combat diminishing attention on
-advertising \cite{Teixeira2014,Orquin2020}.
 
 \section{Methodology}
-
-In this research we investigate the efficacy of contextual targeting strategies
-for obtaining improvements in the mean attention time paid to digital advertising.
-The essential research question is whether the attention as ad attracts
-within a given media context provides information about its future performance.
-The null model assumes that context is not relevant and any contextual
-variation should be subject to a regression to the mean.
-In other words, the control hypothesis is that the mean attention paid to
-a specific creative should be a better predictor of
-future attention, than the attention that was paid within a specific context.
-
-For the purposes of obtaining large scale measurements of attention time on
-display advertising we utilise a machine learning system trained on data
-collected from eye-tracking studies.
-The attention model provides an impression level estimate of attention time,
-that aggregates up into low error measurements of mean attention
-time over groups of inventory.
-
-\subsection{Attention Measurement}
-
-We developed an attention measurement system that predicts attention time from user
-behavioural signals. The training data is collected from eye tracking panels in
-which subjects read media in self-directed sessions while eye tracking data is collected
-using a gaze fixation model trained on facial images \cite{Krafka2016}.
-
-As the eye tracking data is collected, we track a large number of other signals
-about the user experience including environmental signals like the page structure,
-and behavioural data like scroll events and the position of the advertising
-in the viewport.
 

### 2022-09-16 paper/abstract.tex
Paper notes

Many data science problems require processing log data derived from web pages, apis or other 
internet based services. URLs are one of the key pieces of information that describe almost
all types of internet activity. While they are structurally rich, it is not entirely obvious 
how to derive the optimal features from a set of URLs or domains.

In this talk we will discuss a wide variety of approaches to deriving features from URLs and domains. 
We begin with a breakdown of the broad categories of URL derived features and then discuss some of 
the key implementation details, and types of problems for which they are appropriate.
Many of the ideas in this talk have been implemented in the open source python library url2features.

https://github.com/getting-data-science-done/url2features

### 2022-09-16 paper/paper.tex
Paper init

@@
 \begin{abstract}
+Many data science problems require processing log data derived from web pages, apis or other
+internet based services. URLs are one of the key pieces of information that describe almost
+all types of internet activity, and hence need to be processed in a wide variety of machine 
+learning applications for internet data. While URLs are structurally rich, they are not subject
+to universal principles of construction making fetaure engineering for internet data challenging.
 
+In this research we outline the key classes of approaches to deriving features from URLs and domains,
+and demonstrate their utility in an open source URL fetaure engineering package url2features.
+We begin with a breakdown of the broad categories of URL derived features and then discuss some of
+the key implementation details, and types of problems for which they are appropriate.
 \end{abstract}
@@
 %%
+
 \begin{CCSXML}
@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10002951.10003260.10003261</concept_id>
+<concept_desc>Information systems~Web searching and information discovery</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
+<concept_id>10002951.10003260.10003277.10003280</concept_id>
+<concept_desc>Information systems~Web log analysis</concept_desc>
+<concept_significance>500</concept_significance>
 </concept>
 <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+<concept_id>10010147.10010257</concept_id>
+<concept_desc>Computing methodologies~Machine learning</concept_desc>
+<concept_significance>500</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Information systems~Web searching and information discovery}
+\ccsdesc[500]{Information systems~Web log analysis}
+\ccsdesc[500]{Computing methodologies~Machine learning}
 

### 2022-09-16 paper/paper.tex
Paper

@@
 \setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
+\copyrightyear{2022}
+\acmYear{2022}
 \acmDOI{XXXXXXX.XXXXXXX}
@@
   conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
+  2022}{Austin, TX}
 \acmPrice{15.00}
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{What's in a Domain?}
+\title{What's in a Domain?: Feature Engineering for URLs}
 
@@
 Many data science problems require processing log data derived from web pages, apis or other
-internet based services. URLs are one of the key pieces of information that describe almost
-all types of internet activity, and hence need to be processed in a wide variety of machine 
-learning applications for internet data. While URLs are structurally rich, they are not subject
-to universal principles of construction making fetaure engineering for internet data challenging.
+internet traffice sources. URLs are one of the few universal pieces of information that describe
+internet activity, hence URLs require effective processing for a wide variety of machine 
+learning applications. While URLs are structurally rich, they are not subject
+to universal principles of construction making fetaure engineering for internet data an ongoing challenge.
 
-In this research we outline the key classes of approaches to deriving features from URLs and domains,
-and demonstrate their utility in an open source URL fetaure engineering package url2features.
-We begin with a breakdown of the broad categories of URL derived features and then discuss some of
-the key implementation details, and types of problems for which they are appropriate.
+In this research we outline the key categories of information structure in domains and URLs.
+We share an open source implementation of these ideas and demonstrate their utility across a range of 
+internet traffic machine learning problems.
 \end{abstract}

### 2022-09-17 paper/paper.tex
Literature review

@@
 
+Litrature review
+
+Write a literature review \cite{Vazhayil2018}
+\cite{Canali2011}
+\cite{Ayes2019}
+\cite{Mamun2016}
+\cite{Li2020}
+\cite{Basnet2012}
+\cite{Basnet2014}
+\cite{Tupsamudre2019}
+\cite{Le2018}
+\cite{Baykan2009}
+\cite{Kan2005}
+\cite{Hernandez2012}
+\cite{Chung2022}
+\cite{Qiu2020}
+\cite{Vaishnavi2021}
+\cite{Xu2021}
+\cite{Rhea2022}
+
 \section{Methodology}
@@
 \subsection{Data}
-The data used in this study was collected from a wide range of advertisers running
-broadly targeted campaigns between February and March 2022. It includes brands in
-the automotive, retail, travel and health services verticals.
-The data is broken into two one week time periods, the raw data was filtered
-such that we had impressions for every creative in both
-periods of time. This was a requirement of our approach so that we can
-study the continuity of the relationships between creative, context and attention
-across time.
 
-In the analysis that follows we apply different levels of aggregation to the
-log level impression data, so that we calculate the mean attention time for
-a given creative in the specific context. Within each experiment we will
-filter the aggregated data to ensure that every sample point is derived from
-a least 50 impressions. This is done to ensure robust estimates of mean attention within
-a given category.
-Summary statistics for the dataset are shown in Table \ref{tab:dataset}. Note, that
-due to the restriction outlined above, not every sample point will be in all experiemnts.
+The data used in this study was collected from a collction of publications that 
+present internet classification problems containing URLs as a key, or sole feature.
+Malcious URL classification \cite{Mamun2016}.
 
 \begin{table}
-\caption{Dataset of Attention Measured Impressions}
+\caption{Datasets}
 \label{tab:dataset}
@@
 
-In order to derive contextual categories for each record in our dataset,
-we applied the Verity API (\citeauthor{verity}) to the URLs. We converted the results of
-the API response into a variety of features that describe the contextual
-categories derived from the iAB V2.0 hierarchy \cite{iabv2}.
-
-We identified the iAB category for which Verity had returned the
+Verity had returned the
 highest score and converted that category into a set of labels for
@@
 
-\begin{figure*}
-\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_url_repeat.png}
-\caption{Expected Lift in Attention Time on Inventory without Repeated URLs.}
-\label{fig:no_url}
-\end{figure*}
-
-We show the change in attention lift across the dimensions of iAB Tiers and category ranking
-in Figure \ref{fig:no_url}. This figure demonstrates the increased performance with the specificity
-of the iAB Tiers and the reduction in performance with the movement down category ranks.
-
 \subsection{No Domain Repeats}
@@
 
-We show the change in attention lift across the dimensions of iAB Tiers and category ranking
-in Figure \ref{fig:no_dom}. This figure demonstrates that in the no domain repeat experiment
-we get a very similar overall pattern to the previous experiment. The primary difference
-being a higher expected lift at the rank one position, and a faster drop off in expected
-lift as we move down the ranks.
-
-\begin{figure*}
-\includegraphics[scale=0.6]{../ranking_analysis/results/iABv2/no_dom_repeat.png}
-\caption{Expected Lift in Attention Time on Inventory without Repeated Domains.}
-\label{fig:no_dom}
-\end{figure*}
-
 The restriction to unique domains in the second period has lifted the expected improvement
@@
 
-\subsection{Significance Tests}
-
-We estimated p-values for the significance of the proportion of URLs within a given category
-that outperform the baseline. We did this using a binomial distribution, under the null model
-assumption that the relationship between the attention on a URL and its contextual category
-is random. Hence, the p-value can be estimated as the probability of obtaining the observed
-number of successful improvements over the baseline as samples from a binomial with a probability
-of success equal to $0.5$.
-
-The computed p-values were extremely small, starting at $10^{-62}$ for first rank of Tier 1 in
-the \emph{No URL Repeats} experiment, $10^{-24}$ for the \emph{No Domain Repeats} experiment.
-The p-values increase gradually as we move down the ranking of the categories or at deeper
-levels in the iAB hierarchy, but they always remain below a significance level
-of 0.05.
-
-A more stringent analysis would apply a Bonferroni correction to account for the multiple
-hypothesis tests in these tables of data. Even with this correction, the vast majority
-of results
-are many orders of magnitude below the significance threshold. However, under this criteria
-we would reject the third ranking category within the \emph{No Domain Repeats} experiments.
-However, as the observed data is overwhelmingly statistically significant, and these values
-are consistent with the hypothesis being true, but suffering from a diminishing effect size,
-and reduced sample sizes, we included the values for the third ranking categories in the
-table.
-
 \section{Conclusion}
-The pattern we observe is consistent between the two experiments. Regardless of
-how novel the inventory is, there is a tendency for media sharing the top contextual
-categories from the
-initial period to consistently outperform the baseline attention.
-This pattern is strongest with the number one category, and then recedes
-as we progress down the ranking of categories from the first period.
-
-Similarly, the bottom performing category from the first period consistently under performs
-the baseline in the subsequent period, regardless of whether you are looking at new URLs
-on existing domains, or entirely new domains.
-These results strongly suggest that the topics discussed on pages in which an ad appears
-interact with ad creatives in a way that enables prediction of ad attention.
-
-As we move deeper into the hierarchy from Tier 1 down to Tier 4 we see that the average size
-of the improvement increases, but this effect appears to plateau at Tier 3. We note that this
-improvement would often be countered by reduced inventory volumes, suggesting that application
-of these results will require weighting the gains against potential reach.
-
-When we look at inventory on novel domains we see that there is a further small drop in the
-proportion of instances where the category continues to deliver improved results. This is
-countered by an improvement in the gain for the top performing category, suggesting that a
-reasonable and risk efficient strategy for finding new inventory is to target multiple top
-ranking categories on known websites, but just the top ranking category on novel websites.
-
-Overall, these results provide strong evidence that attention measurement provides a signal
-as to whether a given contextual targeting strategy is aligned with an advertising creative.
-Performance, in terms of attention garnered, in an initial period is predictive of
-attention in a future period even when the specific media changes.
-The reliability of attention on new URLs or domains within the same contextual category
-suggests that the iAB hierarchy provides insight into factors that align advertising
-creatives with consumer psychology beyond the specifics of a particular media platform.
 
 \section{Acknowledgments}
-This research was financially supported by Playground XYZ and Gumgum.
-The content benefited from commentary and observations made by Rob Hall.
 
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{../bibliography/refs}
+\bibliography{refs}
 

### 2022-09-19 paper/paper.tex
References

@@
 
-Litrature review
+The Uniform Resource Locator (URL) is now a ubiquitous element of modern life. 
+We use them to advertise and locate businesses, to retrieve news and media and 
+to interact with other people across a broad of social applications. It should
+be no surprise that processing URLs is key component of many tasks that involve
+analysing internet data. In many applications the URL is the central piece of 
+information available because the demands of the task require immediate analysis.
+Prominent examples include security analysis of potenital phishing attacks\cite{Basnet2014}, 
+detection of potential spam emails \cite{}, and applications to online advertsing
+including anticipation of conversions \cite{Qiu2020} or contextual analysis of
+the content of webpages\cite{Kan2005,Baykan2009}.
 
+The URL is made up of multiple elements, but at its core is the domain. The domain
+contains internal information about both its intended purpose, legitimacy and likely
+origin. It is also a source of additional information through requests to Domain Name
+Servers (DNS) to understand both its history and place within the network topology.
+
+Common feature engineering strategies exploit these potential sources of information
+in ways that are appropriate for a given task. However, while there are wide variety
+of approaches that inconsistently applied, there has not yet been a study that evaluates
+the overall effectiveness of different strategies across a range of applications.
+
+In this work we describe an ontology of URL fetaures that relates to underlying origin
+and purpose. We then present an open source package for generating features within these
+ontologocal classes and apply them to a variety of tasks. We present our results as a
+cross-task evaluation of URL features.
+
+Multiple data science and machine learning applications on internet data 
 Write a literature review \cite{Vazhayil2018}
@@
 \cite{Rhea2022}
+
+Common approaches to feature engineering on URLs include string matching and regular expressions to
+identify key sequences \cite{}, generation of task specific embedding vectors\cite{Qiu2020} and the
+usage of domain name servers or registrars for ancillary information \cite{}
 

### 2022-09-19 paper/paper.tex
References cleanup and intro/lit review

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{What's in a Domain?: Feature Engineering for URLs}
+\title{What's in a Domain? Anaylsis of URL Features}
 
@@
 \cite{Hernandez2012}
-\cite{Chung2022}
+\cite{Chung2010}
 \cite{Qiu2020}
@@
 
-Common approaches to feature engineering on URLs include string matching and regular expressions to
-identify key sequences \cite{}, generation of task specific embedding vectors\cite{Qiu2020} and the
+Common approaches to feature engineering on URLs include string patterns and regular expressions to
+identify key sequences \cite{}, n-gram models \cite{Baykan2009}, 
+the generation of task specific embedding vectors\cite{Qiu2020} and the
 usage of domain name servers or registrars for ancillary information \cite{}
@@
 Malcious URL classification \cite{Mamun2016}.
+
+4 Universities data http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-20/www/data/
 

### 2022-09-19 paper/paper.tex
Literature

@@
 including anticipation of conversions \cite{Qiu2020} or contextual analysis of
-the content of webpages\cite{Kan2005,Baykan2009}.
+the content\cite{Kan2005,Baykan2009} or language\cite{Baykan2013} of webpages.
 
@@
 \cite{Rhea2022}
+\cite{Ma2009}
+\cite{Verma2017}
+\cite{Sountharrajan2020}
 

### 2022-09-21 paper/paper.tex
Literature review work

@@
 \cite{Tupsamudre2019}
-\cite{Le2018}
+URLnet learns word and charcater embedings \cite{Le2018}
 \cite{Baykan2009}
@@
 \cite{Sountharrajan2020}
+Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
+of the URL to features derived from either link anchor text or the web page document itself \cite{Kan2004}.
 
 Common approaches to feature engineering on URLs include string patterns and regular expressions to
-identify key sequences \cite{}, n-gram models \cite{Baykan2009}, 
-the generation of task specific embedding vectors\cite{Qiu2020} and the
-usage of domain name servers or registrars for ancillary information \cite{}
+identify key sequences \cite{Kan2004}, n-gram or bag of words models \cite{Baykan2009}, 
+the generation of task specific embedding vectors\cite{Le2018,Qiu2020} and the
+usage of domain name servers or registrars for ancillary information \cite{}. Some authors have 
+empahsized that URLs are sequences of characters and require features that respect this ordering\cite{Le2018}.
+However, the ordering of key features within URLs is predominantly fixed.
 

### 2022-09-28 url2features/cli.py
Adding no prefix option and protocol features

@@ -54,27 +54,36 @@ def get_cmd_line_params(argv):
     options = argv[1:-1]
     result = {"dataset":data,
               "columns":[], 
+              "prefix":True, 
               "simple":False, 
+              "protocol":False, 
               "domain":False, 
               "extension":False, 
-              "dns":False, 
               "file":False, 
+              "dns":False, 
     }
     for o in options:
         parts = o.split("=")
+        if parts[0] == "-np":
+            result["prefix"]=False
         if parts[0] == "-simple":
             result["simple"]=True
+        if parts[0] == "-protocol":
+            result["protocol"]=True
         if parts[0] == "-domain":
             result["domain"]=True
+        if parts[0] == "-extension":
+            result["extension"]=True
         if parts[0] == "-file":
             result["file"]=True
         if parts[0] == "-dns":
             result["dns"]=True
-        if parts[0] == "-extension":
-            result["extension"]=True
         if parts[0] == "-columns":
             cols = parts[1].split(",")
             result["columns"]=cols
+
+    if len(result["columns"])>1:
+        result["prefix"] = True # Force prefix for multiple columns
 
     return result
 
@@ -86,11 +95,13 @@ def print_usage(args):
     print("  <PATH TO DATASET> - Supported file types: csv, tsv, xls, xlsx, odf")
     print(" [ARGS] In most cases these are switches that turn on the feature type")
     print("  -columns=<COMMA SEPARATED LIST>. REQUIRED")
-    print("  -simple            Default: False. Features derived from the URL string: length, depth")
+    print("  -simple            Default: False. Features derived from the URL string: length, depth, components")
     print("  -domain            Default: False. Features from the domain registration (requires internet).")
-    print("  -file              Default: False. Features derived from the final file.")
-    print("  -dns               Default: False. Features derived from the DNS records (requires internet).")
     print("  -extension         Default: False. Features about the domain extension and structure.")
+    print("  -protocol          Default: False. Features from the URL protocol.")
+    print("  -file              Default: False. Features derived from the final file type")
+    print("  -dns               Default: False. Features derived from the DNS records (requires internet).")
+    print("  -np                Deactivate use of column name prefix. Only works for a single column.")
     print("")
 
 

### 2022-09-28 url2features/dns.py

@@ -19,19 +19,19 @@ import re
 """
 
 ########################################################################################
-def dns_features(df, columns):
+def dns_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
         calculate the DNS summary features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_dns_features(rez, col)
+        rez = add_dns_features(rez, col, add_prefix)
     return rez
 
 
 ########################################################################################
-def add_dns_features(df, col):
+def add_dns_features(df, col, add_prefix=True):
     """
         Given a pandas dataframe and a column name containing a URL
         calculate the DNS features 
@@ -53,7 +53,12 @@ def add_dns_features(df, col):
             country = get_country(url_parts)
         return ns, mx, ptr, country
 
-    df[[ col+'_dns_ns', col+'_dns_mx', col+'_dns_ptr', col+'_dns_country' ]] = df.apply(dns_feature_gen, col=col, axis=1, result_type="expand")
+    if add_prefix:
+        col_names = [ col+'_dns_ns', col+'_dns_mx', col+'_dns_ptr', col+'_dns_country' ]
+    else:
+        col_names = [ 'dns_ns', 'dns_mx', 'dns_ptr', 'dns_country' ]
+
+    df[ col_names ] = df.apply(dns_feature_gen, col=col, axis=1, result_type="expand")
 
     return df
 

### 2022-09-28 url2features/domain.py

@@ -24,14 +24,14 @@ language_codes = ['ab', 'aa', 'af', 'ak', 'sq', 'am', 'ar', 'an', 'hy', 'as', 'a
 
 
 ########################################################################################
-def domain_features(df, columns):
+def domain_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
         calculate the domain features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_domain_features(rez, col)
+        rez = add_domain_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
@@ -65,7 +65,7 @@ def get_subdomain_freq(sub):
         return 0.0
     
 ########################################################################################
-def add_domain_features(df, col):
+def add_domain_features(df, col, add_prefix=True):
     """
         Given a pandas dataframe and a column name.
         add features for the domain:
@@ -100,7 +100,12 @@ def add_domain_features(df, col):
 
         return secs, sub_type, sub_freq, reg_year
 
-    df[[ col+'_domain_sections', col+'_subdomain_type', col+'_subdomain_freq', col+'_dom_reg_year'  ]] = df.apply(dom_features, col=col, axis=1, result_type="expand")
+    if add_prefix:
+        col_names = [ col+'_domain_sections', col+'_subdomain_type', col+'_subdomain_freq', col+'_domain_reg_year'  ]
+    else:
+        col_names = [ 'domain_sections', 'subdomain_type', 'subdomain_freq', 'domain_reg_year'  ]
+
+    df[ col_names ] = df.apply(dom_features, col=col, axis=1, result_type="expand")
 
     return df
  

### 2022-09-28 url2features/extension.py

@@ -23,18 +23,18 @@ tld_pat = r"\.[a-z]+(?:/|$)"
 tld_re = re.compile(tld_pat)
  
 ########################################################################################
-def extension_features(df, columns):
+def extension_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
         calculate the extension features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_extension_features(rez, col)
+        rez = add_extension_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
-def add_extension_features(df, col):
+def add_extension_features(df, col, add_prefix=True):
     """
         Given a pandas dataframe and a column name.
         add simple text match features for extension.
@@ -54,7 +54,13 @@ def add_extension_features(df, col):
                 freq, type = top_level_domain_lookup(temp)
         return freq, type
 
-    df[[ col+'_tld_freq', col+'_tld_type' ]] = df.apply(ext_features, col=col, axis=1, result_type="expand")
+
+    if add_prefix:
+        col_names = [ col+'_tld_freq', col+'_tld_type' ]
+    else:
+        col_names = [ 'tld_freq', 'tld_type' ]
+
+    df[ col_names ] = df.apply(ext_features, col=col, axis=1, result_type="expand")
 
     return df
  

### 2022-09-28 url2features/featurize.py

@@ -6,6 +6,7 @@ import numpy as np
 from .process import start_profile
 from .process import end_profile
 from .simple import simple_features
+from .protocol import protocol_features
 from .domain import domain_features
 from .extension import extension_features
 from .file import file_features
@@ -20,21 +21,26 @@ def process_df(df, params):
     process_df: Function that co-ordinates the process of generating the features
     
     """ 
+    add_prefix = params["prefix"]
     if params["simple"] :
         start_profile("simple")
-        df = simple_features( df, params["columns"] )
+        df = simple_features( df, params["columns"], add_prefix )
         end_profile("simple")
+    if params["protocol"] :
+        start_profile("protocol")
+        df = protocol_features( df, params["columns"], add_prefix )
+        end_profile("protocol")
     if params["file"] :
         start_profile("file")
-        df = file_features( df, params["columns"] )
+        df = file_features( df, params["columns"], add_prefix )
         end_profile("file")
     if params["domain"] :
         start_profile("domain")
-        df = domain_features( df, params["columns"] )
+        df = domain_features( df, params["columns"], add_prefix )
         end_profile("domain")
     if params["extension"] :
         start_profile("extension")
-        df = extension_features( df, params["columns"] )
+        df = extension_features( df, params["columns"], add_prefix )
         end_profile("extension")
     return df
 

### 2022-09-28 url2features/file.py

@@ -16,18 +16,18 @@ from .process import load_dictionary
 extension_types = load_dictionary('file_extensions.dat')
 
 ########################################################################################
-def file_features(df, columns):
+def file_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
         calculate the file type summary features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_file_features(rez, col)
+        rez = add_file_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
-def add_file_features(df, col):
+def add_file_features(df, col, add_prefix):
     """
         Given a pandas dataframe and a column name.
         calculate the file features 
@@ -42,9 +42,15 @@ def add_file_features(df, col):
             if len(sections) > 1:
                 ext = sections[1]
                 type = file_extension_lookup(ext)
+            
         return ext, type
 
-    df[[ col+'_file_extension', col+'_file_ext_type' ]] = df.apply(get_file_features, col=col, axis=1, result_type="expand")
+    if add_prefix:
+        col_names = [ col+'_file_extn', col+'_file_extn_type' ] 
+    else:
+        col_names = [ 'file_extn', 'file_extn_type' ]
+
+    df[ col_names ] = df.apply(get_file_features, col=col, axis=1, result_type="expand")
 
     return df
 

### 2022-09-28 url2features/protocol.py

@@ -1,0 +1,95 @@
+# -*- coding: utf-8 -*-
+import pandas as pd 
+import numpy as np
+import math
+import os
+import re
+
+from .process import load_word_list
+
+"""
+    url2features.protocol: Feature from URL protocol
+"""
+
+########################################################################################
+def protocol_features(df, columns, add_prefix=True):
+    """
+        Given a pandas dataframe and a set of column names.
+        calculate the simple text summary features and add them.
+    """
+    rez = df.copy()
+    for col in columns:
+        rez = add_protocol_features(rez, col, add_prefix)
+    return rez
+
+########################################################################################
+def add_protocol_features(df, col, add_prefix):
+    """
+        Given a pandas dataframe and a column name.
+        calculate the protocol features 
+    """
+    def extract_protocol(x):
+       parts = x.split("://")
+       if len(parts)>1:
+          return parts[0]
+       else:
+          return "None"
+
+    prots = df[col].apply(extract_protocol)
+    if add_prefix:
+        col_name = col + "_protocol"
+    else:
+        col_name = "protocol"
+    df[col_name] = prots
+
+
+    def get_protocol_type(prot):
+       if prot in ['http','https','shttp']:
+          return "web"
+       elif  prot in ['file','ftp','smb','sftp','s3']:
+          return "file"
+       elif prot in ['pop', 'smtp', 'imap']:
+          return "mail"
+       elif prot in ['nntp',]:
+          return "discussion"
+       elif prot in ['mms','lastfm','udp','rtsp','rtmfp']:
+          return "media"
+       elif prot in ['ldap','snmp','rsync']:
+          return "util"
+       elif prot in ['telnet','ssh']:
+          return "terminal"
+       elif prot in ['irc', 'irc6','ircs', 'rtmp']:
+          return "chat"
+       elif prot in ['ipps','ipp']:
+          return "print"
+       elif prot in ['steam','teamspeak']:
+          return "gaming"
+       elif prot in ['git','cvs','svn']:
+          return "src"
+       else:
+           return "unkown"
+
+    if add_prefix:
+        col_name = col + "_protocol_type"
+    else:
+        col_name = "protocol_type"
+    types = [get_protocol_type(p) for p in prots]
+    df[col_name] = types
+
+    def secure_protocol(prot):
+       if prot in ['sftp','https','shttp','ssh', 'ircs','ipps']:
+          return 1
+       else:
+          return 0
+
+    if add_prefix:
+        col_name = col + "_protocol_secure"
+    else:
[…]

### 2022-09-28 url2features/simple.py

@@ -16,18 +16,18 @@ from .process import load_word_list
 """
 
 ########################################################################################
-def simple_features(df, columns):
+def simple_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
         calculate the simple text summary features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_simple_features(rez, col)
+        rez = add_simple_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
-def add_simple_features(df, col):
+def add_simple_features(df, col, add_prefix=True):
     """
         Given a pandas dataframe and a column name.
         calculate the simple features 

### 2022-09-28 url2features/featurize.py
Adding component existance features and improving simple

@@ -10,6 +10,7 @@ from .protocol import protocol_features
 from .domain import domain_features
 from .extension import extension_features
 from .file import file_features
+from .dns import dns_features
 
 """
     url2features.featurize: Core functions to apply a set of features to a data frame.
@@ -42,6 +43,10 @@ def process_df(df, params):
         start_profile("extension")
         df = extension_features( df, params["columns"], add_prefix )
         end_profile("extension")
+    if params["dns"] :
+        start_profile("dns")
+        df = dns_features( df, params["columns"], add_prefix )
+        end_profile("dns")
     return df
 
 ########################################################################################

### 2022-09-28 url2features/file.py

@@ -35,6 +35,7 @@ def add_file_features(df, col, add_prefix):
     def get_file_features(x, col):
         ext = ""
         type = ""
+        existance = 0
         if x[col]==x[col]:
             url = (x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
@@ -42,13 +43,13 @@ def add_file_features(df, col, add_prefix):
             if len(sections) > 1:
                 ext = sections[1]
                 type = file_extension_lookup(ext)
-            
-        return ext, type
+                existance = 1
+        return ext, type, existance
 
     if add_prefix:
-        col_names = [ col+'_file_extn', col+'_file_extn_type' ] 
+        col_names = [ col+'_file_extn', col+'_file_extn_type', col+'_file_extn_exists', ] 
     else:
-        col_names = [ 'file_extn', 'file_extn_type' ]
+        col_names = [ 'file_extn', 'file_extn_type', 'file_extn_exists' ]
 
     df[ col_names ] = df.apply(get_file_features, col=col, axis=1, result_type="expand")
 

### 2022-09-28 url2features/protocol.py

@@ -42,6 +42,12 @@ def add_protocol_features(df, col, add_prefix):
         col_name = "protocol"
     df[col_name] = prots
 
+    if add_prefix:
+        col_name = col + "_protocol_exists"
+    else:
+        col_name = "protocol_exists"
+    existance = [int(p!="None") for p in prots]
+    df[col_name] = existance
 
     def get_protocol_type(prot):
        if prot in ['http','https','shttp']:

### 2022-09-28 url2features/simple.py

@@ -1,6 +1,7 @@
 # -*- coding: utf-8 -*-
 import pandas as pd 
 import numpy as np
+import string
 import math
 import os
 import re
@@ -32,10 +33,28 @@ def add_simple_features(df, col, add_prefix=True):
         Given a pandas dataframe and a column name.
         calculate the simple features 
     """
-    col_name = col + "_length"
-    df[col_name] = df[col].apply(null_tolerant_len)
-    col_name = col + "_depth"
-    df[col_name] = df[col].apply(null_tolerant_depth)
+
+    count = lambda l1,l2: sum([1 for x in l1 if x in l2])
+
+    def simp_feats(x, col):
+        if x[col]!=x[col]:
+            length = -1
+            punct = -1
+            numeric = -1
+            capital = -1
+        else:
+            length = len(x[col])
+            punct = count(x[col], string.punctuation)/length
+            numeric = count(x[col], string.digits)/length
+            capital = sum(1 for c in x[col] if c.isupper())/length
+        return length, punct, numeric, capital
+
+    if add_prefix:
+        col_names = [col+"_length", col+"_punct", col+"_numeric", col+"_capital"]
+    else:
+        col_names = ["url_length","url_punct", "url_numeric", "url_capital"]
+
+    df[ col_names ] = df.apply(simp_feats, col=col, axis=1, result_type="expand")
 
     return df
 

### 2022-09-28 data/sets/WebKb_4Unis/process.py
Data processing for experiments and refs

@@ -1,0 +1,30 @@
+from os.path import isfile, join
+import pandas as pd
+import numpy as np
+import os
+
+rez = pd.DataFrame(columns=['URL','label'])
+
+dir = "webkb"
+
+cat_dirs = [f for f in os.listdir(dir) if not isfile(join(dir,f))]
+
+def clean_url(url):
+   url = url.replace("/", ":")
+   url = url.replace("^", "/")
+   return url
+
+for cat in cat_dirs:
+   mypath = join(dir,cat)
+   files = []
+   for (dirpath, dirnames, filenames) in os.walk(mypath):
+      myfiles = [f for f in filenames if (f!=".DS_Store")]
+      files.extend(myfiles)
+   
+   labels = [cat for f in files]
+   urls = [clean_url(s) for s in files]
+   temp = pd.DataFrame({"URL":urls, "label":labels})
+   rez = rez.append(temp, ignore_index=True)
+
+rez.to_csv("webkb.csv", index=False, header=True)
+

### 2022-09-28 tests/test_functions.py
Fixing failing test

@@ -36,9 +36,9 @@ def test_simple():
     assert rez["url_length"][0] == 18
     assert rez["url_length"][1] == 19
     assert rez["url_length"][2] == 11
-    assert rez["url_depth"][0] == 1
-    assert rez["url_depth"][1] == 1
-    assert rez["url_depth"][2] == 1
+    assert rez["url_path_depth"][0] == 1
+    assert rez["url_path_depth"][1] == 1
+    assert rez["url_path_depth"][2] == 1
 
 def test_domain_features():
     freq, type = top_level_domain_lookup("com")
@@ -72,7 +72,7 @@ def test_file_extension_lookup():
 
 
 def test_country_lookup_from_url():
-    # THIS TEST ONLY WORKS WITH INTERNET (NOT IN GITHUB)
+    # THIS TEST ONLY WORKS WITH INTERNET (NOT INSIDE THE GITHUB ACTION)
     #url = "www.australia.gov.au"
     #country = get_country(url)
     #assert country == "AU"

### 2022-09-28 url2features/simple.py

@@ -42,17 +42,19 @@ def add_simple_features(df, col, add_prefix=True):
             punct = -1
             numeric = -1
             capital = -1
+            depth = -1
         else:
             length = len(x[col])
             punct = count(x[col], string.punctuation)/length
             numeric = count(x[col], string.digits)/length
             capital = sum(1 for c in x[col] if c.isupper())/length
-        return length, punct, numeric, capital
+            depth = null_tolerant_depth(x[col])
+        return length, punct, numeric, capital, depth
 
     if add_prefix:
-        col_names = [col+"_length", col+"_punct", col+"_numeric", col+"_capital"]
+        col_names = [col+"_length", col+"_punct", col+"_numeric", col+"_capital", col+"_path_depth"]
     else:
-        col_names = ["url_length","url_punct", "url_numeric", "url_capital"]
+        col_names = ["url_length","url_punct", "url_numeric", "url_capital", "path_depth"]
 
     df[ col_names ] = df.apply(simp_feats, col=col, axis=1, result_type="expand")
 

### 2022-09-29 url2features/cli.py
Adding URL parameter features

@@ -60,6 +60,7 @@ def get_cmd_line_params(argv):
               "domain":False, 
               "extension":False, 
               "file":False, 
+              "params":False, 
               "dns":False, 
     }
     for o in options:
@@ -76,6 +77,8 @@ def get_cmd_line_params(argv):
             result["extension"]=True
         if parts[0] == "-file":
             result["file"]=True
+        if parts[0] == "-params":
+            result["params"]=True
         if parts[0] == "-dns":
             result["dns"]=True
         if parts[0] == "-columns":
@@ -97,9 +100,10 @@ def print_usage(args):
     print("  -columns=<COMMA SEPARATED LIST>. REQUIRED")
     print("  -simple            Default: False. Features derived from the URL string: length, depth, components")
     print("  -domain            Default: False. Features from the domain registration (requires internet).")
-    print("  -extension         Default: False. Features about the domain extension and structure.")
+    print("  -extension         Default: False. Features about the domain extension, top level domain (TLD)")
     print("  -protocol          Default: False. Features from the URL protocol.")
     print("  -file              Default: False. Features derived from the final file type")
+    print("  -params            Default: False. Features derived from any query string parameters in the URL")
     print("  -dns               Default: False. Features derived from the DNS records (requires internet).")
     print("  -np                Deactivate use of column name prefix. Only works for a single column.")
     print("")

### 2022-09-29 url2features/domain.py

@@ -37,7 +37,7 @@ def domain_features(df, columns, add_prefix=True):
 ########################################################################################
 def extract_full_domain(url):
     url = url.strip()
-    prot = re.findall("https?://", url)
+    prot = re.findall("^[a-zA-Z][a-zA-Z]*://", url)
     if len(prot)>0:
         url = url[len(prot[0]):]
     parts = url.split("/")
@@ -63,7 +63,34 @@ def get_subdomain_freq(sub):
         return subdomain_freqs[sub]
     else:
         return 0.0
-    
+
+########################################################################################
+def domain_is_ip(domain):
+    """
+    Function to detect if a string is an IP address rather than a domain name
+    Srtictly speaking this function should be more restrictive -- To test if the sequence
+     of numbers is a real IP. But for our purposes even a malformed IP should be flagged
+     as an IP address.
+    """
+    if domain.replace(".", "").isdecimal():
+        return 1
+    elif domain.count(':')>1:
+        return 1
+    else:
+        return 0
+
+########################################################################################
+def domain_has_port(domain):
+    """
+    Function to detect if a domain string contains a port number
+    """
+    if domain.count(':')==1:
+        return 1
+    elif domain.count(']:') == 1:
+        return 1
+    else:
+        return 0
+
 ########################################################################################
 def add_domain_features(df, col, add_prefix=True):
     """
@@ -78,11 +105,15 @@ def add_domain_features(df, col, add_prefix=True):
 
     def dom_features(x, col):
         if x[col]!=x[col]:
-            secs = 0
+            is_ip = -1
+            has_port = -1
+            secs = -1
             sub_type = -1
             sub_freq = -1
         else:
             domain = extract_full_domain(x[col])
+            is_ip = domain_is_ip(domain)
+            has_port = domain_has_port(domain)
             parts = domain.split(".")
             secs = len(parts)
             prime, suffix = split_domain_and_suffix(domain)
@@ -98,12 +129,13 @@ def add_domain_features(df, col, add_prefix=True):
                 reg_dom = domain
             reg_year = get_registration_year(reg_dom)
 
-        return secs, sub_type, sub_freq, reg_year
+        return secs, is_ip, has_port, sub_type, sub_freq, reg_year
 
     if add_prefix:
[…]

### 2022-09-29 url2features/featurize.py

@@ -10,6 +10,7 @@ from .protocol import protocol_features
 from .domain import domain_features
 from .extension import extension_features
 from .file import file_features
+from .params import params_features
 from .dns import dns_features
 
 """
@@ -31,10 +32,6 @@ def process_df(df, params):
         start_profile("protocol")
         df = protocol_features( df, params["columns"], add_prefix )
         end_profile("protocol")
-    if params["file"] :
-        start_profile("file")
-        df = file_features( df, params["columns"], add_prefix )
-        end_profile("file")
     if params["domain"] :
         start_profile("domain")
         df = domain_features( df, params["columns"], add_prefix )
@@ -43,6 +40,14 @@ def process_df(df, params):
         start_profile("extension")
         df = extension_features( df, params["columns"], add_prefix )
         end_profile("extension")
+    if params["file"] :
+        start_profile("file")
+        df = file_features( df, params["columns"], add_prefix )
+        end_profile("file")
+    if params["params"] :
+        start_profile("params")
+        df = params_features( df, params["columns"], add_prefix )
+        end_profile("params")
     if params["dns"] :
         start_profile("dns")
         df = dns_features( df, params["columns"], add_prefix )

### 2022-09-29 url2features/params.py

@@ -1,0 +1,80 @@
+# -*- coding: utf-8 -*-
+from urllib import parse
+import pkg_resources
+import pandas as pd
+import numpy as np
+import math
+import os
+import re
+
+
+"""
+    url2features.params: Features based on the any params in the URL string
+"""
+from .process import load_dictionary
+
+
+########################################################################################
+def params_features(df, columns, add_prefix=True):
+    """
+        Given a pandas dataframe and a set of column names.
+        calculate the params summary features and add them.
+    """
+    rez = df.copy()
+    for col in columns:
+        rez = add_params_features(rez, col, add_prefix)
+    return rez
+
+
+
+########################################################################################
+regex = r'('
+regex += r'(?:[A-Z][A-Z]+:\/\/)?'
+regex += r'('
+regex += r'(?:(?:[A-Z0-9][A-Z0-9-]{0,61}[A-Z0-9]\.)+)'
+regex += r'|(?:\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})'
+regex += r'|(?:([A-Z0-9]{2,4}:){3,12}[A-Z0-9]{2,4})'
+regex += r')'
+regex += r'(?::(\d{1,5}))?'
+regex += r'(?:(\/\S+)*)'
+regex += r')'
+find_urls_in_string = re.compile(regex, re.IGNORECASE)
+
+def detect_embedded_url(x):
+    url = find_urls_in_string.search(x)
+    if url is not None and url.group(0) is not None:
+       return 1
+    else:
+       return 0
+
+########################################################################################
+def add_params_features(df, col, add_prefix):
+    """
+        Given a pandas dataframe and a column name.
+        calculate the params features 
+    """
+    def get_params_features(x, col):
+        f_length = 0
+        p_length = 0
+        p_count = 0
+        p_has_url = 0
+        if x[col]==x[col]:
+            url = (x[col])
+            protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
+            f_length = len(fragment)
+            p_length = len(query)
+            if p_length>0:
+               param_set = query.split("&")
+               p_count = len(param_set)
+               p_has_url = detect_embedded_url(query)
+        return f_length, p_length, p_count, p_has_url
+
+    if add_prefix:
+        col_names = [ col+"_frag_len", col+"_params_len", col+"_params_count", col+"_params_has_url" ] 
+    else:
[…]

### 2022-09-29 data/sets/ISCX-URL2016/process.py
Data processing for ISCX-URL2016 data

@@ -1,0 +1,20 @@
+import pandas as pd
+import numpy as np
+import os
+
+benign = pd.read_csv("FinalDataset/URL/Benign_list_big_final.csv", header=None, names=['URL'])
+phishing = pd.read_csv("FinalDataset/URL/phishing_dataset.csv", header=None, names=['URL'])
+malware = pd.read_csv("FinalDataset/URL/Malware_dataset.csv", header=None, names=['URL'])
+benign['label']=0
+phishing['label']=1
+malware['label']=1
+
+malware_df = benign.append(malware, ignore_index=True)
+malware_df.sort_values(by="URL",inplace=True)
+malware_df.to_csv("malware_dataset.csv",header=True,index=False)
+
+phish_df = benign.append(phishing, ignore_index=True)
+phish_df.sort_values(by="URL",inplace=True)
+phish_df.to_csv("phishing_dataset.csv",header=True,index=False)
+
+

### 2022-09-29 url2features/params.py
Adding additional URL param features

@@ -48,6 +48,20 @@ def detect_embedded_url(x):
        return 0
 
 ########################################################################################
+def detect_encoded_link(x):
+    return x.count("%3A%2F%2F")
+
+########################################################################################
+enc_chars_in_string = re.compile(r'(%[0-9A-F][0-9A-F])')
+def detect_encoded_chars(x):
+    url = enc_chars_in_string.search(x)
+    if url is not None and url.group(0) is not None:
+       return 1
+    else:
+       return 0
+
+
+########################################################################################
 def add_params_features(df, col, add_prefix):
     """
         Given a pandas dataframe and a column name.
@@ -58,6 +72,8 @@ def add_params_features(df, col, add_prefix):
         p_length = 0
         p_count = 0
         p_has_url = 0
+        p_enc_url = 0
+        p_enc_char = 0
         if x[col]==x[col]:
             url = (x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
@@ -67,12 +83,15 @@ def add_params_features(df, col, add_prefix):
                param_set = query.split("&")
                p_count = len(param_set)
                p_has_url = detect_embedded_url(query)
-        return f_length, p_length, p_count, p_has_url
+               p_enc_url = detect_encoded_link(query)
+               p_enc_char = detect_encoded_chars(query)
+        return f_length, p_length, p_count, p_has_url, p_enc_url, p_enc_char 
 
     if add_prefix:
-        col_names = [ col+"_frag_len", col+"_params_len", col+"_params_count", col+"_params_has_url" ] 
+        col_names = [ col+"_frag_len", col+"_params_len", col+"_params_count", 
+                      col+"_params_has_url", col+"params_enc_url", col+"params_enc_char" ] 
     else:
-        col_names = [ "frag_len", "params_len", "params_count", "params_has_url" ]
+        col_names = [ "frag_len", "params_len", "params_count", "params_has_url", "params_enc_url", "params_enc_char" ]
 
     df[ col_names ] = df.apply(get_params_features, col=col, axis=1, result_type="expand")
 

### 2022-09-29 url2features/pipeline.py
Adding missing features to pipeline

@@ -54,15 +54,27 @@ class URLTransform(TransformerMixin, BaseEstimator):
         result = {
               "columns":columns,
               "simple":False,
+              "protocol":False,
               "domain":False,
               "extension":False,
+              "file":False,
+              "params":False,
+              "dns":False,
         }
         if "simple" in params:
            result["simple"]=True
+        if "protocol":
+           result["protocol"]=True
         if "domain" in params:
            result["domain"]=True
         if "extension" in params:
            result["extension"]=True
+        if "file" in params:
+           result["file"]=True
+        if "params" in params:
+           result["params"]=True
+        if "dns" in params:
+           result["dns"]=True
 
         return result
 

### 2022-09-29 setup.py
Adding missing requirements to package

@@ -19,7 +19,7 @@ setup(
       name = "url2features",
       packages = ["url2features"],
       install_requires=[
-        'pandas','numpy','sklearn','whois'
+        'pandas','numpy','sklearn','whois','dnspython','geocoder'
       ],
       include_package_data=True,
       entry_points = {
@@ -31,7 +31,7 @@ setup(
       long_description_content_type='text/markdown',
       author = "John Hawkins",
       author_email = "johnc@getting-data-science-done.com",
-      url = "http://john-hawkins.github.io",
+      url = "http://getting-data-science-done.com",
       project_urls = {
           'Documentation': "http://url2features.readthedocs.io",
           'Source': 'https://github.com/getting-data-science-done/url2features',

### 2022-09-29 paper/paper.tex
reference add
Fleshing out experiments for paper

@@
 
-\begin{table}
-  \caption{Attention Measurement Model - Aggregate Error}
-  \label{tab:atm}
-\begin{tabular}{|l|r|r|}
-\toprule
-Metric                  &Banner       &MREC       \\
-\midrule
-Aggregate MAE           &10.5 ms      &12.5 ms    \\
-95\% Upper Bound        &19.0 ms      &20.6 ms    \\
-95\% Lower Bound        &-22.8 ms     &-31.1 ms   \\
-  \bottomrule
-\end{tabular}
-\end{table}
+We design a feature extraction library for URLs that is sensitive to the various sections of URL
+structure outlined above. We then apply this library to multiple machine learning tasks using only URLs
+as the input variable. We experiment with multiple standard machine learning techniques and evaluate
+the impact of the URL features using the SHAP package for feature importance.
 
-The signals collected along with the eye tracking data allow us to build and deploy an
-attention measurment model that can predict the attention time paid to
-specific ad units within a page. The attention model can
-be applied to all digital inventory that accepts the javascript tag.
+\subsection{Features}
 
-Our model evaluation process focuses on the accuracy of measuring mean
-attention time for a specific ad format, over varying samples of inventory.
-To generate the performance statistics we run bootstrap sampling of the test data
-to look at the expected error when predicting the mean attention time over
-impressions for a specific ad format. Each metric is calculated by taking 50 impression
-samples 2000 times, and using the resulting distribution of mean error.
-The mean attention time measurement performance is summarised in Table
-\ref{tab:atm}.
-We see that the aggregate mean absolute error (MAE) for both formats is very low
-at $10.5 ms$ and $12.5 ms$ for banners and MRECs respectively. Furthermore, the
-$95\%$ confidence intervals for these values is tightly constrained to be well under
-$50 ms$ either side of the true value.
-We apply this attention measurement model across large scale digitial inventory to
-collect a data set of attention time paid to a range of advertisments over time.
-We use these attention measured impressions to investigate the
-impact of contextual categories of media on the attention paid to advertising.
+The features generated by the url2feature package are summaize in Table \ref{tab:features}
 
@@
 present internet classification problems containing URLs as a key, or sole feature.
-Malcious URL classification \cite{Mamun2016}.
-
-4 Universities data http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-20/www/data/
+The IS Malcious URL classification dataset contains both malware and phishing URLS 
+that need to be discriminated against benign URLS\cite{Mamun2016}.
+The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
+range of university URLs categorised into multiple topic categories\cite{Craven1998}.
+These 3 URL classification problems are summarised in Table \ref{tab:data}
 
@@
 \caption{Datasets}
-\label{tab:dataset}
+\label{tab:data}
 \begin{tabular}{|l|r|r|}
 \toprule
-Metric          &Feb 18 - 24    &Feb 25 - March 03          \\
+Dataset        &Records        &Classes  \\
 \midrule
-Impressions     &16,895,661     &10,488,816     \\
-URLS            &26,006         &27,855         \\
-Domains         &2,263          &2,585          \\
-Creatives       &683            &683            \\
-Advertisers     &59             &59             \\
+Malware        &               &2        \\
+Phishing       &               &2        \\
+WebKb 4Uni     &               &7        \\
 \bottomrule

### 2022-09-29 RUN_EXPERIMENTS.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+
+python experiments/malware/00_analysis.py
+python experiments/malware/01_baseline.py
+python experiments/malware/02_log_regression.py
+python experiments/malware/03_extra_trees.py
+python experiments/malware/04_lgbm.py
+
+python experiments/phishing/00_analysis.py
+python experiments/phishing/01_baseline.py
+python experiments/phishing/02_log_regression.py
+python experiments/phishing/03_extra_trees.py
+python experiments/phishing/04_lgbm.py
+
+python experiments/webkb/00_analysis.py
+python experiments/webkb/01_baseline.py
+python experiments/webkb/02_log_regression.py
+python experiments/webkb/03_extra_trees.py
+python experiments/webkb/04_lgbm.py
+
+python experiments/tabulate_results.py
+

### 2022-09-29 paper/paper.tex
Paper development

@@
 Many data science problems require processing log data derived from web pages, apis or other
-internet traffice sources. URLs are one of the few universal pieces of information that describe
-internet activity, hence URLs require effective processing for a wide variety of machine 
+internet traffic sources. URLs are one of the few ubiquitous data fields that describe
+internet activity, hence they require effective processing for a wide variety of machine 
 learning applications. While URLs are structurally rich, they are not subject
@@
 We share an open source implementation of these ideas and demonstrate their utility across a range of 
-internet traffic machine learning problems.
+internet traffic machine learning problems. Python package available at https://pypi.org/project/url2features
 \end{abstract}
@@
 \cite{Sountharrajan2020}
+
+\cite{Murthy2022}
 Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
@@
 The features generated by the url2feature package are summaize in Table \ref{tab:features}
+
+\begin{table*}
+\caption{URL Features}
+\label{tab:features}
+\begin{tabular}{|l|l|l|l|}
+\toprule
+Group         &Feature              &Type        &Definition  \\
+\midrule
+Protocol      &protocol\_name        &Category    &The exact protocol name    \\
+              &protocol\_type        &Category    &Protocol categorised by purpose    \\
+              &protocol\_exists      &Boolean     &Flag indicating presence of protocol   \\
+\midrule
+Host          &host\_is\_ip           &Boolean     &Flag indicating if the host is an IP address    \\
+              &ext\_type             &Category    &TLD extension categorised by purpose    \\
+              &ext\_freq             &Boolean     &TLD extension frequency in internet traffic   \\
+\midrule
+Path          &path\_depth           &Numeric     &The number of forward slashes    \\
+              &path\_words           &Numeric     &Count of distinct words    \\
+\midrule
+File          &file\_ext             &Category    &The exact file extension e.g. "exe" or "php"    \\
+              &file\_type            &Category    &File extension categorised by function \& purpose    \\
+              &file\_ext\_exists      &Boolean     &Flag indicating presence of protocol   \\
+\midrule
+Params        &name                 &Category    &The exact protocol name    \\
+              &type                 &Category    &Protocol categorised by purpose    \\
+              &exists               &Boolean     &Flag indicating presence of protocol   \\
+\bottomrule
+\end{tabular}
+\end{table*}
+
+These URL feature functions are all available in the open source python package \emph{url2features}
+available at https://pypi.org/project/url2features with links to usage documentation and source
+code.
 
@@
 
-\subsection{Contextual Categorisation}
-
-Verity had returned the
-highest score and converted that category into a set of labels for
-classification across the four Tiers of iAB V2.0. In instances where the
-classified category is from a higher position in the hierarchy, then the
-lower level tiers are given the deepest category. For example, if we have
-a URL that is classified as iABv2 category "Business and Finance"
-(a Tier 1 category) then Tiers 2, 3 and 4 will also contain the same value.
-
-Alternatively, if we have another URL that is classified as "Marketing and Advertising"
-(a Tier3 category below "Business and Finance"), then the hierarchical labels
-would be assigned as follows:
-
-\begin{itemize}
-    \item {\texttt{Tier 1}}: ["Business and Finance"]
-    \item {\texttt{Tier 2}}: ["Business"]
-    \item {\texttt{Tier 3}}: ["Marketing and Advertising"]
-    \item {\texttt{Tier 4}}: ["Marketing and Advertising"]
-\end{itemize}
-
-The idea of this scheme is that every page will be assigned a categorisation across
-all four levels in the hierarchy, but sometimes the category at a given Tier
-will not be any more specific than the parent category. This approach ensures
-that comparisons can always be made, and when we look at a deeper level in the hierarchy
-we will have at least as many distinct categories as the parent.
-
-\subsection{Metrics}
-
-The focus of our analysis is to determine whether the performance of each creative,
-in a set of contexts, remains consistent across the two time periods.
-Within each time period we aggregate
-the measured attention time over the impression level data to obtain multiple metrics
-for the reliability of attention time within a given context.
-
-The attention metrics are calculated for a set of impressions $I_p$ in a time period $p$.
-We first define a baseline for a creative $c$ in period $p$ as:
-${}^c\mathcal{A}_p$. This is defined in equation \ref{campaign_baseline}.
+\subsection{Feature Importance}
 
@@
 
-Where the function $A(i)$ returns the attention measured on impression $i$ and
-$\mathbf{1}^c(i)$ is an indicator function that
-tests whether impression $i$ belongs to creative $c$, as shown in equation \ref{indicator}.
-
-\begin{equation}
-\label{indicator}
-  \mathbf{1}^{c}(i):=
-  \begin{cases}1~&{\text{ if }}~i\in c~,\\0~&{\text{ if }}~i\notin c~.\end{cases}
-\end{equation}
-
-Similarly, we denote the baseline attention achieved by ads on pages classified
-as belonging to category $t$ in period $p$ as: ${}_t\mathcal{A}_p$. Defined in
-equation \ref{topic_baseline}. Note, we use the notation $t$ for categories as they
-are equivalent to topics, and this distinguishes them from the creatives.
-
-\begin{equation}
-\label{topic_baseline}
-{}_t\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}_t(i) A(i) }{ \sum_{i \in I_p} \mathbf{1}_t(i) }
-\end{equation}
-
-Where $\mathbf{1}_t(i)$ is an indicator function that
-tests whether impression $i$ was shown on a page classified as category $t$,
-as show in in equation \ref{indicator2}.
-
-\begin{equation}
-\label{indicator2}
-  \mathbf{1}_{t}(i):=
-  \begin{cases}1~&{ i\text{ categorised as }}~t~,\\0~&{\text{ otherwise }}.\end{cases}
-\end{equation}
-
-We denote the mean attention performance for a creative $c$, on media of category $t$
-within period $p$ as ${}^c_t\mathcal{A}_p$.
-This is defined as shown in Equation \ref{mean_attention}.
-
-\begin{equation}
-\label{mean_attention}
-{}^c_t\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}^c_t(i) A(i) }{ \sum_{i \in I_p} \mathbf{1}^c_t(i) }
-\end{equation}
-
-Where we simply apply a indicator function $\mathbf{1}^c_t(i)$ that is a composite
-of Equations \ref{indicator} and \ref{indicator2} to filter for inventory that
-belongs both to creative $c$ and category $t$. These equations should illustrate that we
-make our evaluations by looking at the expected attention time across difference slices
-of the inventory.
-
-\subsection{Analysis}
-
-Our analysis proceeds by ranking all topics that each creative $c$ was exposed
-to according to the value of ${}^c_t\mathcal{A}_1$.
-We then look at the same creatives in period 2 and
-evaluate ${}^c_t\mathcal{A}_2$ for the top three ranking categories from the first period,
-as well as the bottom ranking category.
-This approach necessitates that each creative be exposed to a minimum
-of these same 4 categories in both periods.
-In the results that will follow we report the number
-of records in each trial, reflecting the number of aggregated records
-that fulfills these requirements.
-
-Once we have the datasets in each period that meet these requirements we use multiple metrics
-to evaluate the impact of the contextual categories. Our primary metric is the percentage
-of instances in which the category specific performance ${}^c_t\mathcal{A}_2$ is above the
-creative's baseline expected performance ${}^c\mathcal{A}_1$.
-This is shown as \textbf{\% Over} (the baseline) in the tables of results.
-
-In addition we look at the mean difference between ${}^c_t\mathcal{A}_2$ and ${}^c\mathcal{A}_1$
-over all creatives in the experiment. This is denoted \boldmath$\mu\delta$ (or mean delta) in
-the tables and defined in Equation \ref{delta}
-
-\begin{equation}
-\label{delta}
-\mu\delta = \frac{ \sum_{c \in \mathcal{C}} {}^c_t\mathcal{A}_2 - {}^c\mathcal{A}_1 }{ \mathcal{C} }
-\end{equation}
-
-The mean delta illustrates an expectation of the difference between attention time performance
-and the creative baseline, using a specific contextual targeting strategy. In addition, we show
-that difference expressed as a mean percentage (against the baseline) in the column
-$\mathbf{\mu\%\delta}$. This can be interpreted as the expected percentage increase/decrease
-relative to the creative's baseline attention, when using that contextual targeting strategy.
-
 \section{Results}
-
-We conduct two variations of the experiment, each one looking at different
-criteria for evaluating performance on new inventory.
-These are referred to as the
-\emph{No URL Repeats} and the \emph{No Domain Repeats} experiments.
-
-\subsection{No URL Repeats}
-
-In Table \ref{tab:nourlrepeats} we see the results of looking at performance on novel
-URLs for a creative, where the iAB V2.0 contextual categories of those URLs were present
-in either the top three or last ranking position in the initial period.
-
-\begin{table}
-\caption{Attention Performance by Category Rank on Novel URLs}
-\label{tab:nourlrepeats}
-\begin{tabular}{|l|r|l|r|r|r|}
-\toprule
-Level   &Count    &Rank &\% Over  &$\mu\delta$  &$\mu\%\delta$        \\
-\midrule
-Tier1   &206      &1st  &100.0\%    &4.5         &93.2\%     \\
-        &         &2nd  &96.6\%     &2.6         &49.8\%     \\
-        &         &3rd  &80.6\%     &1.4         &28.7\%     \\
-        &         &Last &0.0\%      &-3.7        &-53.3\%     \\
-Tier2   &210      &1st  &99.5\%     &6.3         &132.0\%     \\
-        &         &2nd  &95.7\%     &3.7         &68.6\%     \\
-        &         &3rd  &80.0\%     &2.4         &41.2\%     \\
-        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
-Tier3   &210      &1st  &99.5\%     &6.4         &135.7\%     \\
-        &         &2nd  &95.7\%     &3.8         &69.5\%     \\
-        &         &3rd  &79.5\%     &2.4         &41.8\%     \\
-        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
-Tier4   &210      &1st  &99.5\%     &6.4         &135.7\%     \\
-        &         &2nd  &95.7\%     &3.8         &69.5\%     \\
-        &         &3rd  &79.5\%     &2.4         &41.8\%     \\
-        &         &Last &0.0\%      &-4.1        &-59.2\%     \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-We see that, in general, targeting pages using categories deeper into the hierarchy
-improves the expected increase in attention through contextual targeting.
-However, the effect appears to plateau at Tier3, likely due to the small proportion of inventory
-that is uniquely classified at a Tier 4 level.
-
-\subsection{No Domain Repeats}
-We repeat the analysis restricting ourselves to impressions in the second period
-that involve URLS for which the domain was not present in the URLs for the first period.
-The results are shown in Table \ref{tab:nodomainrepeats}.
-We note that the number of records has dropped by
-more than half in this experiment, due to the difficulty of finding domains that were
-not present in the first period.
-
-\begin{table}
-\caption{Attention Performance by Category Rank on Novel Domains}
-\label{tab:nodomainrepeats}
-\begin{tabular}{|l|r|l|r|r|r|}
-\toprule
-Level   &Count  &Rank &\% Over  &$\mu\delta$  &$\mu\%\delta$        \\
-\midrule
-Tier1   &86       &1st  &98.8\%     &5.2         &144.3\%     \\
-        &         &2nd  &83.7\%     &2.3         &58.8\%     \\
-        &         &3rd  &60.5\%     &0.4         &26.9\%     \\
-        &         &Last &0.0\%      &-4.1        &-64.5\%     \\
-Tier2   &83       &1st  &96.4\%     &6.4         &159.1\%     \\
-        &         &2nd  &84.3\%     &2.6         &71.0\%     \\
-        &         &3rd  &59.0\%     &0.7         &35.8\%     \\
-        &         &Last &0.0\%      &-4.5        &-70.0\%     \\
-Tier3   &82       &1st  &96.3\%     &6.5         &161.3\%     \\
-        &         &2nd  &84.2\%     &2.7         &71.2\%     \\
-        &         &3rd  &56.1\%     &0.6         &34.7\%     \\
-        &         &Last &0.0\%      &-4.6        &-69.9\%     \\
-Tier4   &82       &1st  &96.3\%     &6.5         &161.3\%     \\
-        &         &2nd  &84.2\%     &2.7         &71.6\%     \\
-        &         &3rd  &56.1\%     &0.6         &34.7\%     \\
-        &         &Last &0.0\%      &-4.6        &-69.9\%     \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The restriction to unique domains in the second period has lifted the expected improvement
-of targeting the top performing category (Tier 3) from 135% to 161%. However, this improvement
-only occurs with the category in ranking position one. For the other ranking positions
-the results are mixed, even though the percentage amount is sometimes higher, the
-absolute amount can be lower, due to the fact that the baseline is calculated on
-the impressions that qualify for inclusion.
-
-These result seems counterintuitive at first glance. Our current hypothesis about why
-this is the case is that it relates to the specificity of the content on a given domain.
-The \emph{no domain repeats} study is biased towards data on less common domains.
-These may have a tendency to be more subject specific.
-These ideas need to be tested in follow up research.
-
-Additionally, we note that the percentage of instances where the category targeting
-delivers an improvement over the baseline drops when we look at unique domains.
-This drop is approximately 3% for rank 1 categories, but by the time we arrive at
-the 3rd ranked category it has dropped from 80% to 56% at Tier 4, meaning that
-targeting new domains with the 3rd ranked category offers a marginally better than
-random chance of delivering improved attention.
 

### 2022-09-30 tests/test_functions.py
adding path features, extending test coverage and fixing issues in file features

@@ -8,6 +8,9 @@ from url2features.process import isNaN
 
 from url2features.dns import get_country
 from url2features.simple import simple_features
+from url2features.path import path_features
+from url2features.file import file_features
+from url2features.params import params_features
 
 from url2features.extension import top_level_domain_lookup
 
@@ -36,9 +39,27 @@ def test_simple():
     assert rez["url_length"][0] == 18
     assert rez["url_length"][1] == 19
     assert rez["url_length"][2] == 11
-    assert rez["url_path_depth"][0] == 1
-    assert rez["url_path_depth"][1] == 1
-    assert rez["url_path_depth"][2] == 1
+
+def test_path():
+    df = pd.DataFrame({
+        "ID":[1,2,3,4,5], 
+        "url":["http://example.com", "http://example.com/","example.com","example.com/this.html","example.com/this/that.html"]
+    })
+    rez =  path_features(df, ["url"])
+    assert rez["url_path_depth"][0] == 0
+    assert rez["url_path_depth"][1] == 0
+    assert rez["url_path_depth"][2] == 0
+    assert rez["url_path_depth"][3] == 1
+    assert rez["url_path_depth"][4] == 2
+
+def test_file():
+    df = pd.DataFrame({
+        "ID":[1,2],
+        "url":["example.com/this.html","example.com/this/that.php"]
+    })
+    rez =  file_features(df, ["url"])
+    assert rez["url_file_extn"][0] == "html"
+    assert rez["url_file_extn"][1] == "php"
 
 def test_domain_features():
     freq, type = top_level_domain_lookup("com")

### 2022-09-30 url2features/cli.py

@@ -59,6 +59,7 @@ def get_cmd_line_params(argv):
               "protocol":False, 
               "domain":False, 
               "extension":False, 
+              "path":False, 
               "file":False, 
               "params":False, 
               "dns":False, 
@@ -75,6 +76,8 @@ def get_cmd_line_params(argv):
             result["domain"]=True
         if parts[0] == "-extension":
             result["extension"]=True
+        if parts[0] == "-path":
+            result["path"]=True
         if parts[0] == "-file":
             result["file"]=True
         if parts[0] == "-params":
@@ -102,6 +105,7 @@ def print_usage(args):
     print("  -domain            Default: False. Features from the domain registration (requires internet).")
     print("  -extension         Default: False. Features about the domain extension, top level domain (TLD)")
     print("  -protocol          Default: False. Features from the URL protocol.")
+    print("  -path              Default: False. Features derived from the path between host and file")
     print("  -file              Default: False. Features derived from the final file type")
     print("  -params            Default: False. Features derived from any query string parameters in the URL")
     print("  -dns               Default: False. Features derived from the DNS records (requires internet).")

### 2022-09-30 url2features/featurize.py

@@ -10,6 +10,7 @@ from .protocol import protocol_features
 from .domain import domain_features
 from .extension import extension_features
 from .file import file_features
+from .path import path_features
 from .params import params_features
 from .dns import dns_features
 
@@ -40,6 +41,10 @@ def process_df(df, params):
         start_profile("extension")
         df = extension_features( df, params["columns"], add_prefix )
         end_profile("extension")
+    if params["path"] :
+        start_profile("path")
+        df = path_features( df, params["columns"], add_prefix )
+        end_profile("path")
     if params["file"] :
         start_profile("file")
         df = file_features( df, params["columns"], add_prefix )

### 2022-09-30 url2features/file.py

@@ -12,6 +12,7 @@ import re
     url2features.file: Features based on the file type.
 """
 from .process import load_dictionary
+from .process import add_protocol_if_missing
 
 extension_types = load_dictionary('file_extensions.dat')
 
@@ -37,9 +38,10 @@ def add_file_features(df, col, add_prefix):
         type = ""
         existance = 0
         if x[col]==x[col]:
-            url = (x[col])
+            url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
             sections = path.split(".")
+            print(sections)
             if len(sections) > 1:
                 ext = sections[1]
                 type = file_extension_lookup(ext)

### 2022-09-30 url2features/params.py

@@ -75,7 +75,7 @@ def add_params_features(df, col, add_prefix):
         p_enc_url = 0
         p_enc_char = 0
         if x[col]==x[col]:
-            url = (x[col])
+            url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
             f_length = len(fragment)
             p_length = len(query)
@@ -85,15 +85,29 @@ def add_params_features(df, col, add_prefix):
                p_has_url = detect_embedded_url(query)
                p_enc_url = detect_encoded_link(query)
                p_enc_char = detect_encoded_chars(query)
-        return f_length, p_length, p_count, p_has_url, p_enc_url, p_enc_char 
+        return p_length, p_count, p_has_url, p_enc_url, p_enc_char, f_length
 
     if add_prefix:
-        col_names = [ col+"_frag_len", col+"_params_len", col+"_params_count", 
-                      col+"_params_has_url", col+"params_enc_url", col+"params_enc_char" ] 
+        col_names = [ col+"_params_len", col+"_params_count", col+"_params_has_url", 
+                      col+"params_enc_url", col+"params_enc_char", col+"params_frag_len" ] 
     else:
-        col_names = [ "frag_len", "params_len", "params_count", "params_has_url", "params_enc_url", "params_enc_char" ]
+        col_names = [ "params_len", "params_count", "params_has_url", 
+                      "params_enc_url", "params_enc_char", "params_frag_len" ]
 
     df[ col_names ] = df.apply(get_params_features, col=col, axis=1, result_type="expand")
 
     return df
+
+###################################################################
+def add_protocol_if_missing(x):
+    """
+    Determine if the URL begins with any form of protocol
+    and add a default protocol if it is absent.
+    """
+    p = re.findall(r"^[a-zA-Z]{2,8}://", x)
+    if len(p) > 0: 
+        return x
+    else:
+        return "http://"+x
+
 

### 2022-09-30 url2features/path.py

@@ -1,0 +1,88 @@
+# -*- coding: utf-8 -*-
+from urllib import parse
+import pkg_resources
+import pandas as pd
+import numpy as np
+import math
+import os
+import re
+
+"""
+    url2features.path: Features based on the URL path between host and file
+"""
+from .process import load_dictionary
+from .process import add_protocol_if_missing
+
+########################################################################################
+def path_features(df, columns, add_prefix=True):
+    """
+        Given a pandas dataframe and a set of column names.
+        calculate the path summary features and add them.
+    """
+    rez = df.copy()
+    for col in columns:
+        rez = add_path_features(rez, col, add_prefix)
+    return rez
+
+
+########################################################################################
+def extract_word_count(path):
+   wds = re.split("[-_/~]+", path)
+   return sum([1 for w in wds if len(w)>2])
+
+
+########################################################################################
+date_in_string = re.compile(r'([0-9]{4}[-_][0-9]{2})|[0-9]{2}[-_][0-9]{4}')
+def contains_date(x):
+    url = date_in_string.search(x)
+    if url is not None and url.group(0) is not None:
+       return 1
+    else:
+       return 0
+
+
+########################################################################################
+def clean_path(path):
+    path = path[1:]
+    if len(path)==0:
+       return path
+    elif path[-1] == "/":
+       return path[0:-1]
+    else:
+       return path
+
+
+########################################################################################
+def add_path_features(df, col, add_prefix):
+    """
+        Given a pandas dataframe and a column name.
+        calculate the path features 
+    """
+    def get_path_features(x, col):
+        p_length = 0
+        p_depth = 0
+        p_words = 0
+        p_has_date = 0
+        p_is_home = 0
+        if x[col]==x[col]:
+            url = add_protocol_if_missing(x[col])
+            protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
+            path = clean_path(path)
+            p_length = len(path)
+            if p_length>0:
+               path_set = path.split("/")
+               p_depth = len(path_set)
+               p_words = extract_word_count(path)
+               p_has_date = contains_date(path)
+               p_is_home = int(path[0] == "~")
+        return p_length, p_depth, p_words, p_has_date, p_is_home 
+
+    if add_prefix:
+        col_names = [ col+"_path_len", col+"_path_depth", col+"_path_words", col+"_path_has_date", col+"_path_is_home" ] 
+    else:
[…]

### 2022-09-30 url2features/process.py

@@ -230,3 +230,18 @@ def remove_escapes_and_non_printable(text):
     pattern = "\0|\n|\r|\b|\t|\f|\v"
     new_text1 = re.sub(pattern, " ", new_text0)
     return new_text1
+
+
+###################################################################
+def add_protocol_if_missing(x):
+    """
+    Determine if the URL begins with any form of protocol
+    and add a default protocol if it is absent.
+    """
+    p = re.findall(r"^[a-zA-Z]{2,8}://", x)
+    if len(p) > 0:
+        return x
+    else:
+        return "http://"+x
+
+

### 2022-09-30 paper/paper.tex
Reorganisation of CLI params and function names, bug fixes and documentation

@@
 Host          &host\_is\_ip           &Boolean     &Flag indicating if the host is an IP address    \\
-              &ext\_type             &Category    &TLD extension categorised by purpose    \\
-              &ext\_freq             &Boolean     &TLD extension frequency in internet traffic   \\
+              &host\_has\_port        &Boolean     &Flag indicating if a port number is explicitly specified    \\
+              &domain\_sections       &Numeric     &Count of period separated domain sections    \\
+              &domain\_reg\_year      &Numeric     &Year in which the domain was initially registered    \\
+              &subdomain\_type        &Category    &Categorisation of the purpose of the subdomain \\
+              &subdomain\_freq        &Numeric     &Frequency of the subdomain in internet traffics    \\
+              &tld\_type              &Category    &TLD extension categorised by purpose    \\
+              &tld\_freq              &Boolean     &TLD extension frequency in internet traffic   \\
 \midrule
@@
               &path\_words            &Numeric     &Count of distinct words    \\
+              &path\_has_date         &Boolean     &Flag indicating if a date is detected in the path  \\
+              &path\_is_home          &Boolean     &Flag indicating if the path starts with a home directorys    \\
 \midrule 
@@
 \midrule
-Params        &name                 &Category    &The exact protocol name    \\
-              &type                 &Category    &Protocol categorised by purpose    \\
-              &exists               &Boolean     &Flag indicating presence of protocol   \\
+Params        &params\_len            &Numeric     &The length of the parameter string    \\
+              &params\_count          &Numeric     &The count of the key value pairs in the param string    \\
+              &params\_has\_url       &Boolean     &Flag indicating presence of a raw URL within the parameter string   \\
+              &params\_enc\_url       &Boolean     &Flag indicating presence of an encoded URL within the parameter string   \\
+              &params\_enc\_char      &Boolean     &Flag indicating presence of an encoded character within the parameter string   \\
+              &params\_frag\_len      &Numeric     &Length of a hash delineated fragement at the end of the parameter string   \\
 \bottomrule
@@
 The data used in this study was collected from a collction of publications that 
-present internet classification problems containing URLs as a key, or sole feature.
-The IS Malcious URL classification dataset contains both malware and phishing URLS 
+present internet classification problems containing URLs as the primary feature.
+The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
 that need to be discriminated against benign URLS\cite{Mamun2016}.
@@
 \midrule
-Malware        &               &2        \\
-Phishing       &               &2        \\
-WebKb 4Uni     &               &7        \\
+Malware        &46,944          &2        \\
+Phishing       &45,343          &2        \\
+WebKb 4Uni     &8,284           &7        \\
 \bottomrule
@@
 \end{table}
+
+We generate all url features for each of these datasets and then apply a range of machine learning
+techniques to build an appropriate classifier.
 

### 2022-09-30 tests/test_functions.py

@@ -12,11 +12,11 @@ from url2features.path import path_features
 from url2features.file import file_features
 from url2features.params import params_features
 
-from url2features.extension import top_level_domain_lookup
+from url2features.tld import top_level_domain_lookup
 
-from url2features.domain import extract_full_domain
-from url2features.domain import get_subdomain_type
-from url2features.domain import get_subdomain_freq
+from url2features.host import extract_full_host
+from url2features.host import get_subdomain_type
+from url2features.host import get_subdomain_freq
 
 from url2features.file import file_extension_lookup
 
@@ -68,7 +68,7 @@ def test_domain_features():
     assert type == 3
 
 def test_domain_extract():
-    dom = extract_full_domain("https://www.smh.com.au/sydney-news")
+    dom = extract_full_host("https://www.smh.com.au/sydney-news")
     assert dom == "www.smh.com.au"
 
 def test_subdomain_type():

### 2022-09-30 url2features/__init__.py

@@ -1,4 +1,4 @@
-__version__ = "0.1.0"
+__version__ = "0.2.0"
 
 from .pipeline import URLTransform
 

### 2022-09-30 url2features/cli.py

@@ -57,8 +57,8 @@ def get_cmd_line_params(argv):
               "prefix":True, 
               "simple":False, 
               "protocol":False, 
-              "domain":False, 
-              "extension":False, 
+              "host":False, 
+              "tld":False, 
               "path":False, 
               "file":False, 
               "params":False, 
@@ -72,10 +72,10 @@ def get_cmd_line_params(argv):
             result["simple"]=True
         if parts[0] == "-protocol":
             result["protocol"]=True
-        if parts[0] == "-domain":
-            result["domain"]=True
-        if parts[0] == "-extension":
-            result["extension"]=True
+        if parts[0] == "-host":
+            result["host"]=True
+        if parts[0] == "-tld":
+            result["tld"]=True
         if parts[0] == "-path":
             result["path"]=True
         if parts[0] == "-file":
@@ -102,8 +102,8 @@ def print_usage(args):
     print(" [ARGS] In most cases these are switches that turn on the feature type")
     print("  -columns=<COMMA SEPARATED LIST>. REQUIRED")
     print("  -simple            Default: False. Features derived from the URL string: length, depth, components")
-    print("  -domain            Default: False. Features from the domain registration (requires internet).")
-    print("  -extension         Default: False. Features about the domain extension, top level domain (TLD)")
+    print("  -host              Default: False. Features about the host including subdoamin and registration (requires internet).")
+    print("  -tld               Default: False. Features about the top level domain (TLD)")
     print("  -protocol          Default: False. Features from the URL protocol.")
     print("  -path              Default: False. Features derived from the path between host and file")
     print("  -file              Default: False. Features derived from the final file type")

### 2022-09-30 url2features/featurize.py

@@ -7,8 +7,8 @@ from .process import start_profile
 from .process import end_profile
 from .simple import simple_features
 from .protocol import protocol_features
-from .domain import domain_features
-from .extension import extension_features
+from .host import host_features
+from .tld import tld_features
 from .file import file_features
 from .path import path_features
 from .params import params_features
@@ -33,14 +33,14 @@ def process_df(df, params):
         start_profile("protocol")
         df = protocol_features( df, params["columns"], add_prefix )
         end_profile("protocol")
-    if params["domain"] :
-        start_profile("domain")
-        df = domain_features( df, params["columns"], add_prefix )
-        end_profile("domain")
-    if params["extension"] :
-        start_profile("extension")
-        df = extension_features( df, params["columns"], add_prefix )
-        end_profile("extension")
+    if params["host"] :
+        start_profile("host")
+        df = host_features( df, params["columns"], add_prefix )
+        end_profile("host")
+    if params["tld"] :
+        start_profile("tld")
+        df = tld_features( df, params["columns"], add_prefix )
+        end_profile("tld")
     if params["path"] :
         start_profile("path")
         df = path_features( df, params["columns"], add_prefix )

### 2022-09-30 url2features/host.py

@@ -7,8 +7,8 @@ import os
 import re
 
 """
-    url2features.domain: Domain domain feature flags
-    Generate features for domains
+    url2features.host: Host feature flags
+    Generate features for host including domain, subdomain elements
 """
 
 from .suffixes import split_domain_and_suffix
@@ -24,18 +24,18 @@ language_codes = ['ab', 'aa', 'af', 'ak', 'sq', 'am', 'ar', 'an', 'hy', 'as', 'a
 
 
 ########################################################################################
-def domain_features(df, columns, add_prefix=True):
+def host_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
-        calculate the domain features and add them.
+        calculate the host features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_domain_features(rez, col, add_prefix)
+        rez = add_host_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
-def extract_full_domain(url):
+def extract_full_host(url):
     url = url.strip()
     prot = re.findall("^[a-zA-Z][a-zA-Z]*://", url)
     if len(prot)>0:
@@ -46,7 +46,6 @@ def extract_full_domain(url):
 
 ########################################################################################
 def get_subdomain_type(sub):
-    #print("FUNCTION CALL: get_subdomain_type(", sub, ")")
     if sub in subdomain_types:
         return subdomain_types[sub]
     elif sub in country_codes:
@@ -58,14 +57,13 @@ def get_subdomain_type(sub):
 
 ########################################################################################
 def get_subdomain_freq(sub):
-    #print("FUNCTION CALL: get_subdomain_freq(", sub, ")")
     if sub in subdomain_freqs:
         return subdomain_freqs[sub]
     else:
         return 0.0
 
 ########################################################################################
-def domain_is_ip(domain):
+def host_is_ip(domain):
     """
     Function to detect if a string is an IP address rather than a domain name
     Srtictly speaking this function should be more restrictive -- To test if the sequence
@@ -80,7 +78,7 @@ def domain_is_ip(domain):
         return 0
 
 ########################################################################################
-def domain_has_port(domain):
+def host_has_port(domain):
     """
     Function to detect if a domain string contains a port number
     """
@@ -92,7 +90,7 @@ def domain_has_port(domain):
         return 0
 
 ########################################################################################
[…]

### 2022-09-30 url2features/pipeline.py

@@ -55,8 +55,9 @@ class URLTransform(TransformerMixin, BaseEstimator):
               "columns":columns,
               "simple":False,
               "protocol":False,
-              "domain":False,
-              "extension":False,
+              "host":False,
+              "tld":False,
+              "path":False,
               "file":False,
               "params":False,
               "dns":False,
@@ -65,10 +66,12 @@ class URLTransform(TransformerMixin, BaseEstimator):
            result["simple"]=True
         if "protocol":
            result["protocol"]=True
-        if "domain" in params:
-           result["domain"]=True
-        if "extension" in params:
-           result["extension"]=True
+        if "host" in params:
+           result["host"]=True
+        if "tld" in params:
+           result["tld"]=True
+        if "path" in params:
+           result["path"]=True
         if "file" in params:
            result["file"]=True
         if "params" in params:

### 2022-09-30 url2features/tld.py

@@ -12,9 +12,9 @@ tld_freqs = load_dictionary('tld_freqs.dat')
 tld_types = load_dictionary('tld_types.dat')
 
 """
-    url2features.extension: Domain extension feature flags
+    url2features.tld: Host Top Level Domain feature flags
 
-    Generate features for common domain extensions
+    Generate features for common domain tlds
 
 """
 
@@ -23,21 +23,21 @@ tld_pat = r"\.[a-z]+(?:/|$)"
 tld_re = re.compile(tld_pat)
  
 ########################################################################################
-def extension_features(df, columns, add_prefix=True):
+def tld_features(df, columns, add_prefix=True):
     """
         Given a pandas dataframe and a set of column names.
-        calculate the extension features and add them.
+        calculate the tld features and add them.
     """
     rez = df.copy()
     for col in columns:
-        rez = add_extension_features(rez, col, add_prefix)
+        rez = add_tld_features(rez, col, add_prefix)
     return rez
 
 ########################################################################################
-def add_extension_features(df, col, add_prefix=True):
+def add_tld_features(df, col, add_prefix=True):
     """
         Given a pandas dataframe and a column name.
-        add simple text match features for extension.
+        add simple text match features for tld.
     """
 
     def ext_features(x, col):

### 2022-10-02 paper/paper.tex
Paper update

--- 2022-09-29 paper/paper.tex
@@
 
-The Uniform Resource Locator (URL) is now a ubiquitous element of modern life. 
+The Uniform Resource Locator (URL) is a ubiquitous element the digital world. 
 We use them to advertise and locate businesses, to retrieve news and media and 
-to interact with other people across a broad of social applications. It should
-be no surprise that processing URLs is key component of many tasks that involve
+to interact with other people across a broad of social applications.
+Processing URLs is key component of many tasks that involve
 analysing internet data. In many applications the URL is the central piece of 
 information available because the demands of the task require immediate analysis.
-Prominent examples include security analysis of potenital phishing attacks\cite{Basnet2014}, 
-detection of potential spam emails \cite{}, and applications to online advertsing
-including anticipation of conversions \cite{Qiu2020} or contextual analysis of
-the content\cite{Kan2005,Baykan2009} or language\cite{Baykan2013} of webpages.
+In applications like malicious wesite detection the URL needs to be processed with
+in a rapid and efficient manner to provide utility\cite{Ma2009b}.
+Common use cases for URL centered analysis include security analysis of potenital phishing 
+attacks\cite{Basnet2014,Mamun2016,Vazhayil2018}, and identification of pages 
+that host malware or viruses \cite{Canali2011,Mamun2016}.
+There are also applications to online advertising
+including anticipation of conversions \cite{Qiu2020}, contextual analysis of
+the content\cite{Kan2005,Baykan2009,Meshkizadeh2010} or language\cite{Baykan2013} of webpages.
 
@@
 
-Multiple data science and machine learning applications on internet data 
-Write a literature review \cite{Vazhayil2018}
-\cite{Canali2011}
+A large amount of recent work on machine learning based on URLs has focused on deep learning approaches that
+learn an embedding representation of the content of the URL. Once of the explicit reasons 
+for this approach is the potential for sensitivity to the sequential structure of the URL.
+\cite{Le2018}
+
+Deep learning approaches include the use of convolutional layers to learn word and character 
+embedings \cite{Le2018},
+
 \cite{Ayes2019}
-\cite{Mamun2016}
 \cite{Li2020}
@@
 \cite{Tupsamudre2019}
-URLnet learns word and charcater embedings \cite{Le2018}
 \cite{Baykan2009}
@@
 \cite{Qiu2020}
-\cite{Vaishnavi2021}
 \cite{Xu2021}
@@
 \cite{Sountharrajan2020}
+\cite{Murthy2022}
 
-\cite{Murthy2022}
 Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
@@
 Common approaches to feature engineering on URLs include string patterns and regular expressions to
-identify key sequences \cite{Kan2004}, n-gram or bag of words models \cite{Baykan2009}, 
+identify key sequences and lexical properties \cite{Kan2004,Mamun2016}, 
+creation of lookup tables or likelihood scores based on key sequences
+\cite{Meshkizadeh2010}, n-gram or bag of words models \cite{Baykan2009}, 
 the generation of task specific embedding vectors\cite{Le2018,Qiu2020} and the
-usage of domain name servers or registrars for ancillary information \cite{}. Some authors have 
-empahsized that URLs are sequences of characters and require features that respect this ordering\cite{Le2018}.
-However, the ordering of key features within URLs is predominantly fixed.
+usage of domain name servers or registrars for ancillary information about the domain registration \cite{Canali2011}. 
+Some authors have 
+emphasized that URLs are sequences of characters and require feature extraction methods that respect 
+this sequential nature\cite{Le2018,Vazhayil2018}. They have naturally turned to developing neural network approaches
+based on convolutional or recurrent layers for learning these sequential structures.
+However, the ordering of key features within URLs is predominantly fixed as shown in Figure \ref{fig:url_structure}.
+The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
+sequences which are built from flexible grammars that allow variable positioning of most key elements.
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.3]{images/URL_parts.png}
+\caption{Structural components of a URL requiring specific feature engineering treatment}
+\label{fig:url_structure}
+\end{figure*}
 
@@
 
-The features generated by the url2feature package are summaize in Table \ref{tab:features}
+The features generated by the url2feature package are summairized in Table \ref{tab:features}
 
@@
 \midrule
-Protocol      &protocol\_name        &Category    &The exact protocol name    \\
-              &protocol\_type        &Category    &Protocol categorised by purpose    \\
-              &protocol\_exists      &Boolean     &Flag indicating presence of protocol   \\
+Protocol      &protocol\_name         &Category    &The exact internet protocol name    \\
+              &protocol\_type         &Category    &Internet protocol categorised by its purpose    \\
+              &protocol\_exists       &Boolean     &Flag indicating presence or absence of internet protocol   \\
 \midrule
 Host          &host\_is\_ip           &Boolean     &Flag indicating if the host is an IP address    \\
-              &ext\_type             &Category    &TLD extension categorised by purpose    \\
-              &ext\_freq             &Boolean     &TLD extension frequency in internet traffic   \\
+              &host\_has\_port        &Boolean     &Flag indicating if a port number is explicitly specified    \\
+              &domain\_sections       &Numeric     &Count of period separated domain sections    \\
+              &domain\_reg\_year      &Numeric     &Year in which the domain was initially registered    \\
+              &subdomain\_type        &Category    &Categorisation of the purpose of the subdomain \\
+              &subdomain\_freq        &Numeric     &Frequency of the subdomain in internet traffics    \\
+              &tld\_type              &Category    &Top Level Domain extension categorised by purpose    \\
+              &tld\_freq              &Boolean     &Top Level Domain extension frequency in internet traffic   \\
 \midrule
-Path          &path\_depth           &Numeric     &The number of forward slashes    \\
-              &path\_words           &Numeric     &Count of distinct words    \\
+Path          &path\_depth            &Numeric     &The depth of the directory path between host and file   \\
+              &path\_words            &Numeric     &Count of distinct words in the path between host and file   \\
+              &path\_has\_date         &Boolean     &Flag indicating if a date is detected in the path  \\
+              &path\_is\_home          &Boolean     &Flag indicating if the path starts with a home directory    \\
 \midrule 
@@
               &file\_type             &Category    &File extension categorised by function \& purpose    \\
-              &file\_ext\_exists      &Boolean     &Flag indicating presence of protocol   \\
+              &file\_ext\_exists      &Boolean     &Flag indicating presence of a file extension for the URL target  \\
 \midrule
-Params        &name                 &Category    &The exact protocol name    \\
-              &type                 &Category    &Protocol categorised by purpose    \\
-              &exists               &Boolean     &Flag indicating presence of protocol   \\
+Params        &params\_len            &Numeric     &The character length of the parameter string    \\
+              &params\_count          &Numeric     &The count of the key value pairs in the param string    \\
+              &params\_has\_url       &Boolean     &Flag indicating presence of a raw URL within the parameter string   \\
+              &params\_enc\_url       &Boolean     &Flag indicating presence of an encoded URL within the parameter string   \\
+              &params\_enc\_char      &Boolean     &Flag indicating presence of an encoded character within the parameter string   \\
+              &params\_frag\_len      &Numeric     &Length of a hash delineated fragement at the end of the parameter string   \\
 \bottomrule
@@
 
+The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
+with \cite{Pazzani1996}
+
 \begin{table}
@@
 \label{tab:data}
-\begin{tabular}{|l|r|r|}
+\begin{tabular}{|l|r|r|r|}
 \toprule
-Dataset        &Records        &Classes  \\
+Dataset              &Records        &Classes  &Majority    \\
 \midrule
-Malware        &               &2        \\
-Phishing       &               &2        \\
-WebKb 4Uni     &               &7        \\
+Malware              &46,944          &2       &            \\
+Phishing             &45,343          &2       &            \\
+WebKb 4Uni           &8,284           &7       &            \\
+DMOZ                 &8,284           &7       &            \\
+Syskill \& Webert     &8,284           &7       &            \\
 \bottomrule

### 2022-10-02 RUN_EXPERIMENTS.sh

@@ -1,4 +1,7 @@
 #!/bin/bash
+#
+#
+#
 
 python experiments/malware/00_analysis.py
 python experiments/malware/01_baseline.py

### 2022-10-02 data/sets/Syskill/process.py
Syskill and Webert data

@@ -1,0 +1,31 @@
+import pandas as pd
+import numpy as np
+import os
+
+cols = ['id','label','url','date','title']
+
+bands = pd.read_csv("SW/Bands/index", header=None, names=cols, sep="|")
+biod = pd.read_csv("SW/BioMedical/index", header=None, names=cols, sep="|")
+goats = pd.read_csv("SW/Goats/index", header=None, names=cols, sep="|")
+sheep = pd.read_csv("SW/Sheep/index", header=None, names=cols, sep="|")
+
+def convert_to_ord(x):
+    if x=='cold': return 0
+    if x=='medium': return 1
+    if x=='hot': return 2
+    return np.nan
+
+bands['rating'] = bands['label'].apply(convert_to_ord)
+biod['rating'] = biod['label'].apply(convert_to_ord)
+goats['rating'] = goats['label'].apply(convert_to_ord)
+sheep['rating'] = sheep['label'].apply(convert_to_ord)
+
+total_df = bands.append(biod, ignore_index=True)
+total_df = total_df.append(goats, ignore_index=True)
+total_df = total_df.append(sheep, ignore_index=True)
+total_df.sort_values(by="url",inplace=True)
+
+store_df = total_df.loc[:,['url','label']]
+store_df.to_csv("dataset.csv",header=True,index=False)
+
+

### 2022-10-03 scripts/clean_dom_reg_data.py
Working on domain registration date scripts

@@ -1,0 +1,41 @@
+# ###################################################################################
+# Domain Registrations Data Clean 
+#
+# Purpose of this script is to clean the dictionary of domain regsitration dates
+# ###################################
+import numpy as np
+import pandas as pd
+import json
+import os
+import sys
+
+dict_file = 'url2features/data/dom_reg.dat' 
+
+####################################################################
+def main():
+    """
+    Main function for processing the datafile to add all the domains
+    to the lookup dictionary
+    """ 
+
+    with open(dict_file, 'r') as file:
+        lookup =  json.loads(file.read())
+
+    delete_list = []
+    mydoms = lookup.keys()
+    for dom in mydoms:
+        if lookup[dom] == "None":
+            print("No entry for ", dom)
+            delete_list.append(dom)
+
+    for dom in delete_list:
+        del lookup[dom]
+
+    with open(dict_file, 'w') as file:
+        file.write(json.dumps(lookup))
+
+#########################################################################
+if __name__ == '__main__':
+
+    main()
+

### 2022-10-03 scripts/update_dom_reg_data.py

@@ -13,29 +13,55 @@ import json
 import whois
 import os
 import sys
-
-oldfile = "../attention-and-context/ranking_analysis/data/URLs.csv"
+import re
 
 dict_file = 'url2features/data/dom_reg.dat' 
+
+common_suffixes = [ '.com', '.net', '.ne.jp', '.de', '.org', '.edu', '.nl', '.info', '.biz', '.co.uk', '.cz', '.dk',
+                    '.com.cn', '.mil', '.ac.uk', '.ch', '.eu', '.com.br', '.co.za', '.ad.jp', '.ac.cn', '.com.au',
+                    '.or.jp', '.net.au', '.asia', '.ac.jp', '.mobi', '.co.jp', '.sk', '.edu.tw', 'edu.au', '.net.pl', '.gov' ]
 
 ####################################################################
 """
 Utility functions used by main()
 """
 def extract_domain(url):
+    url = str(url)
+    url = url.strip()
+    prot = re.findall("^[a-zA-Z][a-zA-Z]*://", url)
+    if len(prot)>0:
+        url = url[len(prot[0]):]
     parts = url.split("/")
-    if len(parts)>1:
-        return parts[0]
-    return url
+    domain = parts[0]
+    return domain
+
 
 def remove_subdomain(url):
-    if url[0:3]=='www':
+    url = str(url)
+    if url[0:4]=='www.':
         return url[4:]
+    if url[0:5]=='www1.':
+        return url[5:]
+    for sfx in common_suffixes:
+       sfl = len(sfx)
+       if url[-sfl:] == sfx:
+           base = url[0:len(url)-sfl]
+           dom = base.split(".")
+           if len(dom)>1:
+               return dom[-1] + sfx
+           else:
+              return url
+    # IF all that fails trim to a 2 part domain
     splitd = url.split(".")
-    while len(splitd)>3:
+    while len(splitd)>2:
         url = url[len(splitd[0])+1:]
         splitd = url.split(".")
     return url
+
+
+def remove_port(url):
+    url = str(url)
+    return re.sub(':[0-9]*', '', url)
 
 ####################################################################
 def main(datafile, urlcol, sep=","):
@@ -49,12 +75,13 @@ def main(datafile, urlcol, sep=","):
         lookup =  json.loads(file.read())
 
     df['domain'] = df[urlcol].apply(extract_domain)
- 
-    df['domain2'] = df['domain'].apply(remove_subdomain)
[…]

### 2022-10-03 RUN_EXPERIMENTS.sh
Working on issues with unusual URLs

@@ -1,25 +1,0 @@
-#!/bin/bash
-#
-#
-#
-
-python experiments/malware/00_analysis.py
-python experiments/malware/01_baseline.py
-python experiments/malware/02_log_regression.py
-python experiments/malware/03_extra_trees.py
-python experiments/malware/04_lgbm.py
-
-python experiments/phishing/00_analysis.py
-python experiments/phishing/01_baseline.py
-python experiments/phishing/02_log_regression.py
-python experiments/phishing/03_extra_trees.py
-python experiments/phishing/04_lgbm.py
-
-python experiments/webkb/00_analysis.py
-python experiments/webkb/01_baseline.py
-python experiments/webkb/02_log_regression.py
-python experiments/webkb/03_extra_trees.py
-python experiments/webkb/04_lgbm.py
-
-python experiments/tabulate_results.py
-

### 2022-10-03 experiments/RUN_EXPERIMENTS.sh

@@ -1,0 +1,28 @@
+#!/bin/bash
+
+python malware/00_analysis.py
+python malware/01_baseline.py
+python malware/02_log_regression.py
+python malware/03_extra_trees.py
+python malware/04_lgbm.py
+
+python phishing/00_analysis.py
+python phishing/01_baseline.py
+python phishing/02_log_regression.py
+python phishing/03_extra_trees.py
+python phishing/04_lgbm.py
+
+python webkb/00_analysis.py
+python webkb/01_baseline.py
+python webkb/02_log_regression.py
+python webkb/03_extra_trees.py
+python webkb/04_lgbm.py
+
+python sw/00_analysis.py
+python sw/01_baseline.py
+python sw/02_log_regression.py
+python sw/03_extra_trees.py
+python sw/04_lgbm.py
+
+python tabulate_results.py
+

### 2022-10-03 url2features/host.py

@@ -3,6 +3,7 @@ import pkg_resources
 import pandas as pd 
 import numpy as np
 import math
+import sys
 import os
 import re
 
@@ -102,16 +103,21 @@ def add_host_features(df, col, add_prefix=True):
     """
 
     def dom_features(x, col):
-        if x[col]!=x[col]:
+        url = str(x[col]).strip()
+        print("URL [%s]"%url)
+        if (url == 'None') or (url == 'nan') or (url==""):
             is_ip = np.nan
             has_port = np.nan
             secs = np.nan
             sub_type = np.nan
             sub_freq = np.nan
+            reg_year = np.nan
         else:
             host = extract_full_host(x[col])
             is_ip = host_is_ip(host)
             has_port = host_has_port(host)
+            if has_port:
+                host, port = extract_port(host)
             parts = host.split(".")
             secs = len(parts)
             if is_ip:

### 2022-10-03 url2features/protocol.py

@@ -29,6 +29,7 @@ def add_protocol_features(df, col, add_prefix):
         calculate the protocol features 
     """
     def extract_protocol(x):
+       x = str(x)
        parts = x.split("://")
        if len(parts)>1:
           return parts[0]

### 2022-10-03 url2features/host.py
Fixing problems with domains containing a port

@@ -45,6 +45,10 @@ def extract_full_host(url):
     domain = parts[0]
     return domain
 
+def remove_port(url):
+    url = str(url)
+    return re.sub(':[0-9]*', '', url)
+
 ########################################################################################
 def get_subdomain_type(sub):
     if sub in subdomain_types:
@@ -117,7 +121,7 @@ def add_host_features(df, col, add_prefix=True):
             is_ip = host_is_ip(host)
             has_port = host_has_port(host)
             if has_port:
-                host, port = extract_port(host)
+                host = remove_port(host)
             parts = host.split(".")
             secs = len(parts)
             if is_ip:

### 2022-10-03 data/sets/Syskill/process.py
Processing update for Syskill

@@ -2,7 +2,7 @@ import pandas as pd
 import numpy as np
 import os
 
-cols = ['id','label','url','date','title']
+cols = ['id','label','URL','date','title']
 
 bands = pd.read_csv("SW/Bands/index", header=None, names=cols, sep="|")
 biod = pd.read_csv("SW/BioMedical/index", header=None, names=cols, sep="|")
@@ -23,9 +23,9 @@ sheep['rating'] = sheep['label'].apply(convert_to_ord)
 total_df = bands.append(biod, ignore_index=True)
 total_df = total_df.append(goats, ignore_index=True)
 total_df = total_df.append(sheep, ignore_index=True)
-total_df.sort_values(by="url",inplace=True)
+total_df.sort_values(by="URL",inplace=True)
 
-store_df = total_df.loc[:,['url','label']]
-store_df.to_csv("dataset.csv",header=True,index=False)
+store_df = total_df.loc[:,['URL','label']]
+store_df.to_csv("syskill_dataset.csv",header=True,index=False)
 
 

### 2022-10-03 url2features/host.py
Fixing bugs with TLD suffix detection

@@ -74,10 +74,12 @@ def host_is_ip(domain):
     Srtictly speaking this function should be more restrictive -- To test if the sequence
      of numbers is a real IP. But for our purposes even a malformed IP should be flagged
      as an IP address.
+    TODO: Add IPV6 Support
     """
-    if domain.replace(".", "").isdecimal():
-        return 1
-    elif domain.count(':')>1:
+    domain = str(domain).strip()
+    temp1 = domain.replace(".", "")
+    temp2 = temp1.replace(":", "")
+    if temp2.isdecimal():
         return 1
     else:
         return 0

### 2022-10-03 url2features/suffixes.py

@@ -29,5 +29,11 @@ def split_domain_and_suffix(domain):
     for suffix in suffixes:
         if domain.endswith(suffix):
             return domain[:-len(suffix)], domain[len(domain)-len(suffix):]
-
+    # Unrecognised suffix
+    parts = domain.split(".")
+    if len(parts)>1:
+        dom = domain[:-(len(parts[-1])+1)]
+        return dom, parts[-1]
+    else:
+        return domain, ""
 

### 2022-10-03 INIT_EXPERIMENTAL_DATA.sh
Data prep for experiments

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/Syskill/dataset.csv  > data/sets/Syskill/syskill_processed.csv
+
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/malware_dataset.csv  >  data/sets/ISCX-URL2016/malware_processed.csv
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/phishing_dataset.csv  >  data/sets/ISCX-URL2016/phishing_processed.csv
+
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/WebKb_4Unis/webkb.csv  > data/sets/WebKb_4Unis/webkb_processed.csv
+
+
+projit add dataset syskill data/sets/Syskillprocessed.csv
+projit add dataset malware data/sets/ISCX-URL2016/malware_dataset_processed.csv
+projit add dataset phishing data/sets/ISCX-URL2016/phishing_dataset_processed.csv
+projit add dataset webkb data/sets/WebKb_4Unis/webkb_processed.csv
+
+

### 2022-10-03 INIT_PROJECT.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+projit init "URL2features Experiments"
+
+

### 2022-10-03 paper/paper.tex
Paper update
Removing debug prints, bug fixes, preparing for experiments. Release 0.3.0

@@
 
-The data used in this study was collected from a collction of publications that 
+The data used in this study was colated from a range of publications that 
 present internet classification problems containing URLs as the primary feature.
@@
 range of university URLs categorised into multiple topic categories\cite{Craven1998}.
-These 3 URL classification problems are summarised in Table \ref{tab:data}
-
 The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
-with \cite{Pazzani1996}
+with a human generated categorisation for determining personal preferences in webpage
+content\cite{Pazzani1996}. These 4 URL classification problems are summarised in Table \ref{tab:data}
 
@@
 \midrule
-Malware              &46,944          &2       &            \\
-Phishing             &45,343          &2       &            \\
-WebKb 4Uni           &8,284           &7       &            \\
-DMOZ                 &8,284           &7       &            \\
-Syskill \& Webert     &8,284           &7       &            \\
+Malware              &46,944          &2       &75\%        \\
+Phishing             &45,343          &2       &78\%        \\
+WebKb 4Uni           &8,284           &7       &45\%        \\
+Syskill \& Webert    &330             &3       &68\%        \\
 \bottomrule
@@
 We generate all url features for each of these datasets and then apply a range of machine learning
-techniques to build an appropriate classifier.
+techniques to build classifiers that can be analysed for key features for each task.
 
@@
 
+\begin{table}
+\caption{Machine Learning Results}
+\label{tab:results}
+\begin{tabular}{|l|r|r|r|r|}
+\toprule
+Dataset              &NB     &LR    &XT    &LGBM     \\
+\midrule
+Malware              &-      &-     &-     &-        \\
+Phishing             &-      &-     &-     &-        \\
+WebKb 4Uni           &-      &-     &-     &-        \\
+Syskill \& Webert    &-      &-     &-     &-        \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section{Conclusion}
+
+We have described the structural elements of a URL from which context specific features can be extracted.
+These feature ideas tend to be used indepednetly within different domains. In this paper we have have 
+collated them into an open source URL feature generation package and then compare their utility across a range
+of indepenent tasks. We have observed that the various structural regions play different roles across 
+these tasks, exhibiting varying levels of importance.
 

### 2022-10-03 INIT_EXPERIMENTAL_DATA.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/Syskill/dataset.csv  > data/sets/Syskill/syskill_processed.csv
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/Syskill/syskill_dataset.csv  > data/sets/Syskill/syskill_processed.csv
 
 ./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/malware_dataset.csv  >  data/sets/ISCX-URL2016/malware_processed.csv
 ./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/phishing_dataset.csv  >  data/sets/ISCX-URL2016/phishing_processed.csv
@@ -8,9 +8,9 @@
 ./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/WebKb_4Unis/webkb.csv  > data/sets/WebKb_4Unis/webkb_processed.csv
 
 
-projit add dataset syskill data/sets/Syskillprocessed.csv
-projit add dataset malware data/sets/ISCX-URL2016/malware_dataset_processed.csv
-projit add dataset phishing data/sets/ISCX-URL2016/phishing_dataset_processed.csv
+projit add dataset syskill data/sets/Syskill/syskill_processed.csv
+projit add dataset malware data/sets/ISCX-URL2016/malware_processed.csv
+projit add dataset phishing data/sets/ISCX-URL2016/phishing_processed.csv
 projit add dataset webkb data/sets/WebKb_4Unis/webkb_processed.csv
 
 

### 2022-10-03 url2features/__init__.py

@@ -1,4 +1,4 @@
-__version__ = "0.2.0"
+__version__ = "0.3.0"
 
 from .pipeline import URLTransform
 

### 2022-10-03 url2features/file.py

@@ -41,7 +41,6 @@ def add_file_features(df, col, add_prefix):
             url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
             sections = path.split(".")
-            print(sections)
             if len(sections) > 1:
                 ext = sections[1]
                 type = file_extension_lookup(ext)

### 2022-10-03 url2features/host.py

@@ -110,7 +110,6 @@ def add_host_features(df, col, add_prefix=True):
 
     def dom_features(x, col):
         url = str(x[col]).strip()
-        print("URL [%s]"%url)
         if (url == 'None') or (url == 'nan') or (url==""):
             is_ip = np.nan
             has_port = np.nan

### 2022-10-04 url2features/file.py
Extending features and bug fixes

@@ -27,6 +27,13 @@ def file_features(df, columns, add_prefix=True):
         rez = add_file_features(rez, col, add_prefix)
     return rez
 
+def remove_extension(file_name):
+    file_parts = file_name.split(".")
+    if len(file_parts) > 1:
+        return file_name[0:-(len(file_parts[-1])+1)]
+    else:
+        return file_name
+
 ########################################################################################
 def add_file_features(df, col, add_prefix):
     """
@@ -37,24 +44,39 @@ def add_file_features(df, col, add_prefix):
         ext = ""
         type = ""
         existance = 0
+        file_len = 0
+        file_wds = 0
+        file_wd_len = 0
         if x[col]==x[col]:
             url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
-            sections = path.split(".")
-            if len(sections) > 1:
-                ext = sections[1]
+            sections = path.split("/")
+            final_file = sections[len(sections)-1]
+            file_len = len(final_file)
+            file_wds, file_wd_len = extract_word_stats( remove_extension(final_file) )
+            file_parts = final_file.split(".")
+            if len(file_parts) > 1:
+                ext = file_parts[len(file_parts)-1]
                 type = file_extension_lookup(ext)
                 existance = 1
-        return ext, type, existance
+        return file_len, file_wds, file_wd_len, ext, type, existance
 
     if add_prefix:
-        col_names = [ col+'_file_extn', col+'_file_extn_type', col+'_file_extn_exists', ] 
+        col_names = [ col+'_file_len', col+'_file_wds', col+'_file_wd_len', 
+                      col+'_file_extn', col+'_file_extn_type', col+'_file_extn_exists', ] 
     else:
-        col_names = [ 'file_extn', 'file_extn_type', 'file_extn_exists' ]
+        col_names = [ 'file_len', 'file_wds', 'file_wd_len', 'file_extn', 'file_extn_type', 'file_extn_exists' ]
 
     df[ col_names ] = df.apply(get_file_features, col=col, axis=1, result_type="expand")
 
     return df
+
+########################################################################################
+def extract_word_stats(path):
+   wds = re.split("[-_/~]+", path)
+   wd_len = np.mean([len(w) for w in wds])
+   return sum([1 for w in wds if len(w)>2]), wd_len
+
 
 ########################################################################################
 def file_extension_lookup(ext):

### 2022-10-04 url2features/params.py

@@ -89,7 +89,7 @@ def add_params_features(df, col, add_prefix):
 
     if add_prefix:
         col_names = [ col+"_params_len", col+"_params_count", col+"_params_has_url", 
-                      col+"params_enc_url", col+"params_enc_char", col+"params_frag_len" ] 
+                      col+"_params_enc_url", col+"_params_enc_char", col+"_params_frag_len" ] 
     else:
         col_names = [ "params_len", "params_count", "params_has_url", 
                       "params_enc_url", "params_enc_char", "params_frag_len" ]

### 2022-10-04 url2features/path.py

@@ -26,9 +26,10 @@ def path_features(df, columns, add_prefix=True):
 
 
 ########################################################################################
-def extract_word_count(path):
+def extract_word_stats(path):
    wds = re.split("[-_/~]+", path)
-   return sum([1 for w in wds if len(w)>2])
+   wd_len = np.mean([len(w) for w in wds]) 
+   return sum([1 for w in wds if len(w)>2]), wd_len
 
 
 ########################################################################################
@@ -62,6 +63,7 @@ def add_path_features(df, col, add_prefix):
         p_length = 0
         p_depth = 0
         p_words = 0
+        p_wd_len = 0
         p_has_date = 0
         p_is_home = 0
         if x[col]==x[col]:
@@ -72,15 +74,15 @@ def add_path_features(df, col, add_prefix):
             if p_length>0:
                path_set = path.split("/")
                p_depth = len(path_set)
-               p_words = extract_word_count(path)
+               p_words, p_wd_len = extract_word_stats(path)
                p_has_date = contains_date(path)
                p_is_home = int(path[0] == "~")
-        return p_length, p_depth, p_words, p_has_date, p_is_home 
+        return p_length, p_depth, p_words, p_wd_len, p_has_date, p_is_home 
 
     if add_prefix:
-        col_names = [ col+"_path_len", col+"_path_depth", col+"_path_words", col+"_path_has_date", col+"_path_is_home" ] 
+        col_names = [ col+"_path_len", col+"_path_depth", col+"_path_words", col+"_path_wd_len", col+"_path_has_date", col+"_path_is_home" ] 
     else:
-        col_names = [ "path_len", "path_depth","path_words", "path_has_date", "path_is_home" ]
+        col_names = [ "path_len", "path_depth","path_words", "path_wd_len", "path_has_date", "path_is_home" ]
 
     df[ col_names ] = df.apply(get_path_features, col=col, axis=1, result_type="expand")
 

### 2022-10-04 RUN_EXPERIMENTS.sh
Setting up reusable ML experiments

@@ -1,28 +1,24 @@
 #!/bin/bash
 
-python malware/00_analysis.py
-python malware/01_baseline.py
-python malware/02_log_regression.py
-python malware/03_extra_trees.py
-python malware/04_lgbm.py
+python  experiments/recipes/01_NBayes.py syskill
+python  experiments/recipes/01_NBayes.py malware
+python  experiments/recipes/01_NBayes.py phishing
+python  experiments/recipes/01_NBayes.py webkb
 
-python phishing/00_analysis.py
-python phishing/01_baseline.py
-python phishing/02_log_regression.py
-python phishing/03_extra_trees.py
-python phishing/04_lgbm.py
+python  experiments/recipes/02_LogReg.py syskill
+python  experiments/recipes/02_LogReg.py malware
+python  experiments/recipes/02_LogReg.py phishing
+python  experiments/recipes/02_LogReg.py webkb
 
-python webkb/00_analysis.py
-python webkb/01_baseline.py
-python webkb/02_log_regression.py
-python webkb/03_extra_trees.py
-python webkb/04_lgbm.py
+python  experiments/recipes/03_ExtraTrees.py syskill
+python  experiments/recipes/03_ExtraTrees.py malware
+python  experiments/recipes/03_ExtraTrees.py phishing
+python  experiments/recipes/03_ExtraTrees.py webkb
 
-python sw/00_analysis.py
-python sw/01_baseline.py
-python sw/02_log_regression.py
-python sw/03_extra_trees.py
-python sw/04_lgbm.py
+python  experiments/recipes/04_LGBM.py syskill
+python  experiments/recipes/04_LGBM.py malware
+python  experiments/recipes/04_LGBM.py phishing
+python  experiments/recipes/04_LGBM.py webkb
 
-python tabulate_results.py
+#python tabulate_results.py
 

### 2022-10-04 experiments/recipes/01_NBayes.py

@@ -1,0 +1,126 @@
+from sklearn.naive_bayes import MultinomialNB
+from sklearn.naive_bayes import GaussianNB
+from sklearn.compose import ColumnTransformer
+from sklearn.impute import SimpleImputer
+from sklearn.pipeline import make_pipeline
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import LabelEncoder
+from sklearn.preprocessing import StandardScaler, OrdinalEncoder
+from sklearn.model_selection import train_test_split
+from sklearn.model_selection import GridSearchCV
+from feature_engine.encoding import RareLabelEncoder
+from feature_engine.imputation import AddMissingIndicator
+from sklearn.metrics import balanced_accuracy_score
+import matplotlib.pyplot as plt
+import projit as pit
+import pandas as pd
+import numpy as np
+import argparse
+import shap
+import sys
+
+def main(dataset):
+    experiment_name = "01 - Naive Bayes"
+    target = "label"
+
+    project = pit.projit_load()
+    exec_id = project.start_experiment(experiment_name, sys.argv[0], params={})
+
+    train_df = pd.read_csv( project.get_dataset(dataset), low_memory=False )
+
+    labels = train_df[target].to_list()
+    labels = [str(l) for l in labels]
+    label_enc = LabelEncoder()
+    label_enc.fit(labels)
+    y = label_enc.transform(labels)
+
+    drop_cols = ['URL', 'label', 'URL_domain_reg_year']
+    X = train_df.drop(drop_cols, axis=1)
+
+    percent = 0.02
+    while (percent * len(train_df))<50:
+        percent += 0.02
+    print("Test Percent:", (percent*100))
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
+
+    numeric_cols = list( X_train.select_dtypes(include="number").columns)
+    categorical_cols = list( X_train.select_dtypes(exclude="number").columns)
+
+    numMissingIndicators = AddMissingIndicator(
+        variables=numeric_cols
+    )
+
+    numeric_transformer = make_pipeline(
+        numMissingIndicators,
+        SimpleImputer(strategy='mean'),
+        StandardScaler()
+    )
+
+    categorical_transformer = make_pipeline(
+        SimpleImputer(strategy='constant', fill_value='missing'),
+        RareLabelEncoder(tol=0.01, n_categories=2, replace_with='rare'),
+        OrdinalEncoder()
[…]

### 2022-10-04 experiments/recipes/02_LogReg.py

@@ -1,0 +1,125 @@
+from sklearn.linear_model import LogisticRegression
+from sklearn.compose import ColumnTransformer
+from sklearn.impute import SimpleImputer
+from sklearn.pipeline import make_pipeline
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import LabelEncoder
+from sklearn.preprocessing import StandardScaler,  OneHotEncoder
+from sklearn.model_selection import train_test_split
+from sklearn.model_selection import GridSearchCV
+from feature_engine.encoding import RareLabelEncoder
+from feature_engine.imputation import AddMissingIndicator
+from sklearn.metrics import balanced_accuracy_score
+import matplotlib.pyplot as plt
+import projit as pit
+import pandas as pd
+import numpy as np
+import argparse
+import shap
+import sys
+
+def main(dataset):
+    experiment_name = "02 - Logistic Regression"
+    target = "label"
+
+    project = pit.projit_load()
+    exec_id = project.start_experiment(experiment_name, sys.argv[0], params={})
+
+    train_df = pd.read_csv( project.get_dataset(dataset), low_memory=False )
+
+    labels = train_df[target].to_list()
+    labels = [str(l) for l in labels]
+    label_enc = LabelEncoder()
+    label_enc.fit(labels)
+    y = label_enc.transform(labels)
+
+    drop_cols = ['URL', 'label', 'URL_domain_reg_year']
+    X = train_df.drop(drop_cols, axis=1)
+
+    percent = 0.02
+    while (percent * len(train_df))<50:
+        percent += 0.02
+    print("Test Percent:", (percent*100))
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
+
+    numeric_cols = list( X_train.select_dtypes(include="number").columns)
+    categorical_cols = list( X_train.select_dtypes(exclude="number").columns)
+
+    numMissingIndicators = AddMissingIndicator(
+        variables=numeric_cols
+    )
+
+    numeric_transformer = make_pipeline(
+        numMissingIndicators,
+        SimpleImputer(strategy='mean'),
+        StandardScaler()
+    )
+
+    categorical_transformer = make_pipeline(
+        SimpleImputer(strategy='constant', fill_value='missing'),
+        RareLabelEncoder(tol=0.01, n_categories=2, replace_with='rare'),
+        OneHotEncoder()
+    )
+
+    preprocessor = ColumnTransformer(
[…]

### 2022-10-04 experiments/recipes/03_ExtraTrees.py

@@ -1,0 +1,123 @@
+from sklearn.ensemble import ExtraTreesClassifier
+from sklearn.compose import ColumnTransformer
+from sklearn.impute import SimpleImputer
+from sklearn.pipeline import make_pipeline
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import LabelEncoder
+from sklearn.preprocessing import StandardScaler, OrdinalEncoder
+from sklearn.model_selection import train_test_split
+from sklearn.model_selection import GridSearchCV
+from feature_engine.encoding import RareLabelEncoder
+from feature_engine.imputation import AddMissingIndicator
+from sklearn.metrics import balanced_accuracy_score
+import matplotlib.pyplot as plt
+import projit as pit
+import pandas as pd
+import numpy as np
+import argparse
+import shap
+import sys
+
+def main(dataset):
+    experiment_name = "03 - Extra Trees"
+    target = "label"
+
+    project = pit.projit_load()
+    exec_id = project.start_experiment(experiment_name, sys.argv[0], params={})
+
+    train_df = pd.read_csv( project.get_dataset(dataset), low_memory=False )
+
+    labels = train_df[target].to_list()
+    labels = [str(l) for l in labels]
+    label_enc = LabelEncoder()
+    label_enc.fit(labels)
+    y = label_enc.transform(labels)
+
+    drop_cols = ['URL', 'label', 'URL_domain_reg_year']
+    X = train_df.drop(drop_cols, axis=1)
+
+    percent = 0.02
+    while (percent * len(train_df))<50:
+        percent += 0.02
+    print("Test Percent:", (percent*100))
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
+
+    numeric_cols = list( X_train.select_dtypes(include="number").columns)
+    categorical_cols = list( X_train.select_dtypes(exclude="number").columns)
+
+    numMissingIndicators = AddMissingIndicator(
+        variables=numeric_cols
+    )
+
+    numeric_transformer = make_pipeline(
+        numMissingIndicators,
+        SimpleImputer(strategy='mean'),
+        StandardScaler()
+    )
+
+    categorical_transformer = make_pipeline(
+        SimpleImputer(strategy='constant', fill_value='missing'),
+        RareLabelEncoder(tol=0.01, n_categories=2, replace_with='rare'),
+        OrdinalEncoder()
+    )
+
+    preprocessor = ColumnTransformer(
[…]

### 2022-10-04 experiments/recipes/04_LGBM.py

@@ -1,0 +1,123 @@
+from lightgbm import LGBMClassifier
+from sklearn.naive_bayes import GaussianNB
+from sklearn.compose import ColumnTransformer
+from sklearn.impute import SimpleImputer
+from sklearn.pipeline import make_pipeline
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import LabelEncoder
+from sklearn.preprocessing import StandardScaler, OrdinalEncoder
+from sklearn.model_selection import train_test_split
+from sklearn.model_selection import GridSearchCV
+from feature_engine.encoding import RareLabelEncoder
+from feature_engine.imputation import AddMissingIndicator
+from sklearn.metrics import balanced_accuracy_score
+import matplotlib.pyplot as plt
+import projit as pit
+import pandas as pd
+import numpy as np
+import argparse
+import shap
+import sys
+
+def main(dataset):
+    experiment_name = "04 - LGBM"
+    target = "label"
+
+    project = pit.projit_load()
+    exec_id = project.start_experiment(experiment_name, sys.argv[0], params={})
+
+    train_df = pd.read_csv( project.get_dataset(dataset), low_memory=False )
+
+    labels = train_df[target].to_list()
+    labels = [str(l) for l in labels]
+    label_enc = LabelEncoder()
+    label_enc.fit(labels)
+    y = label_enc.transform(labels)
+
+    drop_cols = ['URL', 'label', 'URL_domain_reg_year']
+    X = train_df.drop(drop_cols, axis=1)
+
+    percent = 0.02
+    while (percent * len(train_df))<50:
+        percent += 0.02
+    print("Test Percent:", (percent*100))
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
+
+    numeric_cols = list( X_train.select_dtypes(include="number").columns)
+    categorical_cols = list( X_train.select_dtypes(exclude="number").columns)
+
+    numMissingIndicators = AddMissingIndicator(
+        variables=numeric_cols
+    )
+
+    numeric_transformer = make_pipeline(
+        numMissingIndicators,
+        SimpleImputer(strategy='mean'),
+        StandardScaler()
+    )
+
+    categorical_transformer = make_pipeline(
+        SimpleImputer(strategy='constant', fill_value='missing'),
+        RareLabelEncoder(tol=0.01, n_categories=2, replace_with='rare'),
+        OrdinalEncoder()
+    )
+
[…]

### 2022-10-05 PLOT_RESULTS.sh
URl Feature Importance Plot

@@ -1,0 +1,5 @@
+#!/bin/bash
+ 
+python scripts/plot_url_importance.py "URL_" "col_name" "feature_importance_vals" results/final/Syskill.csv,results/final/WebKb.csv,results/final/Phishing.csv,results/final/Malware.csv 
+
+

### 2022-10-05 scripts/plot_url_importance.py

@@ -1,0 +1,152 @@
+# ###################################################################################
+# Plot URL Imprtance
+#
+# ###################################
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.path as mpath
+import matplotlib.lines as mlines
+import matplotlib.patches as mpatches
+from matplotlib.collections import PatchCollection
+import pandas as pd
+import sys
+import os
+
+def add_global(axes, ypos, alph):
+   myy = ypos-0.55
+   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 16.1, 0.7,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='grey')
+   )
+
+
+def add_protocol(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((3.3, myy), 2.0, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_subdomain(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((6.0, myy), 0.8, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_domain(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((7.4, myy), 1.7, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_tld(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((9.7, myy), 0.4, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_path(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((10.7, myy), 2.3, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_file(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((13.7, myy), 1.6, 0.4,
[…]

### 2022-10-05 experiments/recipes/03_ExtraTrees.py
Recipe extension for SHAP values, syskill data cleanup

@@ -36,9 +36,9 @@ def main(dataset):
     drop_cols = ['URL', 'label', 'URL_domain_reg_year']
     X = train_df.drop(drop_cols, axis=1)
 
-    percent = 0.02
+    percent = 0.005
     while (percent * len(train_df))<50:
-        percent += 0.02
+        percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
 

### 2022-10-05 experiments/recipes/04_LGBM.py

@@ -37,9 +37,9 @@ def main(dataset):
     drop_cols = ['URL', 'label', 'URL_domain_reg_year']
     X = train_df.drop(drop_cols, axis=1)
 
-    percent = 0.02
+    percent = 0.005
     while (percent * len(train_df))<50:
-        percent += 0.02
+        percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
 

### 2022-10-08 paper/paper.tex
Expanding experiments to cover SPAM and DMOZ

@@
 Common use cases for URL centered analysis include security analysis of potenital phishing 
-attacks\cite{Basnet2014,Mamun2016,Vazhayil2018}, and identification of pages 
+attacks\cite{Basnet2012,Basnet2014,Mamun2016,Vazhayil2018,Tupsamudre2019}, and identification of pages 
 that host malware or viruses \cite{Canali2011,Mamun2016}.
@@
 
-In this work we describe an ontology of URL fetaures that relates to underlying origin
-and purpose. We then present an open source package for generating features within these
+In this work we develop a feature engineering library that maintains an ontology of URL features 
+that relate to underlying structure of the URL, with a method for visualising the importance of features
+across the URL structure. These techniques can prove useful for analysing features for problems that
+consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}. 
+We then present an open source package for generating features within these
 ontologocal classes and apply them to a variety of tasks. We present our results as a
@@
 \cite{Li2020}
-\cite{Basnet2012}
-\cite{Basnet2014}
-\cite{Tupsamudre2019}
 \cite{Baykan2009}
@@
 Common approaches to feature engineering on URLs include string patterns and regular expressions to
-identify key sequences and lexical properties \cite{Kan2004,Mamun2016}, 
+identify key sequences and lexical properties \cite{Kan2004,Mamun2016,Tupsamudre2019}, 
 creation of lookup tables or likelihood scores based on key sequences
@@
 The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
-sequences which are built from flexible grammars that allow variable positioning of most key elements.
+sequences which are built from flexible grammars that allow variable positioning of most key elements. Furthermore,
+there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
+for phishing attack URLS \cite{Tupsamudre2019}), which emphasize the utility of feature engineering techniques that
+respect the inherent structure of URLs.
 
@@
 
-The features generated by the url2feature package are summairized in Table \ref{tab:features}
+We generate URL features in groups that focus on distinct regions across the URL. We create a group
+of global features that contain general string properties of the entire URL, then create regions
+specific features as outlined in Table \ref{tab:features}.
 
@@
               &path\_words            &Numeric     &Count of distinct words in the path between host and file   \\
+              &path\_wd\_len          &Numeric     &The mean length of the individual words in the path  \\
               &path\_has\_date        &Boolean     &Flag indicating if a date is detected in the path  \\
@@
 \midrule 
-File          &file\_ext              &Category    &The exact file extension e.g. "exe" or "php"    \\
-              &file\_type             &Category    &File extension categorised by function \& purpose    \\
+File          &file\_len              &Numeric     &The character length of the target file    \\
+              &file\_wds              &Numeric     &The count of words longer than 2 chars in the file name   \\
+              &file\_wd\_len          &Numeric     &The mean length of the individual words in the file name  \\
+              &file\_ext              &Category    &The exact file extension e.g. "exe" or "php"    \\
+              &file\_type             &Category    &File extension categorised by function \& purpose (e.g. Static or dynamic)   \\
               &file\_ext\_exists      &Boolean     &Flag indicating presence of a file extension for the URL target  \\
@@
 
-These URL feature functions are all available in the open source python package \emph{url2features}
-available at https://pypi.org/project/url2features with links to usage documentation and source
-code.
+These URL feature functions are available in our open source implmentation and python package \emph{url2features}. 
+The package is designed such that it can process large files in chunks and will only add the specific sub-groups of
+features a user requests.
 
@@
 
-\begin{equation}
-\label{campaign_baseline}
-{}^c\mathcal{A}_p =  \frac{ \sum_{i \in I_p} \mathbf{1}^c(i) A_i }{ \sum_{i \in I_p} \mathbf{1}^c(i) }
-\end{equation}
+We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
+of approximately 50 smaples per experiment. We aggregate the shapley values for these sample points to calculate the mean
+absolute contribution of each feature.
+
+For our URL feature analysis, we then group these individual feature importance values by the URL segment
+that belong to. We sum the feature importance for all features from that segment to allow us to plot the
+segment contributions to model performance. These plots allow structural comparison features across the 
+four problems in this study.
 
 \section{Results}
+
+A set of standard machine learning pipelines are applied to each of the four problems. Each approach is applied
+using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
+of model. All details are available in the source repository for the experiments. The performance of the models
+is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
+metric is appropriate and comparable across all four problems.
 
@@
 \midrule
-Malware              &-      &-     &-     &-        \\
-Phishing             &-      &-     &-     &-        \\
-WebKb 4Uni           &-      &-     &-     &-        \\
-Syskill \& Webert    &-      &-     &-     &-        \\
+Malware              &0.65   &0.93  &0.99  &1.00     \\
+Phishing             &0.89   &0.98  &0.99  &1.00     \\
+WebKb 4Uni           &0.30   &0.36  &0.58  &0.49     \\
+Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
 \bottomrule
@@
 \end{table}
+
+We take the best performing model for each problem and generate the SHAP values for the records in the test data.
+These records are then used to generate the URL Feature Importance Plot shown in Figure \ref{fig:importance}.
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.8]{images/URL_importance.png}
+\caption{Structural Depiction of URL Feature Importance}
+\label{fig:importance}
+\end{figure*}
 

### 2022-10-08 INIT_EXPERIMENTAL_DATA.sh

@@ -5,12 +5,16 @@
 ./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/malware_dataset.csv  >  data/sets/ISCX-URL2016/malware_processed.csv
 ./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/phishing_dataset.csv  >  data/sets/ISCX-URL2016/phishing_processed.csv
 
-./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/WebKb_4Unis/webkb.csv  > data/sets/WebKb_4Unis/webkb_processed.csv
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params  data/sets/ISCX-URL2016/spam_dataset.csv  >  data/sets/ISCX-URL2016/spam_processed.csv
 
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/WebKb_4Unis/webkb.csv  > data/sets/WebKb_4Unis/webkb_processed.csv
+ 
+./url2features-runner.py -columns=URL -simple -host -tld -protocol -path -file -params data/sets/DMOZ/dmoz_dataset.csv > data/sets/DMOZ/dmoz_processed.csv
 
 projit add dataset syskill data/sets/Syskill/syskill_processed.csv
 projit add dataset malware data/sets/ISCX-URL2016/malware_processed.csv
 projit add dataset phishing data/sets/ISCX-URL2016/phishing_processed.csv
+projit add dataset spam data/sets/ISCX-URL2016/spam_processed.csv
 projit add dataset webkb data/sets/WebKb_4Unis/webkb_processed.csv
-
+projit add dataset dmoz data/sets/DMOZ/dmoz_processed.csv
 

### 2022-10-08 RUN_EXPERIMENTS.sh

@@ -20,5 +20,15 @@ python  experiments/recipes/04_LGBM.py malware
 python  experiments/recipes/04_LGBM.py phishing
 python  experiments/recipes/04_LGBM.py webkb
 
+python  experiments/recipes/01_NBayes.py dmoz
+python  experiments/recipes/02_LogReg.py dmoz
+python  experiments/recipes/03_ExtraTrees.py dmoz
+python  experiments/recipes/04_LGBM.py dmoz
+
+python  experiments/recipes/01_NBayes.py spam
+python  experiments/recipes/02_LogReg.py spam
+python  experiments/recipes/03_ExtraTrees.py spam
+python  experiments/recipes/04_LGBM.py spam
+
 #python tabulate_results.py
 

### 2022-10-08 data/sets/DMOZ/process.py

@@ -1,0 +1,9 @@
+import pandas as pd
+import numpy as np
+import os
+
+df = pd.read_csv("archive/URL Classification.csv", header=None, names=['id','URL','label'])
+df = df.loc[:,['URL','label']]
+df.sort_values(by="URL",inplace=True)
+df.to_csv("dmoz_dataset.csv",header=True,index=False)
+

### 2022-10-08 data/sets/ISCX-URL2016/process.py

@@ -5,9 +5,12 @@ import os
 benign = pd.read_csv("FinalDataset/URL/Benign_list_big_final.csv", header=None, names=['URL'])
 phishing = pd.read_csv("FinalDataset/URL/phishing_dataset.csv", header=None, names=['URL'])
 malware = pd.read_csv("FinalDataset/URL/Malware_dataset.csv", header=None, names=['URL'])
+spam = pd.read_csv("FinalDataset/URL/spam_dataset.csv", header=None, names=['URL'])
+
 benign['label']=0
 phishing['label']=1
 malware['label']=1
+spam['label']=1
 
 malware_df = benign.append(malware, ignore_index=True)
 malware_df.sort_values(by="URL",inplace=True)
@@ -17,4 +20,7 @@ phish_df = benign.append(phishing, ignore_index=True)
 phish_df.sort_values(by="URL",inplace=True)
 phish_df.to_csv("phishing_dataset.csv",header=True,index=False)
 
+spam_df = benign.append(spam, ignore_index=True)
+spam_df.sort_values(by="URL",inplace=True)
+spam_df.to_csv("spam_dataset.csv",header=True,index=False)
 

### 2022-10-08 experiments/recipes/01_NBayes.py
Changing experimental protocol for 80-100 test samples

@@ -11,6 +11,7 @@ from sklearn.model_selection import GridSearchCV
 from feature_engine.encoding import RareLabelEncoder
 from feature_engine.imputation import AddMissingIndicator
 from sklearn.metrics import balanced_accuracy_score
+from sklearn.metrics import f1_score
 import matplotlib.pyplot as plt
 import projit as pit
 import pandas as pd
@@ -38,7 +39,7 @@ def main(dataset):
     X = train_df.drop(drop_cols, axis=1)
 
     percent = 0.005
-    while (percent * len(train_df))<50:
+    while (percent * len(train_df))<80:
         percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
@@ -81,9 +82,13 @@ def main(dataset):
     temp = model.predict(X_test)
 
     ba = balanced_accuracy_score(y_test, temp)
+    f1 = f1_score(y_test, temp, average='weighted')
 
     project.add_result(experiment_name, "BAcc", ba, dataset)
+    project.add_result(experiment_name, "F1", f1, dataset)
+
     print("Finished [%s] - Bal Acc:"%dataset, ba)
+    print("                     F1:", f1)
     print("Explaining")
 
     feature_names = X.columns
@@ -94,8 +99,12 @@ def main(dataset):
     #shap_kernel_explainer = shap.KernelExplainer(model_predict, X_train, link='logit')
     mydata = shap.sample(X_train, 200)
     shap_kernel_explainer = shap.KernelExplainer(model_predict, mydata)
-    shap_values = shap_kernel_explainer.shap_values(X_test)
-    shap.summary_plot(shap_values, X_test, plot_type="bar", show=False)
+    if len(X_test)>100:
+        mytest = shap.sample(X_test, 100)
+    else:
+        mytest = X_test
+    shap_values = shap_kernel_explainer.shap_values(mytest)
+    shap.summary_plot(shap_values, mytest, plot_type="bar", show=False)
     plot_name = "results/"+dataset+"_01_NBayes_SHAP.png"
     plt.savefig(plot_name)
 

### 2022-10-08 experiments/recipes/02_LogReg.py

@@ -10,6 +10,7 @@ from sklearn.model_selection import GridSearchCV
 from feature_engine.encoding import RareLabelEncoder
 from feature_engine.imputation import AddMissingIndicator
 from sklearn.metrics import balanced_accuracy_score
+from sklearn.metrics import f1_score
 import matplotlib.pyplot as plt
 import projit as pit
 import pandas as pd
@@ -37,7 +38,7 @@ def main(dataset):
     X = train_df.drop(drop_cols, axis=1)
 
     percent = 0.005
-    while (percent * len(train_df))<50:
+    while (percent * len(train_df))<80:
         percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
@@ -80,9 +81,14 @@ def main(dataset):
     temp = model.predict(X_test)
 
     ba = balanced_accuracy_score(y_test, temp)
+    f1 = f1_score(y_test, temp, average='weighted')
 
     project.add_result(experiment_name, "BAcc", ba, dataset)
+    project.add_result(experiment_name, "F1", f1, dataset)
+
     print("Finished [%s] - Bal Acc:"%dataset, ba)
+    print("                     F1:", ba)
+
     print("Explaining")
 
     feature_names = X.columns
@@ -93,8 +99,14 @@ def main(dataset):
     #shap_kernel_explainer = shap.KernelExplainer(model_predict, X_train, link='logit')
     mydata = shap.sample(X_train, 200)
     shap_kernel_explainer = shap.KernelExplainer(model_predict, mydata)
-    shap_values = shap_kernel_explainer.shap_values(X_test)
-    shap.summary_plot(shap_values, X_test, plot_type="bar", show=False)
+
+    if len(X_test)>100:
+        mytest = shap.sample(X_test, 100)
+    else:
+        mytest = X_test
+    shap_values = shap_kernel_explainer.shap_values(mytest)
+    shap.summary_plot(shap_values, mytest, plot_type="bar", show=False)
+
     plot_name = "results/"+dataset+"_02_LogReg_SHAP.png"
     plt.savefig(plot_name)
 

### 2022-10-08 experiments/recipes/03_ExtraTrees.py

@@ -10,6 +10,7 @@ from sklearn.model_selection import GridSearchCV
 from feature_engine.encoding import RareLabelEncoder
 from feature_engine.imputation import AddMissingIndicator
 from sklearn.metrics import balanced_accuracy_score
+from sklearn.metrics import f1_score
 import matplotlib.pyplot as plt
 import projit as pit
 import pandas as pd
@@ -37,7 +38,7 @@ def main(dataset):
     X = train_df.drop(drop_cols, axis=1)
 
     percent = 0.005
-    while (percent * len(train_df))<50:
+    while (percent * len(train_df))<80:
         percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
@@ -80,9 +81,14 @@ def main(dataset):
     temp = model.predict(X_test)
 
     ba = balanced_accuracy_score(y_test, temp)
+    f1 = f1_score(y_test, temp, average='weighted')
 
     project.add_result(experiment_name, "BAcc", ba, dataset)
+    project.add_result(experiment_name, "F1", f1, dataset)
+
     print("Finished [%s] - Bal Acc:"%dataset, ba)
+    print("                     F1:", ba)
+
     print("Explaining")
 
     feature_names = X.columns
@@ -92,8 +98,14 @@ def main(dataset):
 
     mydata = shap.sample(X_train, 200)
     shap_kernel_explainer = shap.KernelExplainer(model_predict, mydata)
-    shap_values = shap_kernel_explainer.shap_values(X_test)
-    shap.summary_plot(shap_values, X_test, plot_type="bar", show=False)
+
+    if len(X_test)>100:
+        mytest = shap.sample(X_test, 100)
+    else:
+        mytest = X_test
+    shap_values = shap_kernel_explainer.shap_values(mytest)
+    shap.summary_plot(shap_values, mytest, plot_type="bar", show=False)
+
     plot_name = "results/"+dataset+"_03_ExtraTrees_SHAP.png"
     plt.savefig(plot_name)
 

### 2022-10-08 experiments/recipes/04_LGBM.py

@@ -11,6 +11,7 @@ from sklearn.model_selection import GridSearchCV
 from feature_engine.encoding import RareLabelEncoder
 from feature_engine.imputation import AddMissingIndicator
 from sklearn.metrics import balanced_accuracy_score
+from sklearn.metrics import f1_score
 import matplotlib.pyplot as plt
 import projit as pit
 import pandas as pd
@@ -38,7 +39,7 @@ def main(dataset):
     X = train_df.drop(drop_cols, axis=1)
 
     percent = 0.005
-    while (percent * len(train_df))<50:
+    while (percent * len(train_df))<80:
         percent += 0.005
     print("Test Percent:", (percent*100))
     X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=percent, stratify=y, random_state=0)
@@ -81,9 +82,14 @@ def main(dataset):
     temp = model.predict(X_test)
 
     ba = balanced_accuracy_score(y_test, temp)
+    f1 = f1_score(y_test, temp, average='weighted')
 
     project.add_result(experiment_name, "BAcc", ba, dataset)
+    project.add_result(experiment_name, "F1", f1, dataset)
+
     print("Finished [%s] - Bal Acc:"%dataset, ba)
+    print("                     F1:", ba)
+
     print("Explaining")
 
     feature_names = X.columns
@@ -93,8 +99,12 @@ def main(dataset):
 
     mydata = shap.sample(X_train, 200)
     shap_kernel_explainer = shap.KernelExplainer(model_predict, mydata)
-    shap_values = shap_kernel_explainer.shap_values(X_test)
-    shap.summary_plot(shap_values, X_test, plot_type="bar", show=False)
+    if len(X_test)>100:
+        mytest = shap.sample(X_test, 100)
+    else:
+        mytest = X_test
+    shap_values = shap_kernel_explainer.shap_values(mytest)
+    shap.summary_plot(shap_values, mytest, plot_type="bar", show=False)
     plot_name = "results/"+dataset+"_04_LGBM_SHAP.png"
     plt.savefig(plot_name)
     write_shap_values(shap_values,feature_names, "results/"+dataset+"_04_LGBM_SHAP.csv")

### 2022-10-08 url2features/file.py
Adding features for first word in path or file, key value params and bug fix for registration

@@ -47,25 +47,28 @@ def add_file_features(df, col, add_prefix):
         file_len = 0
         file_wds = 0
         file_wd_len = 0
+        file_1st_wd_prefix = ""
+        file_1st_wd = ""
         if x[col]==x[col]:
             url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
             sections = path.split("/")
             final_file = sections[len(sections)-1]
             file_len = len(final_file)
-            file_wds, file_wd_len = extract_word_stats( remove_extension(final_file) )
+            file_1st_wd_prefix, file_1st_wd, file_wds, file_wd_len = extract_word_stats( remove_extension(final_file) )
             file_parts = final_file.split(".")
             if len(file_parts) > 1:
                 ext = file_parts[len(file_parts)-1]
                 type = file_extension_lookup(ext)
                 existance = 1
-        return file_len, file_wds, file_wd_len, ext, type, existance
+        return file_len, file_1st_wd_prefix, file_1st_wd, file_wds, file_wd_len, ext, type, existance
 
     if add_prefix:
-        col_names = [ col+'_file_len', col+'_file_wds', col+'_file_wd_len', 
+        col_names = [ col+'_file_len', col+"_file_1st_wd_prefix", col+"_file_1st_wd", col+'_file_wd_count', col+'_file_wd_len', 
                       col+'_file_extn', col+'_file_extn_type', col+'_file_extn_exists', ] 
     else:
-        col_names = [ 'file_len', 'file_wds', 'file_wd_len', 'file_extn', 'file_extn_type', 'file_extn_exists' ]
+        col_names = [ 'file_len', "file_1st_wd_prefix", "file_1st_wd", 'file_wd_count', 'file_wd_len', 
+                      'file_extn', 'file_extn_type', 'file_extn_exists' ]
 
     df[ col_names ] = df.apply(get_file_features, col=col, axis=1, result_type="expand")
 
@@ -75,7 +78,17 @@ def add_file_features(df, col, add_prefix):
 def extract_word_stats(path):
    wds = re.split("[-_/~]+", path)
    wd_len = np.mean([len(w) for w in wds])
-   return sum([1 for w in wds if len(w)>2]), wd_len
+   my_wds = [w for w in wds if len(w)>2]
+   if len(my_wds)>0:
+      fst_wd = my_wds[0]
+   else:
+      fst_wd = ""
[…]

### 2022-10-08 url2features/params.py

@@ -3,16 +3,15 @@ from urllib import parse
 import pkg_resources
 import pandas as pd
 import numpy as np
+import string
 import math
 import os
 import re
-
 
 """
     url2features.params: Features based on the any params in the URL string
 """
 from .process import load_dictionary
-
 
 ########################################################################################
 def params_features(df, columns, add_prefix=True):
@@ -24,8 +23,6 @@ def params_features(df, columns, add_prefix=True):
     for col in columns:
         rez = add_params_features(rez, col, add_prefix)
     return rez
-
-
 
 ########################################################################################
 regex = r'('
@@ -60,6 +57,8 @@ def detect_encoded_chars(x):
     else:
        return 0
 
+########################################################################################
+count = lambda l1,l2: sum([1 for x in l1 if x in l2])
 
 ########################################################################################
 def add_params_features(df, col, add_prefix):
@@ -71,9 +70,16 @@ def add_params_features(df, col, add_prefix):
         f_length = 0
         p_length = 0
         p_count = 0
+        p_match = np.nan
         p_has_url = 0
         p_enc_url = 0
         p_enc_char = 0
+        key_count = 0
+        key_len = 0
+        key_numeric = 0
+        val_count = 0
+        val_len = 0
+        val_numeric = 0
         if x[col]==x[col]:
             url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
@@ -85,14 +91,38 @@ def add_params_features(df, col, add_prefix):
                p_has_url = detect_embedded_url(query)
                p_enc_url = detect_encoded_link(query)
                p_enc_char = detect_encoded_chars(query)
-        return p_length, p_count, p_has_url, p_enc_url, p_enc_char, f_length
+               keys = []
+               vals = []
+               for pair in param_set:
+                   brok = pair.split("=")
+                   keys.append(brok[0])
+                   if len(brok)>1:
+                      vals.append(brok[1])
+               if len(keys)>0:
+                 key_count = len(keys)
+                 key_len = np.mean([len(k) for k in keys])
+                 all_keys = "".join(keys)
+                 if len(all_keys)>0:
+                    key_numeric = count(all_keys, string.digits)/len(all_keys)  
+               if len(vals)>0:
+                 val_count = len(vals)
+                 val_len = np.mean([len(v) for v in vals])
[…]

### 2022-10-08 url2features/path.py

@@ -29,7 +29,17 @@ def path_features(df, columns, add_prefix=True):
 def extract_word_stats(path):
    wds = re.split("[-_/~]+", path)
    wd_len = np.mean([len(w) for w in wds]) 
-   return sum([1 for w in wds if len(w)>2]), wd_len
+   my_wds = [w for w in wds if len(w)>2]
+   if len(my_wds)>0:
+      fst_wd = my_wds[0]
+   else:
+      fst_wd = ""
+   if len(fst_wd)>3:
+      fst_wd_pre = fst_wd[0:3]
+   else:
+      fst_wd_pre = fst_wd
+
+   return fst_wd_pre, fst_wd, sum([1 for w in wds if len(w)>2]), wd_len
 
 
 ########################################################################################
@@ -64,6 +74,8 @@ def add_path_features(df, col, add_prefix):
         p_depth = 0
         p_words = 0
         p_wd_len = 0
+        p_1st_wd = ""
+        p_1st_wd_pre = ""
         p_has_date = 0
         p_is_home = 0
         if x[col]==x[col]:
@@ -74,15 +86,17 @@ def add_path_features(df, col, add_prefix):
             if p_length>0:
                path_set = path.split("/")
                p_depth = len(path_set)
-               p_words, p_wd_len = extract_word_stats(path)
+               p_1st_wd_pre, p_1st_wd, p_words, p_wd_len = extract_word_stats(path)
                p_has_date = contains_date(path)
                p_is_home = int(path[0] == "~")
-        return p_length, p_depth, p_words, p_wd_len, p_has_date, p_is_home 
+        return p_length, p_depth, p_1st_wd_pre, p_1st_wd, p_words, p_wd_len, p_has_date, p_is_home 
 
     if add_prefix:
-        col_names = [ col+"_path_len", col+"_path_depth", col+"_path_words", col+"_path_wd_len", col+"_path_has_date", col+"_path_is_home" ] 
+        col_names = [ col+"_path_len", col+"_path_depth", col+"_path_1st_wd_prefix", col+"_path_1st_wd", 
+                      col+"_path_wd_count", col+"_path_wd_len", col+"_path_has_date", col+"_path_is_home" ] 
     else:
-        col_names = [ "path_len", "path_depth","path_words", "path_wd_len", "path_has_date", "path_is_home" ]
[…]

### 2022-10-08 url2features/registration.py

@@ -17,7 +17,10 @@ def get_registration_year(domain):
     #print("FUNCTION CALL: get_registration_year(", domain, ")")
     reg = get_domain_registration_date(domain)
     if reg:
+      try:
         return int(reg[0:4])
+      except:
+        return np.nan
     else:
         return np.nan
 

### 2022-10-08 url2features/tld.py

@@ -43,6 +43,7 @@ def add_tld_features(df, col, add_prefix=True):
     def ext_features(x, col):
         freq = 0
         type = 0
+        tld = ""
         if x[col]!=x[col]:
             freq = 0
             type = 0
@@ -50,15 +51,15 @@ def add_tld_features(df, col, add_prefix=True):
             url = (x[col])
             exts = tld_re.findall(url)
             if len(exts) > 0:
-                temp = exts[0].replace('.', '').replace('/','')
-                freq, type = top_level_domain_lookup(temp)
-        return freq, type
+                tld = exts[0].replace('.', '').replace('/','')
+                freq, type = top_level_domain_lookup(tld)
+        return tld, freq, type
 
 
     if add_prefix:
-        col_names = [ col+'_tld_freq', col+'_tld_type' ]
+        col_names = [ col+'_tld_name', col+'_tld_freq', col+'_tld_type' ]
     else:
-        col_names = [ 'tld_freq', 'tld_type' ]
+        col_names = [  'tld_name', 'tld_freq', 'tld_type' ]
 
     df[ col_names ] = df.apply(ext_features, col=col, axis=1, result_type="expand")
 

### 2022-10-08 PLOT_RESULTS.sh
URL Feature Importance changes

@@ -1,5 +1,12 @@
 #!/bin/bash
- 
-python scripts/plot_url_importance.py "URL_" "col_name" "feature_importance_vals" results/final/Syskill.csv,results/final/WebKb.csv,results/final/Phishing.csv,results/final/Malware.csv 
 
+mkdir results/final
+
+cp results/webkb_03_ExtraTrees.csv  results/final/WebKb.csv
+cp results/syskill_01_NBayes_SHAP.csv  results/final/Syskill.csv
+cp results/phishing_04_LGBM_SHAP.csv  results/final/Phishing.csv
+cp results/malware_04_LGBM_SHAP.csv  results/final/Malware.csv 
+cp results/dmoz_03_ExtraTrees.csv  results/final/DMOZ.csv
+
+python scripts/plot_url_importance.py "URL_" "col_name" "feature_importance_vals" results/final/Syskill.csv,results/final/WebKb.csv,results/final/Phishing.csv,results/final/Malware.csv,results/final/DMOZ.csv
 

### 2022-10-08 scripts/plot_url_importance.py

@@ -14,9 +14,9 @@ import sys
 import os
 
 def add_global(axes, ypos, alph):
-   myy = ypos-0.55
-   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 16.1, 0.7,
-       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='grey')
+   myy = ypos-0.25
+   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 16.1, 0.2,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.05), alpha=alph, color='grey')
    )
 
 
@@ -62,15 +62,27 @@ def add_params(axes, ypos, alph):
        boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
    )
 
+def add_keys(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((16, myy), 1.7, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_vals(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((18, myy), 1.7, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
 ####################################################################
 def get_plotable_features(file, fnames, importance, prefix=""):
     df = pd.read_csv(file)
     max_val = df[importance].max()
-    df[importance] = df[importance]/(2*max_val)
+    df[importance] = df[importance]/(1.3*max_val)
     def map_to_group(x):
         x = x[len(prefix):]
         parts = x.split("_")
-        if parts[0] in ["protocol", "subdomain", "domain", "tld", "path", "file", "params"]:
+        if parts[0] in ["protocol", "subdomain", "domain", "tld", "path", "file", "params", "keys", "values"]:
             return parts[0]
         return "global" 
     df['fgroup'] = df[fnames].apply(map_to_group)
@@ -91,8 +103,8 @@ def main(files, prefix, fnames, imports):
         name_parts = fname.split(".")
         plt.text(0, ystart, name_parts[0], ha="left", family='sans-serif', size=11)
         plotables = get_plotable_features(f, fnames, imports, prefix)
-        #if plotables.__contains__("global"):
-        #    #add_global(ax, ystart, plotables["global"])
[…]

### 2022-10-08 paper/paper.tex
Paper expansion

@@
 Common use cases for URL centered analysis include security analysis of potenital phishing 
-attacks\cite{Basnet2012,Basnet2014,Mamun2016,Vazhayil2018,Tupsamudre2019}, and identification of pages 
-that host malware or viruses \cite{Canali2011,Mamun2016}.
-There are also applications to online advertising
+attacks\cite{Garera2007,Basnet2012,Basnet2014,Mamun2016,Verma2017,Vazhayil2018,Tupsamudre2019,Li2020}, 
+and identification of pages that host malware or viruses \cite{Canali2011,Mamun2016}.
+There are also applications to online advertising,
 including anticipation of conversions \cite{Qiu2020}, contextual analysis of
-the content\cite{Kan2005,Baykan2009,Meshkizadeh2010} or language\cite{Baykan2013} of webpages.
+the content\cite{Kan2004,Shih2004,Baykan2009,Meshkizadeh2010,Hernandez2012,Arya2016}, relevance \cite{Kan2005} 
+or language\cite{Baykan2013} of webpages. 
+Content categorisation has also been applied to spam web pages using URLs alone for the sake
+of search results filtering\cite{Chung2010}.
 
@@
 
-\cite{Ayes2019}
-\cite{Li2020}
-\cite{Baykan2009}
-\cite{Kan2005}
-\cite{Hernandez2012}
-\cite{Chung2010}
-\cite{Qiu2020}
-\cite{Xu2021}
-\cite{Rhea2022}
-\cite{Ma2009}
-\cite{Verma2017}
-\cite{Sountharrajan2020}
-\cite{Murthy2022}
-
 Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
@@
 Common approaches to feature engineering on URLs include string patterns and regular expressions to
-identify key sequences and lexical properties \cite{Kan2004,Mamun2016,Tupsamudre2019}, 
+identify key sequences and lexical properties \cite{Kan2004,Garera2007,Mamun2016,Tupsamudre2019}, 
 creation of lookup tables or likelihood scores based on key sequences
-\cite{Meshkizadeh2010}, n-gram or bag of words models \cite{Baykan2009}, 
+\cite{Meshkizadeh2010}, n-gram or bag of words models \cite{Baykan2009,Verma2017}, 
 the generation of task specific embedding vectors\cite{Le2018,Qiu2020} and the
-usage of domain name servers or registrars for ancillary information about the domain registration \cite{Canali2011}. 
+usage of domain name servers or registrars for ancillary information about the domain registration 
+and server configuration\cite{Canali2011,Li2020}. In many modern approaches to malicious URL detection
+multiple feature engineering approaches are typically combined\cite{Sayamber2014,Li2020}. Increasingly,
+sophisticated methods are used to combine, select or learn from combinations of features to adapt to
+changing requirements, particularly in internet security applications\cite{Sountharrajan2020,Li2020}.
+
 Some authors have 
@@
 The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
-sequences which are built from flexible grammars that allow variable positioning of most key elements. Furthermore,
+sequences which are built from flexible grammars that allow variable positioning of most key elements. The
+inherent structure of URLs has been shown to be a source of information that can be exploited in algorithm design \cite{Shih2004}.
+Furthermore,
 there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
@@
               &subdomain\_freq        &Numeric     &Frequency of the subdomain in internet traffics    \\
+              &tld\_name              &Category    &Top Level Domain Name    \\
               &tld\_type              &Category    &Top Level Domain extension categorised by purpose    \\
-              &tld\_freq              &Boolean     &Top Level Domain extension frequency in internet traffic   \\
+              &tld\_freq              &Numeric     &Top Level Domain extension frequency in internet traffic   \\
 \midrule
 Path          &path\_depth            &Numeric     &The depth of the directory path between host and file   \\
-              &path\_words            &Numeric     &Count of distinct words in the path between host and file   \\
+              &path\_1st\_wd          &Category    &The first distinct word in the path longer than 2 chars  \\
+              &path\_1st\_wd\_prefix  &Category    &The first 3 chars of the first distinct word in the path > 2 chars   \\
+              &path\_wd\_count        &Numeric     &Count of distinct words in the path between host and file   \\
               &path\_wd\_len          &Numeric     &The mean length of the individual words in the path  \\
@@
 File          &file\_len              &Numeric     &The character length of the target file    \\
-              &file\_wds              &Numeric     &The count of words longer than 2 chars in the file name   \\
+              &file\_1st\_wd          &Category    &The first distinct word in the file name  \\
+              &file\_1st\_wd\_prefix  &Category    &The first 3 chars of the first distinct word in the filename  \\
+              &file\_wd\_count        &Numeric     &The count of words longer than 2 chars in the file name   \\
               &file\_wd\_len          &Numeric     &The mean length of the individual words in the file name  \\
@@
               &params\_count          &Numeric     &The count of the key value pairs in the param string    \\
+              &params\_match          &Boolean     &Flag indicating if the count of keys and values in the param string match    \\
               &params\_has\_url       &Boolean     &Flag indicating presence of a raw URL within the parameter string   \\
@@
               &params\_frag\_len      &Numeric     &Length of a hash delineated fragement at the end of the parameter string   \\
+              &keys\_len              &Numeric     &The mean length of the individual keys in the params  \\
+              &keys\_numeric          &Numeric     &The proportion of numeric characters in the param keys \\
+              &values\_len            &Numeric     &The mean length of the individual values in the params  \\
+              &values\_numeric        &Numeric     &The proportion of numeric characters in the param values \\
 \bottomrule
@@
 Syskill \& Webert    &330             &3       &68\%        \\
+DMOZ                 &1,562,978       &15      &16\%        \\
 \bottomrule
@@
 We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
-of approximately 50 smaples per experiment. We aggregate the shapley values for these sample points to calculate the mean
-absolute contribution of each feature.
+of 80-100 smaples per experiment. We aggregate the shapley values for these sample points to calculate the mean
+absolute contribution of each feature, as is typically done in Shaplet fetaure importance plots.
 
-For our URL feature analysis, we then group these individual feature importance values by the URL segment
-that belong to. We sum the feature importance for all features from that segment to allow us to plot the
-segment contributions to model performance. These plots allow structural comparison features across the 
-four problems in this study.
+For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
+that the feature was derive from, using Figure \ref{fig:url} as a guide to these segments. 
+We sum the feature importance for all features within a URL segment to allow us to plot the
+segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
+which captures the importance of global features (like URL length). If the script is applied to a dataset with
+more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
+URL features are plotted below their segment in a canonical example URL.
+
+These plots allow for structural understanding of how URL data
+controbutes to predictive performance of a model and permits the comparison of feature importance 
+across the five problems in this study. The script for generating these plots is provides as part of the
+`url2features` open source package.
 
@@
 Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
+DMOZ                 &0.12   &0.17  &0.29  &0.25     \\
 \bottomrule
@@
 We take the best performing model for each problem and generate the SHAP values for the records in the test data.
-These records are then used to generate the URL Feature Importance Plot shown in Figure \ref{fig:importance}.
+These records are then used to generate the URL Structure Feature Importance Plot shown in Figure \ref{fig:importance}.
 
@@
 \end{figure*}
+
+We see that for all tasks in these experiments the `path` segment provides the most consistent contribution. The subdomain
+and global fetaures appear to be strong for all of the malicious URL detection problems.
 

### 2022-10-09 PLOT_RESULTS.sh
Feature expansion for params and domain, force lowercase and bug fixes in path and file, update to feature importance

@@ -7,6 +7,7 @@ cp results/syskill_01_NBayes_SHAP.csv  results/final/Syskill.csv
 cp results/phishing_04_LGBM_SHAP.csv  results/final/Phishing.csv
 cp results/malware_04_LGBM_SHAP.csv  results/final/Malware.csv 
 cp results/dmoz_03_ExtraTrees.csv  results/final/DMOZ.csv
+cp results/spam_03_ExtraTrees.csv  results/final/Spam.csv
 
-python scripts/plot_url_importance.py "URL_" "col_name" "feature_importance_vals" results/final/Syskill.csv,results/final/WebKb.csv,results/final/Phishing.csv,results/final/Malware.csv,results/final/DMOZ.csv
+python scripts/plot_url_importance.py "URL_" "col_name" "feature_importance_vals" results/final/Syskill.csv,results/final/WebKb.csv,results/final/Spam.csv,results/final/Phishing.csv,results/final/Malware.csv,results/final/DMOZ.csv
 

### 2022-10-09 RUN_EXPERIMENTS.sh

@@ -1,34 +1,40 @@
 #!/bin/bash
 
+echo "SySkill"
 python  experiments/recipes/01_NBayes.py syskill
-python  experiments/recipes/01_NBayes.py malware
-python  experiments/recipes/01_NBayes.py phishing
-python  experiments/recipes/01_NBayes.py webkb
-
 python  experiments/recipes/02_LogReg.py syskill
-python  experiments/recipes/02_LogReg.py malware
-python  experiments/recipes/02_LogReg.py phishing
-python  experiments/recipes/02_LogReg.py webkb
-
 python  experiments/recipes/03_ExtraTrees.py syskill
-python  experiments/recipes/03_ExtraTrees.py malware
-python  experiments/recipes/03_ExtraTrees.py phishing
-python  experiments/recipes/03_ExtraTrees.py webkb
-
 python  experiments/recipes/04_LGBM.py syskill
-python  experiments/recipes/04_LGBM.py malware
-python  experiments/recipes/04_LGBM.py phishing
+
+echo "WebKb"
+python  experiments/recipes/01_NBayes.py webkb
+python  experiments/recipes/02_LogReg.py webkb
+python  experiments/recipes/03_ExtraTrees.py webkb
 python  experiments/recipes/04_LGBM.py webkb
 
-python  experiments/recipes/01_NBayes.py dmoz
-python  experiments/recipes/02_LogReg.py dmoz
-python  experiments/recipes/03_ExtraTrees.py dmoz
-python  experiments/recipes/04_LGBM.py dmoz
-
+echo "SPAM"
 python  experiments/recipes/01_NBayes.py spam
 python  experiments/recipes/02_LogReg.py spam
 python  experiments/recipes/03_ExtraTrees.py spam
 python  experiments/recipes/04_LGBM.py spam
+
+echo "Malware"
+python  experiments/recipes/01_NBayes.py malware
+python  experiments/recipes/02_LogReg.py malware
+python  experiments/recipes/03_ExtraTrees.py malware
+python  experiments/recipes/04_LGBM.py malware
+
+echo "Phishing"
+python  experiments/recipes/01_NBayes.py phishing
+python  experiments/recipes/02_LogReg.py phishing
+python  experiments/recipes/03_ExtraTrees.py phishing
+python  experiments/recipes/04_LGBM.py phishing
+
+echo "DMOZ"
+python  experiments/recipes/01_NBayes.py dmoz
[…]

### 2022-10-09 data/sets/DMOZ/convert.py

@@ -1,0 +1,28 @@
+import time
+import pandas as pd
+import urllib.request
+
+df = pd.read_csv("dmoz_dataset_head.csv")
+
+all_links = df["URL"].to_list()
+
+response_times = []
+active_links = []
+
+for x in all_links:
+    st = time.time()
+    try:
+        rez = urllib.request.urlopen(x).getcode()
+        active = 1
+    except:
+        active = 0
+    et = time.time()
+    resp = et - st
+    response_times.append(resp)
+    active_links.append(active)
+
+total_data = pd.DataFrame({"URL":all_links, "active":active_links, "response":response_times})
+
+total_data.to_csv("DMOZ_active_response_test.csv", index=False, header=True)
+
+

### 2022-10-09 scripts/plot_url_importance.py

@@ -19,7 +19,6 @@ def add_global(axes, ypos, alph):
        boxstyle=mpatches.BoxStyle("Round", pad=0.05), alpha=alph, color='grey')
    )
 
-
 def add_protocol(axes, ypos, alph):
    myy = ypos-0.4
    axes.add_patch(mpatches.FancyBboxPatch((3.3, myy), 2.0, 0.4,
@@ -64,13 +63,13 @@ def add_params(axes, ypos, alph):
 
 def add_keys(axes, ypos, alph):
    myy = ypos-0.4
-   axes.add_patch(mpatches.FancyBboxPatch((16, myy), 1.7, 0.4,
+   axes.add_patch(mpatches.FancyBboxPatch((16, myy), 1.1, 0.4,
        boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
    )
 
 def add_vals(axes, ypos, alph):
    myy = ypos-0.4
-   axes.add_patch(mpatches.FancyBboxPatch((18, myy), 1.7, 0.4,
+   axes.add_patch(mpatches.FancyBboxPatch((18.0, myy), 1.1, 0.4,
        boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
    )
 
@@ -78,7 +77,7 @@ def add_vals(axes, ypos, alph):
 def get_plotable_features(file, fnames, importance, prefix=""):
     df = pd.read_csv(file)
     max_val = df[importance].max()
-    df[importance] = df[importance]/(1.3*max_val)
+    df[importance] = df[importance]/(1.2*max_val)
     def map_to_group(x):
         x = x[len(prefix):]
         parts = x.split("_")
@@ -119,6 +118,10 @@ def main(files, prefix, fnames, imports):
             add_tld(ax, ystart, plotables["tld"])
         if plotables.__contains__("file"):
             add_file(ax, ystart, plotables["file"])
+        if plotables.__contains__("keys"):
+            add_keys(ax, ystart, plotables["keys"])
+        if plotables.__contains__("values"):
+            add_vals(ax, ystart, plotables["values"])
         ystart += 2
 
     plt.axis('equal')

### 2022-10-09 url2features/file.py

@@ -58,7 +58,7 @@ def add_file_features(df, col, add_prefix):
             file_1st_wd_prefix, file_1st_wd, file_wds, file_wd_len = extract_word_stats( remove_extension(final_file) )
             file_parts = final_file.split(".")
             if len(file_parts) > 1:
-                ext = file_parts[len(file_parts)-1]
+                ext = file_parts[len(file_parts)-1].lower()
                 type = file_extension_lookup(ext)
                 existance = 1
         return file_len, file_1st_wd_prefix, file_1st_wd, file_wds, file_wd_len, ext, type, existance
@@ -88,7 +88,7 @@ def extract_word_stats(path):
    else:
       fst_wd_pre = fst_wd
 
-   return fst_wd_pre, fst_wd, sum([1 for w in wds if len(w)>2]), wd_len
+   return fst_wd_pre.lower(), fst_wd.lower(), sum([1 for w in wds if len(w)>2]), wd_len
 
 
 ########################################################################################

### 2022-10-09 url2features/host.py

@@ -1,6 +1,7 @@
 # -*- coding: utf-8 -*-
 import pkg_resources
 import pandas as pd 
+import string
 import numpy as np
 import math
 import sys
@@ -107,6 +108,7 @@ def add_host_features(df, col, add_prefix=True):
         Note: We use the value -1 to indicate that the subdomain is missing
               Where 0 is reserved for a subdomain that is present but unknown
     """
+    count = lambda l1,l2: sum([1 for x in l1 if x in l2])
 
     def dom_features(x, col):
         url = str(x[col]).strip()
@@ -114,6 +116,9 @@ def add_host_features(df, col, add_prefix=True):
             is_ip = np.nan
             has_port = np.nan
             secs = np.nan
+            dom_len = np.nan
+            dom_alpha = np.nan
+            subbie = np.nan
             sub_type = np.nan
             sub_freq = np.nan
             reg_year = np.nan
@@ -126,6 +131,9 @@ def add_host_features(df, col, add_prefix=True):
             parts = host.split(".")
             secs = len(parts)
             if is_ip:
+                subbie = ""
+                dom_len = np.nan
+                dom_alpha = np.nan
                 sub_type = np.nan
                 sub_freq = np.nan
                 reg_dom = host
@@ -133,11 +141,22 @@ def add_host_features(df, col, add_prefix=True):
                 prime, suffix = split_domain_and_suffix(host)
                 parts = prime.split(".")
                 if len(parts) > 1:
-                    subbie = ".".join(parts[0:-1])
+                    dom_len = len(parts[-1])
+                    if dom_len > 0:
+                        dom_alpha = count(parts[-1], string.ascii_lowercase)/dom_len
+                    else:
+                        dom_alpha = np.nan
+                    subbie = ".".join(parts[0:-1]).lower()
                     sub_type = get_subdomain_type(subbie)
                     sub_freq = get_subdomain_freq(subbie)
                     reg_dom = prime[len(subbie)+1:] + suffix
                 else:
+                    subbie = ""
+                    dom_len = len(prime)
+                    if dom_len > 0:
+                        dom_alpha = count(prime, string.ascii_lowercase)/dom_len
+                    else:
+                        dom_alpha = np.nan
                     sub_type = -1
                     sub_freq = -1
                     reg_dom = host
[…]

### 2022-10-09 url2features/params.py

@@ -68,6 +68,8 @@ def add_params_features(df, col, add_prefix):
     """
     def get_params_features(x, col):
         f_length = 0
+        f_sections = 0
+        f_enc_char = 0
         p_length = 0
         p_count = 0
         p_match = np.nan
@@ -84,6 +86,10 @@ def add_params_features(df, col, add_prefix):
             url = add_protocol_if_missing(x[col])
             protocol, host, path, params, query, fragment = parse.urlparse(url.strip())
             f_length = len(fragment)
+            if f_length>0:
+               fparts = re.split(r'[?=&]', fragment)
+               f_sections = len(fparts)
+               f_enc_char = detect_encoded_chars(fragment)
             p_length = len(query)
             if p_length>0:
                param_set = query.split("&")
@@ -111,16 +117,18 @@ def add_params_features(df, col, add_prefix):
                  if len(all_vals)>0:
                     val_numeric = count(all_vals, string.digits)/len(all_vals)
             p_match = int( val_count == key_count )  
-        return p_length, p_count, p_match, p_has_url, p_enc_url, p_enc_char, f_length, key_count, key_len, key_numeric, val_count, val_len, val_numeric
+        return p_length, p_count, p_match, p_has_url, p_enc_url, p_enc_char, f_length, f_sections, f_enc_char, key_count, key_len, key_numeric, val_count, val_len, val_numeric
 
     if add_prefix:
         col_names = [ col+"_params_len", col+"_params_count", col+"_params_match", col+"_params_has_url", 
-                      col+"_params_enc_url", col+"_params_enc_char", col+"_params_frag_len",
+                      col+"_params_enc_url", col+"_params_enc_char", 
+                      col+"_frag_len", col+"_frag_secs",  col+"_frag_enc_char", 
                       col+"_keys_count", col+"_keys_len", col+"_keys_numeric", 
                       col+"_value_count", col+"_values_len", col+"_values_numeric"  ] 
     else:
         col_names = [ "params_len", "params_count", col+"_params_match", "params_has_url", 
-                      "params_enc_url", "params_enc_char", "params_frag_len", 
+                      "params_enc_url", "params_enc_char", 
+                      "frag_len", "frag_secs", "frag_enc_char", 
                       "keys_count", "keys_len", "keys_numeric", 
                       "values_count", "values_len", "values_numeric" ]
 

### 2022-10-09 url2features/path.py

@@ -39,7 +39,7 @@ def extract_word_stats(path):
    else:
       fst_wd_pre = fst_wd
 
-   return fst_wd_pre, fst_wd, sum([1 for w in wds if len(w)>2]), wd_len
+   return fst_wd_pre.lower(), fst_wd.lower(), sum([1 for w in wds if len(w)>2]), wd_len
 
 
 ########################################################################################

### 2022-10-09 paper/paper.tex
updating feature importance plot to include param fragment

@@
 \centering
-\includegraphics[scale=0.3]{images/URL_parts.png}
+\includegraphics[scale=0.6]{images/URL_parts.png}
 \caption{Structural components of a URL requiring specific feature engineering treatment}
@@
               &host\_has\_port        &Boolean     &Flag indicating if a port number is explicitly specified    \\
+              &domain\_len            &Numeric     &Character length of the domain name (minus TLD and subdomain)     \\
+              &domain\_alpha          &Numeric     &Proportion of characters in the domain that are letters    \\
               &domain\_sections       &Numeric     &Count of period separated domain sections    \\
-              &domain\_reg\_year      &Numeric     &Year in which the domain was initially registered    \\
+              &subdomain              &Category    &The text value of the subdomain  \\
               &subdomain\_type        &Category    &Categorisation of the purpose of the subdomain \\
@@
               &params\_frag\_len      &Numeric     &Length of a hash delineated fragement at the end of the parameter string   \\
+              &keys\_count            &Numeric     &Count of the distinct keys used in the parameter string  \\
               &keys\_len              &Numeric     &The mean length of the individual keys in the params  \\
               &keys\_numeric          &Numeric     &The proportion of numeric characters in the param keys \\
+              &values\_count          &Numeric     &Count of the distinct values used in the parameter string  \\
               &values\_len            &Numeric     &The mean length of the individual values in the params  \\
               &values\_numeric        &Numeric     &The proportion of numeric characters in the param values \\
+              &frag\_len              &Numeric     &The character length of the fragment string    \\
+              &frag\_secs             &Numeric     &Count of distinct sections in the fragment string delimited by [?\&=]  \\
+              &frag\_enc\_char        &Boolean     &Flag indicating presence of an encoded character within the fragment string    \\
 \bottomrule
@@
 
-The data used in this study was colated from a range of publications that 
-present internet classification problems containing URLs as the primary feature.
-The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
-that need to be discriminated against benign URLS\cite{Mamun2016}.
+The data used in this study was colated from a range of sources to represent a varity of 
+Internet resource classification problems containing URLs as the primary feature.
+The ISCX Malcious URL classification dataset contains malware, spam and phishing URLS 
+that need to be discriminated against a set of benign URLS\cite{Mamun2016}.
 The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
@@
 with a human generated categorisation for determining personal preferences in webpage
-content\cite{Pazzani1996}. These 4 URL classification problems are summarised in Table \ref{tab:data}
+content\cite{Pazzani1996}. Finally, we utilise the Kaggle DMOZ dataset that contains 
+a large set of topic categorised URLs\cite{dmoz}.
+
+These 6 URL classification problems are summarised in Table \ref{tab:data}, where
+show the number of records, the cardinality of the target classes, and the proportion
+of the data that belongs to the most common class in the set.
 
@@
 \midrule
+spam                 &47,378          &2       &75\%        \\
 Malware              &46,944          &2       &75\%        \\
@@
 
-We generate all url features for each of these datasets and then apply a range of machine learning
+We generate all URL features for each of these datasets and then apply a range of machine learning
 techniques to build classifiers that can be analysed for key features for each task.
@@
 is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
-metric is appropriate and comparable across all four problems.
+metric is appropriate and comparable across all six problems.
 
@@
 \midrule
+Spam                 &1.00   &1.00  &1.00  &1.00     \\
 Malware              &0.65   &0.93  &0.99  &1.00     \\
@@
 \end{table}
+
+It should be clear from this table that the internet security probelms are much more amenable to URL based 
+classification. All three of these problems result in high performing classifiers. In comparison the topic
+and user preference based tasks achieve far more modest performance. These problems are hindered by both higher 
+cardinality targets, and 2 or the 3 data sets being much smaller. However, the results suggest that in general
+URL based topic classification is likely to be difficult.
 

### 2022-10-09 scripts/plot_url_importance.py

@@ -15,7 +15,7 @@ import os
 
 def add_global(axes, ypos, alph):
    myy = ypos-0.25
-   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 16.1, 0.2,
+   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 18.0, 0.2,
        boxstyle=mpatches.BoxStyle("Round", pad=0.05), alpha=alph, color='grey')
    )
 
@@ -73,15 +73,21 @@ def add_vals(axes, ypos, alph):
        boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
    )
 
+def add_frag(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((20.0, myy), 1.1, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
 ####################################################################
 def get_plotable_features(file, fnames, importance, prefix=""):
     df = pd.read_csv(file)
     max_val = df[importance].max()
-    df[importance] = df[importance]/(1.2*max_val)
+    df[importance] = df[importance]/(max_val)
     def map_to_group(x):
         x = x[len(prefix):]
         parts = x.split("_")
-        if parts[0] in ["protocol", "subdomain", "domain", "tld", "path", "file", "params", "keys", "values"]:
+        if parts[0] in ["protocol", "subdomain", "domain", "tld", "path", "file", "params", "keys", "values", "frag"]:
             return parts[0]
         return "global" 
     df['fgroup'] = df[fnames].apply(map_to_group)
@@ -93,7 +99,7 @@ def main(files, prefix, fnames, imports):
     fig, ax = plt.subplots( figsize=(8, 6))
     plt.gca().invert_yaxis()
     ax.plot([0, 20],[0, 20], alpha=0.0)
-    example_url = "protocol://sub.domain.tld/path/way/file.ext?query=done"
+    example_url = "protocol://sub.domain.tld/path/way/file.ext?query=done#frag"
     plt.text(3, 2, example_url, ha="left", family='sans-serif', size=11)
     ystart = 4
     for f in files:
@@ -122,6 +128,8 @@ def main(files, prefix, fnames, imports):
             add_keys(ax, ystart, plotables["keys"])
         if plotables.__contains__("values"):
             add_vals(ax, ystart, plotables["values"])
[…]

### 2022-10-09 url2features/__init__.py
Prep for new release

@@ -1,4 +1,4 @@
-__version__ = "0.3.0"
+__version__ = "0.4.0"
 
 from .pipeline import URLTransform
 

### 2022-10-09 paper/paper.tex
Paper update

@@
 
+\begin{figure*}
+\centering
+\includegraphics[scale=0.6]{images/URL_parts.png}
+\caption{Structural components of a URL requiring specific feature engineering treatment}
+\label{fig:url_structure}
+\end{figure*}
+
 Common feature engineering strategies exploit these potential sources of information
@@
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.6]{images/URL_parts.png}
-\caption{Structural components of a URL requiring specific feature engineering treatment}
-\label{fig:url_structure}
-\end{figure*}
-
 \section{Methodology}
@@
 We design a feature extraction library for URLs that is sensitive to the various sections of URL
-structure outlined above. We then apply this library to multiple machine learning tasks using only URLs
-as the input variable. We experiment with multiple standard machine learning techniques and evaluate
-the impact of the URL features using the SHAP package for feature importance.
+structure outlined above. Previous work has presented datasets for specific problems where the features
+are provided with a similar structural grouping\cite{Vrban2020}. However, we provide our feature extraction
+application designed so that any specific subset of these features can be extracted for a specific task.
 
-\subsection{Features}
+We apply this library to multiple machine learning tasks using only URLs as the input variable. We choose
+these tasks such that they span very different classes of problems an dataset sizes. 
+We experiment with multiple standard machine learning techniques and evaluate
+the impact of the URL features using the SHAP package for feature importance. We develop a process
+for analysing thess features within the logical structure of the URL.
 
-We generate URL features in groups that focus on distinct regions across the URL. We create a group
-of global features that contain general string properties of the entire URL, then create regions
-specific features as outlined in Table \ref{tab:features}.
+\subsection{Data}
+The data used in this study was colated from a range of sources to represent a varity of
+Internet resource classification problems containing URLs as the primary feature.
+The ISCX Malcious URL classification dataset contains malware, spam and phishing URLS
+that need to be discriminated against a set of benign URLS\cite{Mamun2016}.
+The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
+range of university URLs categorised into multiple topic categories\cite{Craven1998}.
+The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
+with a human generated categorisation for determining personal preferences in webpage
+content\cite{Pazzani1996}. Finally, we utilise the Kaggle DMOZ dataset that contains
+a large set of topic categorised URLs\cite{dmoz}.
+
+These 6 URL classification problems are summarised in Table \ref{tab:data}, where
+show the number of records, the cardinality of the target classes, and the proportion
+of the data that belongs to the most common class in the set.
+
+\begin{table}
+\caption{Datasets}
+\label{tab:data}
+\begin{tabular}{|l|r|r|r|}
+\toprule
+Dataset              &Records        &Classes  &Majority    \\
+\midrule
+spam                 &47,378          &2       &75\%        \\
+Malware              &46,944          &2       &75\%        \\
+Phishing             &45,343          &2       &78\%        \\
+WebKb 4Uni           &8,284           &7       &45\%        \\
+Syskill \& Webert    &330             &3       &68\%        \\
+DMOZ                 &1,562,978       &15      &16\%        \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+We generate all URL features for each of these datasets and then apply a range of machine learning
+techniques to build classifiers that can be analysed for key features for each task.
 
@@
 
+\subsection{Features}
+
+We generate URL features in groups that focus on distinct regions across the URL. We create a group
+of global features that contain general string properties of the entire URL, then create regions
+specific features as outlined in Table \ref{tab:features}.
+
 These URL feature functions are available in our open source implmentation and python package \emph{url2features}. 
 The package is designed such that it can process large files in chunks and will only add the specific sub-groups of
-features a user requests.
-
-\subsection{Data}
-
-The data used in this study was colated from a range of sources to represent a varity of 
-Internet resource classification problems containing URLs as the primary feature.
-The ISCX Malcious URL classification dataset contains malware, spam and phishing URLS 
-that need to be discriminated against a set of benign URLS\cite{Mamun2016}.
-The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
-range of university URLs categorised into multiple topic categories\cite{Craven1998}.
-The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
-with a human generated categorisation for determining personal preferences in webpage
-content\cite{Pazzani1996}. Finally, we utilise the Kaggle DMOZ dataset that contains 
-a large set of topic categorised URLs\cite{dmoz}.
-
-These 6 URL classification problems are summarised in Table \ref{tab:data}, where
-show the number of records, the cardinality of the target classes, and the proportion
-of the data that belongs to the most common class in the set.
-
-\begin{table}
-\caption{Datasets}
-\label{tab:data}
-\begin{tabular}{|l|r|r|r|}
-\toprule
-Dataset              &Records        &Classes  &Majority    \\
-\midrule
-spam                 &47,378          &2       &75\%        \\
-Malware              &46,944          &2       &75\%        \\
-Phishing             &45,343          &2       &78\%        \\
-WebKb 4Uni           &8,284           &7       &45\%        \\
-Syskill \& Webert    &330             &3       &68\%        \\
-DMOZ                 &1,562,978       &15      &16\%        \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-We generate all URL features for each of these datasets and then apply a range of machine learning
-techniques to build classifiers that can be analysed for key features for each task.
+features a user requests. In addition, the naming convention is designed so that features relating to specific
+regions of the URL can be identified and analysed as a group.
 
@@
 
-It should be clear from this table that the internet security probelms are much more amenable to URL based 
-classification. All three of these problems result in high performing classifiers. In comparison the topic
-and user preference based tasks achieve far more modest performance. These problems are hindered by both higher 
-cardinality targets, and 2 or the 3 data sets being much smaller. However, the results suggest that in general
-URL based topic classification is likely to be difficult.
-
-We take the best performing model for each problem and generate the SHAP values for the records in the test data.
-These records are then used to generate the URL Structure Feature Importance Plot shown in Figure \ref{fig:importance}.
-
 \begin{figure*}
@@
 
-We see that for all tasks in these experiments the `path` segment provides the most consistent contribution. The subdomain
-and global fetaures appear to be strong for all of the malicious URL detection problems.
+The table of results indicates that internet security problems appear much more amenable to URL based 
+classification. All three of these problems result in high performing classifiers. In comparison the topic
+and user preference based tasks achieve far more modest performance. It is worth noting that these problems 
+are hindered by both higher cardinality targets and greater variability in dataset size, 2 of the 3 data 
+sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
+dataset strongly suggests that, in general, URL based topic classification is likely to remain a difficult
+problem.
+
+We used the results from the best performing classification model for each individual problem and generated
+the SHAP values for the records in the test dataset. These records are then used to generate the URL Structure 
+Feature Importance Plot shown in Figure \ref{fig:importance}. This plot aggregates the importance of individual
+features into their region of origin within the URL structure. Allowing us to visualise the source of signal for
+each task and compare features across tasks.
+
+We see that there is substantial variability across all classification tasks in these experiments.
+The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classifcation
+task, where we see some value in the URL parameter features. The domain, path and file regions are the predominant sources
+of signal across these tasks. Nevertheless, the emphasis changes between them. The subdomain appears particularly
+important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classifciation data.
+
+The internet security problems appear to derive less utility from the global features when compared to the three
+topic classification problems, as is indicated by the strength of the grey lines through the middle of the plot 
+for each task. The contributions of the domain name itself and the top level domain vary across the tasks and do
+not appear consistant across the top broad categories of secutity and topic classification. Suggesting that developers
+need to test these features on a task by task basis rather than relying on heuristics.
 

### 2022-10-11 data/sets/DMOZ/convert.py
minor

@@ -2,7 +2,10 @@ import time
 import pandas as pd
 import urllib.request
 
-df = pd.read_csv("dmoz_dataset_head.csv")
+#dataset = "dmoz_dataset.csv"
+dataset = "dmoz_dataset_tail_01.csv"
+
+df = pd.read_csv(dataset)
 
 all_links = df["URL"].to_list()
 
@@ -20,9 +23,9 @@ for x in all_links:
     resp = et - st
     response_times.append(resp)
     active_links.append(active)
+    print(f"{x},{active},{resp}")
 
-total_data = pd.DataFrame({"URL":all_links, "active":active_links, "response":response_times})
-
-total_data.to_csv("DMOZ_active_response_test.csv", index=False, header=True)
+#total_data = pd.DataFrame({"URL":all_links, "active":active_links, "response":response_times})
+#total_data.to_csv("DMOZ_active_response_test.csv", index=False, header=True)
 
 

### 2023-03-15 paper/paper.tex
Paper update

@@
 internet activity, hence they require effective processing for a wide variety of machine 
-learning applications. While URLs are structurally rich, they are not subject
-to universal principles of construction making fetaure engineering for internet data an ongoing challenge.
+learning applications. While URLs are structurally rich, the structure can be both domain specific
+and subject to change over time, making feature engineering for URLs an ongoing challenge.
 
-In this research we outline the key categories of information structure in domains and URLs.
-We share an open source implementation of these ideas and demonstrate their utility across a range of 
-internet traffic machine learning problems. Python package available at https://pypi.org/project/url2features
+In this research we outline the key structural components of URLs and discuss the information
+available within each. We describe methods for generating features on these URL components and 
+share an open source implementation of these ideas. In addition, we describe a method for 
+exploring URL feature impact that allows for comparison and analysis of the information available inside URLS.
+We experiment with a collection of URL classification problems and demonstrate their utility 
+of these tools. 
 \end{abstract}
+% https://pypi.org/project/url2features
 
@@
 The Uniform Resource Locator (URL) is a ubiquitous element the digital world. 
-We use them to advertise and locate businesses, to retrieve news and media and 
-to interact with other people across a broad of social applications.
+We use them to retrieve news and media, advertise or find businesses and services, 
+and to interact with other people across a broad of social applications. Below the
+surface many online services use URLs internally for communicating with other digital
+services, making the URL a fundamental data point for both users and machines.
+
 Processing URLs is key component of many tasks that involve
@@
 information available because the demands of the task require immediate analysis.
-In applications like malicious wesite detection the URL needs to be processed with
+In applications like malicious wesite detection the URL needs to be processed
 in a rapid and efficient manner to provide utility\cite{Ma2009b}.
 Common use cases for URL centered analysis include security analysis of potenital phishing 
-attacks\cite{Garera2007,Basnet2012,Basnet2014,Mamun2016,Verma2017,Vazhayil2018,Tupsamudre2019,Li2020}, 
+attacks\cite{Garera2007,Basnet2012,Basnet2014,Mamun2016,Verma2017,Vazhayil2018,Tupsamudre2019,Sirigineedi2020,Li2020}, 
 and identification of pages that host malware or viruses \cite{Canali2011,Mamun2016}.
@@
 Content categorisation has also been applied to spam web pages using URLs alone for the sake
-of search results filtering\cite{Chung2010}.
+of search results filtering\cite{Chung2010,Hassan2008}.
 
 The URL is made up of multiple elements, but at its core is the domain. The domain
-contains internal information about both its intended purpose, legitimacy and likely
-origin. It is also a source of additional information through requests to Domain Name
-Servers (DNS) to understand both its history and place within the network topology.
+contains internal information about both the intended purpose of a URL, its legitimacy 
+and the likely country of origin. The domain is also a source of additional information 
+through requests to Domain Name Servers (DNS) to understand both its history and structure
+ of its network topology and resources.
+
+Beyond the domain, the URL consists of a sequence of words, categories, identfiers, dates
+or domain specific abreviations. This sequence can indicate the psychoogical elements of how
+information is categeoried, or the internal logic of an application that generates or presents
+content dynamically.
 
@@
 
-Common feature engineering strategies exploit these potential sources of information
-in ways that are appropriate for a given task. However, while there are wide variety
-of approaches that inconsistently applied, there has not yet been a study that evaluates
-the overall effectiveness of different strategies across a range of applications.
-
-In this work we develop a feature engineering library that maintains an ontology of URL features 
-that relate to underlying structure of the URL, with a method for visualising the importance of features
-across the URL structure. These techniques can prove useful for analysing features for problems that
-consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}. 
-We then present an open source package for generating features within these
-ontologocal classes and apply them to a variety of tasks. We present our results as a
-cross-task evaluation of URL features.
-
-A large amount of recent work on machine learning based on URLs has focused on deep learning approaches that
-learn an embedding representation of the content of the URL. Once of the explicit reasons 
-for this approach is the potential for sensitivity to the sequential structure of the URL.
-\cite{Le2018}
-
-Deep learning approaches include the use of convolutional layers to learn word and character 
-embedings \cite{Le2018},
-
-Classify Web pages based on URLs from the 4 Universities WebKB dataset. Comparing features derived from segmentation
-of the URL to features derived from either link anchor text or the web page document itself \cite{Kan2004}.
-
 Common approaches to feature engineering on URLs include string patterns and regular expressions to
@@
 \cite{Meshkizadeh2010}, n-gram or bag of words models \cite{Baykan2009,Verma2017}, 
-the generation of task specific embedding vectors\cite{Le2018,Qiu2020} and the
+the generation of task specific word embedding vectors based on a segmentation of the URL \cite{Le2018,Qiu2020} and the
 usage of domain name servers or registrars for ancillary information about the domain registration 
@@
 sequences which are built from flexible grammars that allow variable positioning of most key elements. The
-inherent structure of URLs has been shown to be a source of information that can be exploited in algorithm design \cite{Shih2004}.
-Furthermore,
+inherent structure of URLs has been shown to be a source of information that can be exploited in 
+algorithm design \cite{Shih2004}. Furthermore,
 there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
@@
 
+Typically, researchers employ feature engineering strategies exploit these potential sources of information
+in ways that are appropriate for a given task. However, while there are wide variety
+of approaches that are inconsistently applied, there have been limited studies into
+the overall effectiveness of different strategies across a range of applications.
+
+In this work we develop a feature engineering library that maintains an ontology of URL features
+related to underlying structure of the URL. In addition we provide a method for visualising the importance of features
+across the URL structure. These techniques can prove useful for analysing features for problems that
+consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}.
+We then present an open source package for generating features within these
+ontologocal classes and apply them to a variety of tasks. We present our results as a
+cross-task evaluation of URL features.
+
 \section{Methodology}
 
-We design a feature extraction library for URLs that is sensitive to the various sections of URL
-structure outlined above. Previous work has presented datasets for specific problems where the features
+The structural components of a URL shown in Figure \ref{fig:url_structure} are tabulated with an overview of both
+the information source in those components are potenital issues with feature engineering in Table \ref{tab:components}
+
+\begin{table*}
+\caption{URL Components and Feature Information}
+\label{tab:components}
+\begin{tabular}{|l|l|l|}
+\toprule
+Component    &Subcomponent      &Type of Feature Information       \\
+\midrule
+Protocol     &                  &Type of content, technology, security of transmission             \\
+\midrule
+Domain       &                  &Textual data indicating general purpose      \\
+             &Subdomain         &Specific purpose or categorisation of content           \\
+             &Top Level Domain  &Business or service purpose, authenticty, geograpahy, age           \\
+\midrule
+Path         &                  &Content structure, file or operation system, application type or structure         \\
+\midrule
+File         &                  &Naming of specific content, psychological intent, executable or static types      \\
+\midrule
+Parameters   &                  &Substructure of content, personalization, security, tracking         \\
+             &Keys              &Set of categories used to differentiate substructure        \\
+             &Values            &Set of values for substructure, indication of page content        \\
+             &Fragment          &Labels for specifc substructure, source of new application customisation        \\
+\bottomrule
+\end{tabular}
+\end{table*}
+
+We design a feature extraction library for URLs that generates features specific to each component of the
+URL indepenently and using an naming convention that permits sepearation and grouping for analysis.
+Previous work has presented datasets for specific problems where the features
 are provided with a similar structural grouping\cite{Vrban2020}. However, we provide our feature extraction
-application designed so that any specific subset of these features can be extracted for a specific task.
+application designed so that any specific subset of these features can be extracted and analysed 
+for a specific task.
 
@@
 topic classification problems, as is indicated by the strength of the grey lines through the middle of the plot 
-for each task. The contributions of the domain name itself and the top level domain vary across the tasks and do
-not appear consistant across the top broad categories of secutity and topic classification. Suggesting that developers
+for each task. This suggests that these problems rely more heavily on the information from specific components
+of the URL structure.
+
+The contributions of the domain remain high across all problems evaluated. However, whether the key elements is the
+domain name itself, the subdomain or the top level domain varies considerably across the tasks and does
+not appear consistant across the top broad categories of security and topic classification problems. 
+This suggests that data scientists and machine learning engineers
 need to test these features on a task by task basis rather than relying on heuristics.
@@
 We have described the structural elements of a URL from which context specific features can be extracted.
-These feature ideas tend to be used indepednetly within different domains. In this paper we have have 
-collated them into an open source URL feature generation package and then compare their utility across a range
-of indepenent tasks. We have observed that the various structural regions play different roles across 
-these tasks, exhibiting varying levels of importance.
+These features tend to be used indepedently within different problem types and tuned for specific purposes. 
+In this paper we have described an open source URL feature generation package that is both sensitive to the 
+source of information within each component and sufficiently flexible for general use. We conducted experiments
+using the features across a range of indepenent URL classification tasks.
+
+Our experiments demonstrated that the various structural regions play different roles across 
+these tasks, exhibiting varying levels of importance. Some patterns (like the strength of global URL features)
+could be attributed to broader categories of the task, while others appear task specific.
+We have observed that the domain name, with its subcomponents, is a strong and consistent contributor to the
+performance of models across tasks. The source of information from within the domain varies, but it remains
+a rich source of information for machine learning tasks that rely on the URL as acentral feature.
 

### 2023-03-15 scripts/plotting_experiment.py

@@ -1,0 +1,172 @@
+# ###################################################################################
+# Plot URL Imprtance
+#
+# ###################################
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.path as mpath
+import matplotlib.lines as mlines
+import matplotlib.patches as mpatches
+from matplotlib.collections import PatchCollection
+import pandas as pd
+import sys
+
+def add_global(axes, ypos, alph):
+   myy = ypos-0.55
+   axes.add_patch(mpatches.FancyBboxPatch((3.15, myy), 16.1, 0.7,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='grey')
+   )
+
+
+def add_protocol(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((3.3, myy), 2.0, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_subdomain(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((6.0, myy), 0.8, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_domain(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((7.4, myy), 1.7, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_tld(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((9.7, myy), 0.4, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_path(axes, ypos, alph):
+   myy = ypos-0.4
+   axes.add_patch(mpatches.FancyBboxPatch((10.7, myy), 2.3, 0.4,
+       boxstyle=mpatches.BoxStyle("Round", pad=0.2), alpha=alph, color='green')
+   )
+
+def add_file(axes, ypos, alph):
+   myy = ypos-0.4
[…]

### 2023-06-18 paper/acm_paper.tex
Reworked paper for confernce submission

--- 2023-03-15 paper/paper.tex
@@
 \setcopyright{acmcopyright}
-\copyrightyear{2022}
-\acmYear{2022}
+\copyrightyear{2023}
+\acmYear{2023}
 \acmDOI{XXXXXXX.XXXXXXX}
@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2022}{Austin, TX}
+\acmConference[ICCDA '23]{}{July, 2023}{GuiYang, CN}
 \acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+\acmISBN{978-1-4503-XXXX-X/23/07}
 
@@
 For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
-that the feature was derive from, using Figure \ref{fig:url} as a guide to these segments. 
+that the feature was derived from, using Figure \ref{fig:url_structure} as a guide to these segments. 
 We sum the feature importance for all features within a URL segment to allow us to plot the

### 2023-07-03 paper/paper.tex
Paper
Paper revisions - following reviewer feedback - DSCC 2023

@@
-%%
-%% This is file `sample-sigconf.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigconf.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%%
-%% Commands for TeXCount
-%TC:macro \cite [option:text,text]
-%TC:macro \citep [option:text,text]
-%TC:macro \citet [option:text,text]
-%TC:envir table 0 1
-%TC:envir table* 0 1
-%TC:envir tabular [ignore] word
-%TC:envir displaymath 0 word
-%TC:envir math 0 word
-%TC:envir comment 0 0
-%%
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+\documentclass{aircc}
+\usepackage{mathpartir}
+\usepackage{listings}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{graphics}
+\usepackage{geometry}
+\usepackage{listings}
+\usepackage{xcolor}
+\usepackage{anyfontsize}
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    Bib\TeX}}}
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2022}
-\acmYear{2022}
-\acmDOI{XXXXXXX.XXXXXXX}
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+\lstset{style=mystyle}
 
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2022}{Austin, TX}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% For managing citations, it is recommended to use bibliography
-%% files in BibTeX format.
-%%
-%% You can then either use BibTeX with the ACM-Reference-Format style,
-%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
-%% support for advanced citation of software artefact from the
-%% biblatex-software package, also separately available on CTAN.
-%%
-%% Look at the sample-*-biblatex.tex files for templates showcasing
-%% the biblatex styles.
-%%
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{What's in a Domain? Anaylsis of URL Features}
+\title{What's in a Domain? Analysis of URL Features}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
 \author{John Hawkins}
-\email{john.hawkins@Getting-Data-Science-Done.com}
-\orcid{1234-5678-9012}
-\affiliation{%
-  \institution{Getting-Data-Science-Done.com}
-  \city{Sydney}
-  \state{NSW}
-  \country{Australia}
-  \postcode{2000}
-}
+\affiliation{Getting-data-science-done.com}
+\affiliation{Transitional AI Research Group}
 
-\renewcommand{\shortauthors}{Hawkins}
+\maketitle
 
 \begin{abstract}
-Many data science problems require processing log data derived from web pages, apis or other
+Many data science problems require processing log data derived from web pages, APIs or other
 internet traffic sources. URLs are one of the few ubiquitous data fields that describe
@@
 share an open source implementation of these ideas. In addition, we describe a method for 
-exploring URL feature impact that allows for comparison and analysis of the information available inside URLS.
-We experiment with a collection of URL classification problems and demonstrate their utility 
-of these tools. 
+exploring URL feature importance that allows for comparison and analysis of the information 
+available inside URLs.
+We experiment with a collection of URL classification datasets and demonstrate the utility 
+of these tools. Package and source code is open on \textit{https://pypi.org/project/url2features}
 \end{abstract}
-% https://pypi.org/project/url2features
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002951.10003260.10003261</concept_id>
-<concept_desc>Information systems~Web searching and information discovery</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10002951.10003260.10003277.10003280</concept_id>
-<concept_desc>Information systems~Web log analysis</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010147.10010257</concept_id>
-<concept_desc>Computing methodologies~Machine learning</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Web searching and information discovery}
-\ccsdesc[500]{Information systems~Web log analysis}
-\ccsdesc[500]{Computing methodologies~Machine learning}
-
-\keywords{URL Features, Document Classification, Machine Learning, Semantic Web}
-
-\maketitle
+\begin{keywords}
+Machine Learning, Feature Engineering, Web Search, Semantic Web, Data Science
+\end{keywords}
 
@@
 
-The Uniform Resource Locator (URL) is a ubiquitous element the digital world. 
+The Uniform Resource Locator (URL) is a ubiquitous element in the digital world. 
 We use them to retrieve news and media, advertise or find businesses and services, 
-and to interact with other people across a broad of social applications. Below the
+and to interact with other people across a broad range of social applications. Below the
 surface many online services use URLs internally for communicating with other digital
@@
 and the likely country of origin. The domain is also a source of additional information 
-through requests to Domain Name Servers (DNS) to understand both its history and structure
- of its network topology and resources.
+through requests to Domain Name Servers (DNS) to understand both its history and the
+structure of its network topology and resources.
 
 Beyond the domain, the URL consists of a sequence of words, categories, identfiers, dates
-or domain specific abreviations. This sequence can indicate the psychoogical elements of how
+or domain specific abreviations. This sequence can indicate the psychological elements of how
 information is categeoried, or the internal logic of an application that generates or presents
@@
 \centering
+\resizebox{\columnwidth}{!}{%
 \includegraphics[scale=0.6]{images/URL_parts.png}
+}
 \caption{Structural components of a URL requiring specific feature engineering treatment}
@@
 sequences which are built from flexible grammars that allow variable positioning of most key elements. The
-inherent structure of URLs has been shown to be a source of information that can be exploited in 
+inherent structure of URLs has been demonstrated to be a source of information that can be exploited in 
 algorithm design \cite{Shih2004}. Furthermore,
@@
 
-Typically, researchers employ feature engineering strategies exploit these potential sources of information
+Typically, researchers employ feature engineering strategies to exploit these potential sources of information
 in ways that are appropriate for a given task. However, while there are wide variety
@@
 ontologocal classes and apply them to a variety of tasks. We present our results as a
-cross-task evaluation of URL features.
+cross-task evaluation of URL features. The strength of our approach lies in the ability to both understand how
+machine learning models use URLs in decision making, this is opposed to the black-box problem with neural network
+models that treat the URL as a text sequence. In addition, the cross-task evaluation we perform provides insight into
+what works within different domains. This is critical as many machine learning problems that rely on URLS require
+models built on relatively small datasets, so that new patterns of fraud and behaviour can be reacted to in a timely
+fashion.
 
@@
 
-The structural components of a URL shown in Figure \ref{fig:url_structure} are tabulated with an overview of both
-the information source in those components are potenital issues with feature engineering in Table \ref{tab:components}
+The structural components of a URL (as illustrated in Figure \ref{fig:url_structure}) are listed in Table \ref{tab:components}.
+We include an overview the information source in each of those components and highlight how these components relate to
+functional machine learning features.
 
@@
 \label{tab:components}
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{|l|l|l|}
@@
 \end{tabular}
+}
 \end{table*}
@@
 We design a feature extraction library for URLs that generates features specific to each component of the
-URL indepenently and using an naming convention that permits sepearation and grouping for analysis.
+URL independently using a naming convention that permits sepearation and grouping for analysis.
 Previous work has presented datasets for specific problems where the features
@@
 We apply this library to multiple machine learning tasks using only URLs as the input variable. We choose
-these tasks such that they span very different classes of problems an dataset sizes. 
+these tasks such that they span very different classes of problems and dataset sizes. 
 We experiment with multiple standard machine learning techniques and evaluate
 the impact of the URL features using the SHAP package for feature importance. We develop a process
-for analysing thess features within the logical structure of the URL.
+for analysing these features within the logical structure of the URL.
 
@@
 \caption{Datasets}
+\fontsize{3pt}{3pt}\selectfont
 \label{tab:data}
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{|l|r|r|r|}
@@
 \end{tabular}
+}
 \end{table}
@@
 \label{tab:features}
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{|l|l|l|l|}
@@
 \end{tabular}
+}
 \end{table*}
 
-\subsection{Features}
+\subsection{Feature Generation}
 
-We generate URL features in groups that focus on distinct regions across the URL. We create a group
-of global features that contain general string properties of the entire URL, then create regions
-specific features as outlined in Table \ref{tab:features}.
+We generate URL features using a set of functions that focus on distinct types of features applied to specific 
+regions across the URL. This permits users to apply subsets of functions that define only the features they
+require. In addition we create a group of global features that contain general string properties of the entire 
+URL, rather than specific regions. The complete set of features, along with their categorisation and definition
+are outlined in Table \ref{tab:features}.
 
@@
 
+\begin{lstlisting}[language=Bash,label={code:cli}, caption=Install and invoke the url2features package from CLI]
+pip install url2features
+url2features -columns=URLCOL -host -tld input.csv > output.csv
+\end{lstlisting}
+
+The commands for installing and invoking the \emph{url2features} package from the command line are shown
+in Listing \ref{code:cli}. 
+When execting this code it will take the tabular data inside the file \emph{input.csv} and then apply feature 
+engineering on the column named \emph{URLCOL}. The features to be created are defined by the switches 
+$-host$ and $-tld$ for the host and top level domain features. By default the application outputs to
+STDOUT, so in this example we are redirecting the output of the program to create a new file \emph{output.csv}.
+
+\begin{lstlisting}[language=Python,label={code:skl}, caption=Usage of url2features with scikit-learn pipelines ]
+from url2features.pipeline import URLTransform
+from sklearn.linear_model import SGDClassifier
+from sklearn.pipeline import Pipeline
+
+pipeline = Pipeline([
+    ('urltransform', URLTransform(['URLCOL'],['host','tld']) ),
+    ('clf', SGDClassifier(loss='log') ),
+])
+\end{lstlisting}
+
+The package can also be invoked programmatically and included inside a machine learning framework like 
+scikit-learn pipelines\cite{pedregosa2011scikit}. This is shown in Listing \ref{code:skl}, where the
+same two feature engineering functions (host and tld) are included as feature transformers in a machine 
+learning pipeline. The advantage of this approach is that these transformations can be built into a single
+serialised model for deployment.
+
 \subsection{Feature Importance}
@@
 We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
-of 80-100 smaples per experiment. We aggregate the shapley values for these sample points to calculate the mean
-absolute contribution of each feature, as is typically done in Shaplet fetaure importance plots.
+of 80-100 samples per experiment. We aggregate the Shapley values for these sample points to calculate the mean
+absolute contribution of each feature, as is typically done in Shapley feature importance plots.
 
 For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
-that the feature was derive from, using Figure \ref{fig:url} as a guide to these segments. 
+that the feature was derived from, using Figure \ref{fig:url_structure} as a guide to these segments. 
 We sum the feature importance for all features within a URL segment to allow us to plot the
@@
 
-These plots allow for structural understanding of how URL data
-controbutes to predictive performance of a model and permits the comparison of feature importance 
-across the five problems in this study. The script for generating these plots is provides as part of the
-`url2features` open source package.
+These plots allow for a structural understanding of how URL data
+contributes to predictive performance of a model and permits the comparison of feature importance 
+across the six problems in this study. The script for generating these plots is provided as part 
+of the source code for the `url2features` package.
 
@@
 
-A set of standard machine learning pipelines are applied to each of the four problems. Each approach is applied
+A set of standard machine learning pipelines are applied to each of the six problems. Each approach is applied
 using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
 of model. All details are available in the source repository for the experiments. The performance of the models
-is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
+is shown in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
 metric is appropriate and comparable across all six problems.
@@
 \caption{Machine Learning Results}
+\fontsize{3pt}{3pt}\selectfont
 \label{tab:results}
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{|l|r|r|r|r|}
@@
 \centering
+\resizebox{\columnwidth}{!}{%
 \includegraphics[scale=0.8]{images/URL_importance.png}
+}
 \caption{Structural Depiction of URL Feature Importance}
@@
 and user preference based tasks achieve far more modest performance. It is worth noting that these problems 
-are hindered by both higher cardinality targets and greater variability in dataset size, 2 of the 3 data 
-sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
+are hindered by both higher cardinality in the classification targets and greater variability in dataset size,
+ 2 of the 3 data sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
 dataset strongly suggests that, in general, URL based topic classification is likely to remain a difficult
@@
 We see that there is substantial variability across all classification tasks in these experiments.
-The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classifcation
-task, where we see some value in the URL parameter features. The domain, path and file regions are the predominant sources
+The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classification
+task, where we see value in the URL parameter features. The domain, path and file regions are the predominant sources
 of signal across these tasks. Nevertheless, the emphasis changes between them. The subdomain appears particularly
-important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classifciation data.
+important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classification data.
 
@@
 
-\section{Acknowledgments}
-
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{ieeetr}
 \bibliography{refs}
@@
 \endinput
-%%
-%% End of file `sample-sigconf.tex'.

### 2023-07-03 scripts/plotting_experiment.py
Missing import in Script

@@ -11,6 +11,7 @@ import matplotlib.patches as mpatches
 from matplotlib.collections import PatchCollection
 import pandas as pd
 import sys
+import os
 
 def add_global(axes, ypos, alph):
    myy = ypos-0.55

### 2023-08-05 paper/paper.tex
Typos and formatting

@@
 internet activity, hence they require effective processing for a wide variety of machine 
-learning applications. While URLs are structurally rich, the structure can be both domain specific
-and subject to change over time, making feature engineering for URLs an ongoing challenge.
+learning applications. While URLs are structurally rich, the structure can be both domain 
+specific and subject to change over time, making feature engineering for URLs an ongoing 
+challenge.
 
@@
 
-Processing URLs is key component of many tasks that involve
+Processing URLs is a key component of many tasks that involve
 analysing internet data. In many applications the URL is the central piece of 
@@
 in a rapid and efficient manner to provide utility\cite{Ma2009b}.
-Common use cases for URL centered analysis include security analysis of potenital phishing 
-attacks\cite{Garera2007,Basnet2012,Basnet2014,Mamun2016,Verma2017,Vazhayil2018,Tupsamudre2019,Sirigineedi2020,Li2020}, 
+Common use cases for URL centered analysis include security analysis of potential 
+phishing attacks\cite{Garera2007,Basnet2012,Basnet2014,Mamun2016,Verma2017,Vazhayil2018,Tupsamudre2019,Sirigineedi2020,Li2020}, 
 and identification of pages that host malware or viruses \cite{Canali2011,Mamun2016}.
@@
 
-Beyond the domain, the URL consists of a sequence of words, categories, identfiers, dates
+Beyond the domain, the URL consists of a sequence of words, categories, identifiers, dates
 or domain specific abreviations. This sequence can indicate the psychological elements of how
@@
 
-Common approaches to feature engineering on URLs include string patterns and regular expressions to
-identify key sequences and lexical properties \cite{Kan2004,Garera2007,Mamun2016,Tupsamudre2019}, 
+Common approaches to feature engineering on URLs include string patterns and regular 
+expressions to identify key sequences and lexical properties 
+\cite{Kan2004,Garera2007,Mamun2016,Tupsamudre2019}, 
 creation of lookup tables or likelihood scores based on key sequences
 \cite{Meshkizadeh2010}, n-gram or bag of words models \cite{Baykan2009,Verma2017}, 
-the generation of task specific word embedding vectors based on a segmentation of the URL \cite{Le2018,Qiu2020} and the
-usage of domain name servers or registrars for ancillary information about the domain registration 
-and server configuration\cite{Canali2011,Li2020}. In many modern approaches to malicious URL detection
-multiple feature engineering approaches are typically combined\cite{Sayamber2014,Li2020}. Increasingly,
-sophisticated methods are used to combine, select or learn from combinations of features to adapt to
-changing requirements, particularly in internet security applications\cite{Sountharrajan2020,Li2020}.
+the generation of task specific word embedding vectors based on a segmentation of the 
+URL \cite{Le2018,Qiu2020} and the usage of domain name servers or registrars for 
+ancillary information about the domain registration 
+and server configuration\cite{Canali2011,Li2020}. 
+In many modern approaches to malicious URL detection
+multiple feature engineering approaches are typically combined\cite{Sayamber2014,Li2020}.
+Increasingly, sophisticated methods are used to combine, select or learn from 
+combinations of features to adapt to changing requirements, particularly in 
+internet security applications\cite{Sountharrajan2020,Li2020}.
 
-Some authors have 
-emphasized that URLs are sequences of characters and require feature extraction methods that respect 
-this sequential nature\cite{Le2018,Vazhayil2018}. They have naturally turned to developing neural network approaches
+Some authors have emphasized that URLs are sequences of characters and require 
+feature extraction methods that respect 
+this sequential nature\cite{Le2018,Vazhayil2018}. 
+They have turned to developing neural network approaches
 based on convolutional or recurrent layers for learning these sequential structures.
-However, the ordering of key features within URLs is predominantly fixed as shown in Figure \ref{fig:url_structure}.
-The core elements of URL structure occur at fixed positions within the sequence, in contrast to human language
-sequences which are built from flexible grammars that allow variable positioning of most key elements. The
-inherent structure of URLs has been demonstrated to be a source of information that can be exploited in 
-algorithm design \cite{Shih2004}. Furthermore,
-there are psychological and social elements to URL construction (such as the use of common brand names in subdomains
-for phishing attack URLS \cite{Tupsamudre2019}), which emphasize the utility of feature engineering techniques that
+However, the ordering of key features within URLs is predominantly fixed as shown 
+in Figure \ref{fig:url_structure}. The core elements of URL structure occur at 
+fixed positions within the sequence, in contrast to human language
+sequences which are built from flexible grammars that allow variable positioning of 
+most key elements. The inherent structure of URLs has been demonstrated to be a source 
+of information that can be exploited in algorithm design \cite{Shih2004}. Furthermore,
+there are psychological and social elements to URL construction (such as the use of 
+common brand names in subdomains for phishing attack URLS \cite{Tupsamudre2019}), 
+which emphasize the utility of feature engineering techniques that
 respect the inherent structure of URLs.
 
-Typically, researchers employ feature engineering strategies to exploit these potential sources of information
+Typically, researchers employ feature engineering strategies to exploit these 
+potential sources of information
 in ways that are appropriate for a given task. However, while there are wide variety
@@
 
-In this work we develop a feature engineering library that maintains an ontology of URL features
-related to underlying structure of the URL. In addition we provide a method for visualising the importance of features
-across the URL structure. These techniques can prove useful for analysing features for problems that
-consist of moving targets and require broad sets of potential features and efficient feature selection \cite{Basnet2012}.
-We then present an open source package for generating features within these
+In this work we develop a feature engineering library that maintains an ontology of 
+URL features related to underlying structure of the URL. In addition we provide a 
+method for visualising the importance of features across the URL structure. 
+These techniques can prove useful for analysing features for problems that
+consist of moving targets and require broad sets of potential features and 
+efficient feature selection \cite{Basnet2012}.
+We present an open source package for generating features within these
 ontologocal classes and apply them to a variety of tasks. We present our results as a
-cross-task evaluation of URL features. The strength of our approach lies in the ability to both understand how
-machine learning models use URLs in decision making, this is opposed to the black-box problem with neural network
-models that treat the URL as a text sequence. In addition, the cross-task evaluation we perform provides insight into
-what works within different domains. This is critical as many machine learning problems that rely on URLS require
-models built on relatively small datasets, so that new patterns of fraud and behaviour can be reacted to in a timely
-fashion.
+cross-task evaluation of URL features. The strength of our approach lies in the 
+ability to both understand how machine learning models use URLs in decision making, 
+as opposed to the black-box problem with neural network
+models that treat the URL as a text sequence. In addition, the cross-task evaluation 
+we perform provides insight into what works within different domains. 
+This is critical as many machine learning problems that rely on URLS require
+models built on relatively small datasets, so that new patterns of fraud and 
+behaviour can be detected rapidly.
 
@@
 
-The structural components of a URL (as illustrated in Figure \ref{fig:url_structure}) are listed in Table \ref{tab:components}.
-We include an overview the information source in each of those components and highlight how these components relate to
-functional machine learning features.
+The structural components of a URL (as illustrated in Figure \ref{fig:url_structure}) 
+are listed in Table \ref{tab:components}.
+We include an overview of the information source in each of those components and 
+highlight how these components relate to machine learning features.
 
@@
 
-We design a feature extraction library for URLs that generates features specific to each component of the
-URL independently using a naming convention that permits sepearation and grouping for analysis.
+We design a feature extraction library for URLs that generates features specific 
+to each component of the URL independently using a naming convention that permits 
+separation and grouping for analysis.
 Previous work has presented datasets for specific problems where the features
-are provided with a similar structural grouping\cite{Vrban2020}. However, we provide our feature extraction
-application designed so that any specific subset of these features can be extracted and analysed 
-for a specific task.
+are provided with a similar structural grouping\cite{Vrban2020}. However, we provide 
+our feature extraction application designed so that any specific subset of these 
+features can be extracted and analysed for a specific task.
 
-We apply this library to multiple machine learning tasks using only URLs as the input variable. We choose
-these tasks such that they span very different classes of problems and dataset sizes. 
-We experiment with multiple standard machine learning techniques and evaluate
-the impact of the URL features using the SHAP package for feature importance. We develop a process
+We apply this library to multiple machine learning tasks using only URLs as the 
+input variable. We choose these tasks such that they span very different classes 
+of problems and dataset sizes. We experiment with multiple standard machine 
+learning techniques and evaluate the impact of the URL features using the SHAP 
+package for feature importance. We develop a process
 for analysing these features within the logical structure of the URL.

### 2023-08-24 paper/paper.tex
Affiliation struction
Paper update

@@
 \author{John Hawkins}
-\affiliation{Getting-data-science-done.com}
-\affiliation{Transitional AI Research Group}
+\affiliation{Transitional AI Research Group\\Getting-Data-Science-Done.com}
 
@@
 there are psychological and social elements to URL construction (such as the use of 
-common brand names in subdomains for phishing attack URLS \cite{Tupsamudre2019}), 
+common brand names in subdomains for phishing attack URLs \cite{Tupsamudre2019}), 
 which emphasize the utility of feature engineering techniques that
@@
 we perform provides insight into what works within different domains. 
-This is critical as many machine learning problems that rely on URLS require
+This is critical as many machine learning problems that rely on URLs require
 models built on relatively small datasets, so that new patterns of fraud and 
@@
 \subsection{Data}
-The data used in this study was colated from a range of sources to represent a varity of
+The data used in this study was colated from a range of sources to represent a variety of
 Internet resource classification problems containing URLs as the primary feature.
-The ISCX Malcious URL classification dataset contains malware, spam and phishing URLS
-that need to be discriminated against a set of benign URLS\cite{Mamun2016}.
+The ISCX Malicious URL classification dataset contains malware, spam and phishing URLS
+that need to be discriminated against a set of benign URLs\cite{Mamun2016}.
 The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
@@
 
-These 6 URL classification problems are summarised in Table \ref{tab:data}, where
+These 6 URL classification problems are summarised in Table \ref{tab:data}, where we
 show the number of records, the cardinality of the target classes, and the proportion
@@
 
-We generate all URL features for each of these datasets and then apply a range of machine learning
-techniques to build classifiers that can be analysed for key features for each task.
+We generate all URL features for each of these datasets and then apply a range of 
+machine learning
+techniques to build classifiers that can be analysed for key features on each task.
 
@@
 
-We generate URL features using a set of functions that focus on distinct types of features applied to specific 
-regions across the URL. This permits users to apply subsets of functions that define only the features they
-require. In addition we create a group of global features that contain general string properties of the entire 
-URL, rather than specific regions. The complete set of features, along with their categorisation and definition
+We generate URL features using a set of functions that focus on distinct types of 
+features applied to specific regions across the URL. 
+This permits users to apply subsets of functions that define only the features they
+require. In addition we create a group of global features that contain general string 
+properties of the entire URL, rather than specific regions. 
+The complete set of features, along with their categorisation and definition
 are outlined in Table \ref{tab:features}.
 
-These URL feature functions are available in our open source implmentation and python package \emph{url2features}. 
-The package is designed such that it can process large files in chunks and will only add the specific sub-groups of
-features a user requests. In addition, the naming convention is designed so that features relating to specific
+These URL feature functions are available in our open source implmentation and 
+python package \emph{url2features}. 
+The package is designed such that it can process large files in chunks and will 
+only add the specific sub-groups of
+features a user requests. In addition, the naming convention is designed so that 
+features relating to specific
 regions of the URL can be identified and analysed as a group.
@@
 
-The commands for installing and invoking the \emph{url2features} package from the command line are shown
-in Listing \ref{code:cli}. 
-When execting this code it will take the tabular data inside the file \emph{input.csv} and then apply feature 
-engineering on the column named \emph{URLCOL}. The features to be created are defined by the switches 
-$-host$ and $-tld$ for the host and top level domain features. By default the application outputs to
-STDOUT, so in this example we are redirecting the output of the program to create a new file \emph{output.csv}.
+The commands for installing and invoking the \emph{url2features} package from the 
+command line are shown in Listing \ref{code:cli}. 
+When executing this code it will take the tabular data inside the file 
+\emph{input.csv} and then apply feature 
+engineering on the column named \emph{URLCOL}. 
+The features to be created are defined by the switches 
+$-host$ and $-tld$ for the host and top level domain features. 
+By default the application outputs to
+STDOUT, so in this example we are redirecting the output of the program to 
+create a new file \emph{output.csv}.
 
@@
 
-The package can also be invoked programmatically and included inside a machine learning framework like 
-scikit-learn pipelines\cite{pedregosa2011scikit}. This is shown in Listing \ref{code:skl}, where the
-same two feature engineering functions (host and tld) are included as feature transformers in a machine 
-learning pipeline. The advantage of this approach is that these transformations can be built into a single
+The package can also be invoked programmatically and included inside a machine 
+learning framework like 
+scikit-learn pipelines\cite{pedregosa2011scikit}. 
+This is shown in Listing \ref{code:skl}, where the
+same two feature engineering functions (host and tld) are included 
+as feature transformers in a machine learning pipeline. 
+The advantage of this approach is that these transformations can be built into a single
 serialised model for deployment.
@@
 
-We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a small holdout test set 
-of 80-100 samples per experiment. We aggregate the Shapley values for these sample points to calculate the mean
-absolute contribution of each feature, as is typically done in Shapley feature importance plots.
+We use the SHAP\cite{Lundberg2017} package to calculate feature importance using a 
+small holdout test set of 80-100 samples per experiment. 
+We aggregate the Shapley values for these sample points to calculate the mean
+absolute contribution of each feature, as is typically done in Shapley feature 
+importance plots.
 
-For our URL feature analysis, we then group these individual feature importance values by the specific URL segment
-that the feature was derived from, using Figure \ref{fig:url_structure} as a guide to these segments. 
+For our URL feature analysis, we then group these individual feature importance 
+values by the specific URL segment that the feature was derived from, 
+using Figure \ref{fig:url_structure} as a guide to these segments. 
 We sum the feature importance for all features within a URL segment to allow us to plot the
-segment contributions to model performance. We provide a thin grey coloured line covering the entire segment
-which captures the importance of global features (like URL length). If the script is applied to a dataset with
+segment contributions to model performance. We provide a thin grey coloured line 
+covering the entire segment
+which captures the importance of global features (like URL length). 
+If the script is applied to a dataset with
 more than just URL features then all non-URL fetaures would be grouped into this global group. All segment specific
@@
 These plots allow for a structural understanding of how URL data
-contributes to predictive performance of a model and permits the comparison of feature importance 
-across the six problems in this study. The script for generating these plots is provided as part 
+contributes to predictive performance of a model and permits the comparison of 
+feature importance 
+across the six problems in this study. 
+The script for generating these plots is provided as part 
 of the source code for the `url2features` package.
@@
 
-A set of standard machine learning pipelines are applied to each of the six problems. Each approach is applied
-using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
-of model. All details are available in the source repository for the experiments. The performance of the models
-is shown in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
+A set of standard machine learning pipelines are applied to each of the six 
+problems. Each approach is applied using default parameters, without any fine tuning. 
+We use feature preprocessing modules appropriate for each class
+of model. All details are available in the source repository for the experiments. 
+The performance of the models is shown in Table \ref{tab:results}, where we show 
+Balanced Accuracy of each model on the holdout data, as this
 metric is appropriate and comparable across all six problems.
@@
 
-The table of results indicates that internet security problems appear much more amenable to URL based 
-classification. All three of these problems result in high performing classifiers. In comparison the topic
-and user preference based tasks achieve far more modest performance. It is worth noting that these problems 
-are hindered by both higher cardinality in the classification targets and greater variability in dataset size,
- 2 of the 3 data sets are much smaller than any of the security datasets. However, the performance on the very large DMOZ
-dataset strongly suggests that, in general, URL based topic classification is likely to remain a difficult
-problem.
+The table of results indicates that internet security problems appear much more 
+amenable to URL based classification. All three of these problems result in high 
+performing classifiers. By comparison the topic and user preference classification
+tasks achieve far more modest performance. It is worth noting that these problems 
+are hindered by both higher cardinality in the classification targets and greater 
+variability in dataset size, 2 of the 3 data sets are much smaller than any of the 
+security datasets. However, the performance on the very large DMOZ
+dataset strongly suggests that, in general, URL based topic classification is 
+likely to remain a difficult problem.
 
-We used the results from the best performing classification model for each individual problem and generated
-the SHAP values for the records in the test dataset. These records are then used to generate the URL Structure 
-Feature Importance Plot shown in Figure \ref{fig:importance}. This plot aggregates the importance of individual
-features into their region of origin within the URL structure. Allowing us to visualise the source of signal for
+We used the results from the best performing classification model for each 
+individual problem and generated the SHAP values for the records in the test dataset. 
+These records are then used to generate the URL Structure Feature Importance Plot 
+shown in Figure \ref{fig:importance}. This plot aggregates the importance of individual
+features into their region of origin within the URL structure. 
+Allowing us to visualise the source of signal for
 each task and compare features across tasks.
 
-We see that there is substantial variability across all classification tasks in these experiments.
-The protocol and parameters sections remain mostly devoid of signal, with the exception of the Spam URL classification
-task, where we see value in the URL parameter features. The domain, path and file regions are the predominant sources
-of signal across these tasks. Nevertheless, the emphasis changes between them. The subdomain appears particularly
-important for the phishing URL identfication, whereas the URL target file is the focus for the WebKb classification data.
+We see that there is substantial variability across all classification tasks in 
+these experiments.
+The protocol and parameters sections remain mostly devoid of signal, with the 
+exception of the Spam URL classification task, where we see value in the URL 
+parameter features. The domain, path and file regions are the predominant sources
+of signal across these tasks. Nevertheless, the emphasis changes between them. 
+The subdomain appears particularly
+important for the phishing URL identfication, whereas the URL from domain to filename 
+is important for the WebKb classification data.
 
-The internet security problems appear to derive less utility from the global features when compared to the three
-topic classification problems, as is indicated by the strength of the grey lines through the middle of the plot 
-for each task. This suggests that these problems rely more heavily on the information from specific components
-of the URL structure.
+The internet security problems appear to derive less utility from the global 
+features when compared to the three topic classification problems, as is 
+indicated by the strength of the grey lines through the middle of the plot 
+for each task. This suggests that these problems rely more heavily on the 
+information from specific components of the URL structure.
 
-The contributions of the domain remain high across all problems evaluated. However, whether the key elements is the
-domain name itself, the subdomain or the top level domain varies considerably across the tasks and does
-not appear consistant across the top broad categories of security and topic classification problems. 
+The contributions of the domain remain high across all problems evaluated. 
+However, whether the key elements is the
+domain name itself, the subdomain or the top level domain varies considerably 
+across the tasks and does not appear consistant across the top broad categories 
+of security and topic classification problems. 
 This suggests that data scientists and machine learning engineers
@@
 
-We have described the structural elements of a URL from which context specific features can be extracted.
-These features tend to be used indepedently within different problem types and tuned for specific purposes. 
-In this paper we have described an open source URL feature generation package that is both sensitive to the 
-source of information within each component and sufficiently flexible for general use. We conducted experiments
+We have described the structural elements of a URL from which context specific 
+features can be extracted.
+These features tend to be used indepedently within different problem types and 
+tuned for specific purposes. 
+In this paper we have described an open source URL feature generation package 
+that is both sensitive to the 
+source of information within each component and sufficiently flexible for general use. 
+We conducted experiments
 using the features across a range of indepenent URL classification tasks.
 
-Our experiments demonstrated that the various structural regions play different roles across 
-these tasks, exhibiting varying levels of importance. Some patterns (like the strength of global URL features)
+Our experiments demonstrated that the various structural regions play different 
+roles across these tasks, exhibiting varying levels of importance. 
+Some patterns (like the strength of global URL features)
 could be attributed to broader categories of the task, while others appear task specific.
-We have observed that the domain name, with its subcomponents, is a strong and consistent contributor to the
-performance of models across tasks. The source of information from within the domain varies, but it remains
-a rich source of information for machine learning tasks that rely on the URL as acentral feature.
+We have observed that the domain name, with its subcomponents, is a strong and 
+consistent contributor to the performance of models across tasks. The source of 
+information from within the domain varies, but it remains
+a rich source of information for machine learning tasks that rely on the URL as a 
+central feature.
 
